### 2023-02-28 manuscript.tex
Remove 'done' TODOs [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/e9be1f19a7a3e08520efc834431cde4dfe4c4d4a.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/e9be1f19a7a3e08520efc834431cde4dfe4c4d4a/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/4292500501

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/e9be1f19a7a3e08520efc834431cde4dfe4c4d4a/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/e9be1f19a7a3e08520efc834431cde4dfe4c4d4a}{habi/EAWAG-manuscript@e9be1f1}
on February 28, 2023.

\hypertarget{authors}{%
\subsection{Authors}\label{authors}}

\begin{itemize}
\item
  \textbf{David Haberthür}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Baltzerstrasse 2, CH-3012 Bern, Switzerland
\item
  \textbf{Mikki Law}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/mlaw-migalig}{mlaw-migalig}
  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, EAWAG, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
\item
  \textbf{Kassandra Ford}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-4413-2633}{0000-0002-4413-2633}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/kassthefish}{kassthefish}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/kassthefish}{kassthefish}
  Department of Biological Sciences, George Washington University; EAWAG Aquatic Research Institute, Switzerland; Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland
\item
  \textbf{Marcel Häsler}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/mphaesler}{mphaesler}
  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, EAWAG, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
\item
  \textbf{Ole Seehausen}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-6598-1434}{0000-0001-6598-1434}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/OleSeehausen}{OleSeehausen}
  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, EAWAG, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
\item
  \textbf{Ruslan Hlushchuk}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-6722-8996}{0000-0002-6722-8996}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/RuslanHlushchuk}{RuslanHlushchuk}
  Institute of Anatomy, University of Bern, Baltzerstrasse 2, CH-3012 Bern, Switzerland
\end{itemize}

\hypertarget{technicalities-temporary}{%
\subsection{Technicalities (temporary)}\label{technicalities-temporary}}

\begin{itemize}
\tightlist
\item
  The \emph{canonical} version of the manuscript are the \href{https://en.wikipedia.org/wiki/Markdown}{Markdown} files in the \href{https://github.com/habi/EAWAG-manuscript/tree/main/content}{\texttt{content} folder} of the repository.
\item
  These files are automatically converted to a \href{https//habi.github.io/EAWAGmanuscript/}{website} as well as a \href{https//habi.github.io/EAWAGmanuscript/manuscript.pdf}{PDF} and \href{https//github.com/habi/EAWAGmanuscript/raw/output/manuscript.docx}{DOC} file through \href{https//manubot.org/}{\texttt{manubot}}.
  You can read whichever file is most convenient for you.
  Each version/file contains a link to the version in the header just below the title.
  This version string is the so-called git hash of the repository.
\item
  On January 26, 2023 I've sent an email to the co-authors with \href{https//en.wikipedia.org/wiki/Request_for_Comments}{RFC}.
  This version of the manuscript was \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v0.618}{tagged as version 0.618}, and there have been some changes since then.
  You can visualize the changes made since then \href{https://github.com/habi/EAWAG-manuscript/compare/v0.618...main}{here}.
\end{itemize}

\hypertarget{abstract}{%
\subsection{Abstract}\label{abstract}}

A large collection of cichlids from Lake Victoria in Africa spanning a size range of 6 to 20 cm was nondestructively imaged using micro-computed tomography.
We describe our method to efficiently obtain three-dimensional tomographic data sets of the oral and pharyngeal jaws and the whole skull of these fishes for accurately describing their morphology.
The tomographic data we acquired (9.5 TB projection images) was reconstructed into 1.4 TB of three-dimensional images used for extracting the relevant features of interest.
Herein we present our method and an outlook on analyzing the acquired data; a morphological description of the oral and pharyngeal jaws of the fishes, a principal component analysis of landmark features on the fish skulls and a robust method to automatically extract the otoliths of the fishes from the tomographic data.

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

\hypertarget{history}{%
\subsubsection{History}\label{history}}

Cichlid fish in African lakes are a powerful model systems in speciation and adaptive evolutionary radiation research {[}\protect\hyperlink{ref-TUQFenhc}{1},\protect\hyperlink{ref-W2f2SDjn}{2}{]}.
The functional decoupling of their oral and pharyngeal jaws is hypothesized to be a factor in making cichlids unusually versatile in their feeding and making it possible for making them able to adapt to a wide range of environmental factors {[}\protect\hyperlink{ref-1GEljkDsf}{3}{]}.
The hypothesis is that the fusion of the lower pharyngeal jaws makes them powerful food processing tools, and this in turn releases the oral jaws from functional constraint.
The oral jaws no longer need to process prey and can therefore specialize on prey capture.

The group of Ole Seehausen has studied the evolutionary diversification of cichlid fish radiations in Lake Victoria in Africa since a long time {[}\protect\hyperlink{ref-W2f2SDjn}{2},\protect\hyperlink{ref-c3poTogo}{4}{]}.
We aim to to better understand the functional anatomy of the skulls and jaws in these fishes in order to test the functional decoupling and other hypotheses about what may facilitate exceptionally high rates of morphological evolution.

The collection of cichlid fish available is extremely valuable, hence a nondestructive imaging method is paramount for studying these samples.
Since micro--computed tomography can be regarded as nondestructive method for biological samples, it is a very well suited method for investigating the oral and pharyngeal jaws as well as the skull features of the fishes presented in this study.

\hypertarget{micro-computed-tomography}{%
\subsubsection{Micro-computed tomography}\label{micro-computed-tomography}}

X-ray microtomography is a valuable tool to gain insights into the inner structure of very diverse samples, namely for specimens related to research done in the biomedical sciences.
Microtomographic imaging has been employed as a method of choice to nondestructively assess the morphology of different kind of fishes, large and small.
For a small overview of analyses which are possible with X-ray microtomographic imaging in relation to fish biology and morphology, see prior work of the authors of this manuscript {[}\protect\hyperlink{ref-8Pmc2mI8}{5},\protect\hyperlink{ref-BDrCSu8p}{6}{]} or other authors {[}\protect\hyperlink{ref-3rxGCEvJ}{7}{]}\footnote{For which David made a tomographic scan of an adult zebrafish in 2016.}.

Depending on the structures of interest, biomedical samples are often tomographically scanned after the tissue/sample has been stained with a contrast agent, most often employing contrast agents containing heavy metals.
Since the structures of interest for the two studies we touch upon in this manuscript (cichlid teeth and skulls) display large enough contrast to the surrounding tissue we did not stain our samples prior to the tomographic imaging presented here.

\hypertarget{materials-methods-and-results}{%
\subsection{Materials, Methods and Results}\label{materials-methods-and-results}}

\hypertarget{sample-procurement-and-preparation}{%
\subsubsection{Sample procurement and preparation}\label{sample-procurement-and-preparation}}

The fishes were kept in 75\% Ethanol for long-term storage in the EAWAG fish collection.
They were delivered to the Institute of Anatomy for micro-CT imaging sorted into several batches by approximately equal length.

\hypertarget{micro-computed-tomographic-imaging}{%
\subsubsection{Micro-computed tomographic imaging}\label{micro-computed-tomographic-imaging}}

All samples were scanned on two of the three available high-resolution micro-CT machines of the Institute of Anatomy of the University of Bern in Switzerland, a SkyScan 1272 and a SkyScan 2214 (both Bruker microCT, Kontich, Belgium).

The fishes were sorted into `bins' based on their physical size.
We used a custom-made sample-holder to scan each of the fish in our machines.
It was 3D-printed on a Form 2 desktop stereolithography printer (Formlabs, Somerville, Massachusetts, USA) and is freely available online {[}\protect\hyperlink{ref-VCZPOv2f}{8}{]} as part of a library of sample holders for tomographic scanning of biomedical samples {[}\protect\hyperlink{ref-115PPSuQp}{9}{]}.
The sample holder was custom-made for this project and is easily parametrized to the different width, height and length classes of the fishes we scanned.

In total, we acquired 362 tomographic scans of 129 different fishes.
All the scanning parameters are collected in a table in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}, a generalized rundown is given below.

Since the fishes greatly varied in their length, the voxel sizes of each of the acquired datasets also varies greatly.
We acquired datasets with (isometric) voxel sizes ranging from 3.5--50 μm.

Depending on the size of the specimen we set the x-ray source voltage to 50--80 kV and---depending on the voltage---to a current between 107 and 200 μA.
Also depending on the size of the fishes, the x-ray spectrum was filtered either by an Aluminum filter of varying thickness (either 0.25, 0.5 or 1 mm) before digitization to projection images or recorded in an unfiltered way.
In total we recorded 9.5 TB of projections images (\texttt{*.tif} and \texttt{*.iif} files, where the \texttt{*.iif} files are for the so-called alignment scans).

All the recorded projection images were subsequently reconstructed into a 3D stack of axial images spanning the regions of interest of each fish.
All the specimens were scanned with their mouths facing downward in the sample holder and rotating along their long axis.
We thus manually aligned each of the reconstructed datasets so that the lateral axis of the fish was horizontal in relation to the x and y direction of the reconstructed slices.
We reconstructed the projection images with NRecon (Version 1.7.4.6, Bruker microCT, Kontich Belgium) with varying ring artifact and beam hardening correction values, depending on each fish (again, all relevant values are listed in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}).
In total, this resulted in 1.4 TB of reconstruction images (nearly one million \texttt{*rec*.png} files).
Each of the 362 scans we performed has on average about 2700 reconstruction images.

While performing the work, a subset of the data was always present on the production system, for working with it (see \protect\hyperlink{preparation-for-analysis}{Preparation for analysis} below).
A small bash script {[}\protect\hyperlink{ref-ZjgrPHTa}{10}{]} was used to generate redundant (archival) copies of the raw projection images and copy all the files to a shared network drive on the \texttt{Research\ Storage} infrastructure of the University of Bern, enabling easy collaboration on the data by all authorized persons at the same time.

\hypertarget{data-analysis}{%
\subsubsection{Data analysis}\label{data-analysis}}

We wrote a set of \emph{Jupyter} {[}\protect\hyperlink{ref-pQ6Wbz73}{11}{]} notebooks with \emph{Python} code to work with the images and wrangle the acquired data.
The notebooks were written at the start of the project, to be able to process new scans as soon as they were reconstructed.
Re-runs of the notebook added newly scanned and reconstructed fishes to the analysis, facilitating an efficient quality check of the scans and batched processing of the data.

All analysis notebooks for this work are available online {[}\protect\hyperlink{ref-1HteOscVd}{12}{]}.

\hypertarget{preparation-for-analysis}{%
\paragraph{Preparation for analysis}\label{preparation-for-analysis}}

The \href{https//github.com/habi/EAWAG/blob/master/DisplayFishes.ipynb}{main Jupyter notebook} for this manuscript dealt with reading all log and image files and preparing images for quality checking and further analysis.
Briefly summarized the below process was implemented.

At first, \emph{all} log files of \emph{all} the data present in the processed folder were read into a \emph{pandas} {[}\protect\hyperlink{ref-19qQOHlFN}{13}{]} dataframe.
This already enabled us to extract the specimen name and scan, since we performed several scans for each specimen, i.e.~a low resolution scan with large field of view for the whole head and one or several scans in high resolution focusing on the oral and pharyngeal jaws.
From the log files we extracted the relevant values for double-checking the necessary parameters of each scan.
All relevant values for each scan were also saved into the dataframe and saved out to the aforementioned table in the \protect\hyperlink{supplementary-materials}{Supplementary Materials} at the end of each run of the notebook.

After several `sanity checks' of the data, we used \emph{Dask} {[}\protect\hyperlink{ref-hj1CnyWB}{14}{]} to efficiently access the very large total amount of axial reconstructions for this project (in the end amounting to a total of nearly a million single images).
On average, each of the tomographic datasets contains around 2700 slices, so the total amount of data is much too large to keep in memory.
The use of the Dask library facilitated efficient access to the huge amount of data on disk.

At first, we extracted the central view of each of the three axial directions of the datasets (i.e.~`anteroposterior', `lateral' and `dorsoventral' view) and either saved those to disk or loaded them from disk if they were already generated in prior runs of the notebook.
The notebook then also generated the maximum intensity projection (MIP) for each of the anatomical planes and either saved them to disk or loaded them from prior runs.

At the end of the notebook we performed a final sanity check on the MIP images.
In this check we examined the mapping of the gray values of the raw projection images to gray values in the reconstructions, i.e.~checked that no overexposed pixels are present in the MIP images.
This is an efficient way for double-checking the gray value mapping, since the MIP images have already been generated in prior steps of the notebook and contain the highest gray values present in all the reconstructed images of each scan.

\hypertarget{image-processing}{%
\subsubsection{Image processing}\label{image-processing}}

\hypertarget{extraction-of-oral-and-pharyngeal-jaws-visualization-of-tomographic-data}{%
\paragraph{Extraction of oral and pharyngeal jaws, visualization of tomographic data}\label{extraction-of-oral-and-pharyngeal-jaws-visualization-of-tomographic-data}}

To extract the oral jaw (OJ) and pharyngeal jaw (PJ) of the fishes, we used \href{https://www.slicer.org}{3DSlicer} (Version 4.11.20210226) {[}\protect\hyperlink{ref-OsCpHsJH}{15}{]} extended with the \emph{SlicerMorph} tools {[}\protect\hyperlink{ref-MwdN6kPV}{16}{]} which aim to help biologists work with 3D specimen data.
The reconstructed PNG stacks were loaded into \emph{ImageStacks}, depending on their size we reduced the image resolution (i.e.~downscaled the images) for this first step.
The three-dimensional volume was rendered via \href{https://slicer.readthedocs.io/en/latest/user_guide/modules/volumerendering.html}{\emph{VTK GPU Ray Casting}}.
A custom-made volume property was used as an input to view the scans.
Using toggles in the volume rendering, we defined regions of interest (ROIs) for both the OJs and PJs in each specimen.
These ROIs were then extracted in their native resolution from the original dataset for further processing.
Using the gray value thresholding function in 3DSlicer's \href{https://slicer.readthedocs.io/en/latest/user_guide/modules/segmenteditor.html}{\emph{Segment Editor}}, the teeth in both the oral and pharyngeal jaws were extracted.
We used the \emph{Scissor} and \emph{Island} tools of the Segment Editor to isolate single regions.

Processed regions of interest were exported as NRRD {[}\protect\hyperlink{ref-12B4h087w}{17}{]} files.
The three-dimensional visualizations of all regions of interest for each specimen were compiled into overview images (see Figure \ref{fig:104016} for an example from the compilation document).
In total we compiled overview of 125 specimens with full head morphology, oral jaw and lower pharyngeal jaw profiles.

\begin{figure}
\hypertarget{fig:104016}{%
\centering
\includegraphics{images/104016.png}
\caption{Overview of data from sample 104016,~\emph{Enterochromis I cinctus} (St.~E)}\label{fig:104016}
}
\end{figure}

\hypertarget{principal-component-analysis-of-skull-landmarks}{%
\paragraph{Principal component analysis of skull landmarks}\label{principal-component-analysis-of-skull-landmarks}}

Current studies are using 3D geometric morphometrics to compare the morphological shape of these scanned cichlids using statistical analysis.
A homologous landmark scheme was produced {[}\protect\hyperlink{ref-BDrCSu8p}{6},\protect\hyperlink{ref-15FafMZm5}{18}{]}, and landmarks were placed on each specimen using 3DSlicer.
To examine differences in shape across the species sampled, we performed a Generalized Procrustes Superimposition on the landmark data to remove the effects of location, size, and rotation from the analysis using the \emph{geomorph} package in \emph{R} (Version 4.2.1) with \emph{RStudio} (Version 2022.07.2+576) {[}\protect\hyperlink{ref-VPUOQA2P}{19},\protect\hyperlink{ref-Ziptbtib}{20},\protect\hyperlink{ref-EwNL0C0Y}{21},\protect\hyperlink{ref-whEyWyQh}{22},\protect\hyperlink{ref-QfVloFVu}{23}{]}.
This process brings all specimens to a common origin, scales the landmarks to a unit centroid size, and rotates specimens to reduce distances between landmarks.
A principal component analysis was then performed on the superimposed landmark data to visualize the major axes of shape change across sampled species.
We then used phylogenetic information to identify instances of repeated evolution of trophic adaptations in these cichlids.

\hypertarget{automatic-extraction-of-otoliths}{%
\paragraph{Automatic extraction of otoliths}\label{automatic-extraction-of-otoliths}}

Otoliths are structures made up of mostly calcium carbonate located in the head of fishes.
Due to their composition they show up nicely on the X-ray images we acquired.
We devised a very robust image processing method to automatically detect the location of the otoliths in the heads of the fishes and extract them from the original data.
The whole method is implemented in its own \href{https://github.com/habi/EAWAG/blob/master/ExtractOtoliths.ipynb}{Jupyter notebook} (part of the aforementioned analysis repository {[}\protect\hyperlink{ref-1HteOscVd}{12}{]}) and is briefly explained below.
The notebook performing the otolith extraction can be run without installation of any software in a web browser, thanks to the help of Binder {[}\protect\hyperlink{ref-Q20Bxdsr}{24}{]}; to do this, one can start the notebook \href{https://mybinder.org/v2/gh/habi/EAWAG/HEAD?labpath=ExtractOtoliths.ipynb}{here}.

Since we took great care to scan the fishes parallel to their \emph{anteroposterior} direction and reconstructed the tomographic datasets parallel to the \emph{lateral} and \emph{dorsoventral} direction of the fishes we could use this `preparation' for automatically extracting the otoliths in scans of the full heads of the fishes.
By extracting both the peaks and the peak widths of the gray values along both the horizontal and vertical direction of the MIP (generated above) we robustly detected the position of the otoliths in the datasets.
The robust detection is supported by suppressing a small, configurable part of each region, i.e.~the front and back, top and bottom or the flanks.

\begin{figure}
\hypertarget{fig:otolithextraction}{%
\centering
\includegraphics{images/104016.head.rec.otolither.position.png}
\caption{Visualization of automatic otolith extraction. The top row shows the found location of the otolith center in each of the three anatomical directions. The bottom row shows a MIP of each of the three anatomical directions of the extracted otolith region.}\label{fig:otolithextraction}
}
\end{figure}

Figure \ref{fig:otolithextraction} shows the visualization of the process.
The colored horizontal and vertical bars in each of the directional MIPs denote the found peak location of the two appropriate values.
The white bars show the mean of the to detected positions, which was used for extracting the otoliths from the original datasets.
Making use of the \texttt{dask} library facilitated efficient access to all the data on disk and writing out small, cropped copies of the datasets around the otolith positions.

By detecting the largest components in the cropped copies of the datasets we can easily extract and visualize the otoliths in 3D, as shown in Figure \ref{fig:otolith3d}.
The extracted otoliths are thus prepared for further analysis and display.
The simple three-dimensional visualization is integrated in the aforementiones Jupyter notebook through an integrated visualization library {[}\protect\hyperlink{ref-a9ZL41Of}{25}{]} and is also shown in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}.

\begin{figure}
\hypertarget{fig:otolith3d}{%
\centering
\includegraphics{images/104016.head.rec.otolith.region.3D.png}
\caption{Static three-dimensional view of extracted otolith of specimen 104016. The specimen was scanned with a voxel size of 13 μm. The extracted otolith has a size of approximately 250 x 350 x 150 pixels. The axes are labeled in mm steps. A dynamic view of the visualization is available in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}.}\label{fig:otolith3d}
}
\end{figure}

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

We acquired high resolution tomographic datasets of a large collection of Cichlids.
The acquired datasets were imaged over a wide-spanning range of voxel size (3.5--50 μm) permitting both the analysis of finest details we wanted to resolve (i.e.~the structure of the teeth) and having datasets spanning the whole region of interest of the fishes (i.e.~the whole head for principle component analysis)

\hypertarget{imaging-and-preparation-for-analysis}{%
\subsubsection{Imaging and preparation for analysis}\label{imaging-and-preparation-for-analysis}}

The whole study we presented here spanned a \emph{long} time frame.
It was thus paramount to make the imaging process and preparation of the tomographic datasets able to run in batch-mode.
The Jupyter notebook written to prepare the datasets for quality control and analysis were facilitating a short turnaround time for feedback on single scans.

\hypertarget{otolith-extraction}{%
\subsubsection{Otolith extraction}\label{otolith-extraction}}

The method to extract the otoliths of the fishes from the tomographic dataset works robustly for all of the different fish sizes and shapes.
The extraction is robust because it is based on a combination of several intricate details of the gray value curve over the different anatomical directions.
The details of the otolith extraction method have been tuned extensively by us and it now runs completely automatically, allowing for highly reproducible and completely unbiased extraction of the otoliths from the tomographic datasets.
This is even the case for one fish which was scanned with still a hook in his mouth, where the otolihts were nonetheless extracted automatically.

Data on such automatically extracted otoliths, like volume and geometric information like eccentricity and moments of inertia could be biologically really interesting as the otoliths grow with the age of the fish.
However, one would first have to calibrate the data on the otolits length or volume with otoliths of fish of known age but this could help to estimate the age of wild fishes.
Estimation of age of tropical fishes is not as simple as for fishes from temperate regions where one can distinguish summer and winter layers within the otolith.

\hypertarget{outlook}{%
\subsubsection{Outlook}\label{outlook}}

The acquired tomographic datasets are the basis for several additional analysis of fish morphology.

The presented method offers an insight and algorithm on how to perform tomographic scans, preview and analyze micro-computer tomographic datasets of a large collection of fishes.
The workflow is relying only on free and open-source software and can thus be used and verified independently by any interested reader.
All the Jupyter notebook described herein is also freely available online {[}\protect\hyperlink{ref-1HteOscVd}{12}{]}.

\hypertarget{acknowledgments}{%
\subsection{Acknowledgments}\label{acknowledgments}}

We thank Salome Mwaiko for taking care of the fish collection at EAWAG and Mark Charran for helping to find suitable specimens to represent each species.
We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{26}{]} for helping us write this manuscript collaboratively.

\hypertarget{supplementary-materials}{%
\subsection{Supplementary Materials}\label{supplementary-materials}}

\hypertarget{parameters-of-tomographic-scans-of-all-the-fishes}{%
\subsubsection{Parameters of tomographic scans of all the fishes}\label{parameters-of-tomographic-scans-of-all-the-fishes}}

The CSV file \href{https://github.com/habi/EAWAG-manuscript/blob/main/content/data/ScanningDetails.csv}{ScanningDetails.csv} gives a tabular overview of all the (relevant) parameters of all the scans we performed.
This file was generated with the \href{https://github.com/habi/EAWAG/blob/master/DataWrangling.ipynb}{data processing notebook} and contains the data which is read from \emph{all} the log files of \emph{all} the scans we performed.
A copy of each log file is available in a \href{https://github.com/habi/EAWAG/tree/master/logfiles}{folder in the data processing repository}.

\hypertarget{three-dimensional-view-of-one-of-the-extracted-otoliths}{%
\subsubsection{\texorpdfstring{Three-dimensional view of \emph{one} of the extracted otoliths}{Three-dimensional view of one of the extracted otoliths}}\label{three-dimensional-view-of-one-of-the-extracted-otoliths}}

The three-dimensional view of sample 104016 was generated in \href{https://github.com/habi/EAWAG/blob/master/ExtractOtoliths.ipynb}{the otolith extraction notebook} and saved as \href{https://github.com/habi/EAWAG-manuscript/blob/main/content/data/104016.head.rec.otolith.region.3D.html}{104016.head.rec.otolith.region.3D.html} file.
A fully functional copy can be viewed through the \href{https://htmlpreview.github.io/?https://github.com/habi/EAWAG-manuscript/blob/main/content/data/104016.head.rec.otolith.region.3D.html}{GitHub HTML preview}.

\hypertarget{references}{%
\subsection{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-TUQFenhc}{}}%
\CSLLeftMargin{1. }
\CSLRightInline{\textbf{Adaptive evolution and explosive speciation: the cichlid fish model}
\CSLBlock{Thomas D Kocher} \emph{Nature Reviews Genetics} (2004-04-01) \url{https://doi.org/dkgf93}
\CSLBlock{DOI: \href{https://doi.org/10.1038/nrg1316}{10.1038/nrg1316} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/15131652}{15131652}}}

\leavevmode\vadjust pre{\hypertarget{ref-W2f2SDjn}{}}%
\CSLLeftMargin{2. }
\CSLRightInline{\textbf{African cichlid fish: a model system in adaptive radiation research}
\CSLBlock{Ole Seehausen} \emph{Proceedings of the Royal Society B: Biological Sciences} (2006-05-09) \url{https://doi.org/frrhbq}
\CSLBlock{DOI: \href{https://doi.org/10.1098/rspb.2006.3539}{10.1098/rspb.2006.3539} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/16846905}{16846905} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1635482}{PMC1635482}}}

\leavevmode\vadjust pre{\hypertarget{ref-1GEljkDsf}{}}%
\CSLLeftMargin{3. }
\CSLRightInline{\textbf{Evolutionary Strategies and Morphological Innovations: Cichlid Pharyngeal Jaws}
\CSLBlock{Karel F Liem} \emph{Systematic Zoology} (1973-12) \url{https://doi.org/b969fp}
\CSLBlock{DOI: \href{https://doi.org/10.2307/2412950}{10.2307/2412950}}}

\leavevmode\vadjust pre{\hypertarget{ref-c3poTogo}{}}%
\CSLLeftMargin{4. }
\CSLRightInline{\textbf{Process and pattern in cichlid radiations -- inferences for understanding unusually high rates of evolutionary diversification}
\CSLBlock{Ole Seehausen} \emph{New Phytologist} (2015-05-13) \url{https://doi.org/f7gczg}
\CSLBlock{DOI: \href{https://doi.org/10.1111/nph.13450}{10.1111/nph.13450} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/25983053}{25983053}}}

\leavevmode\vadjust pre{\hypertarget{ref-8Pmc2mI8}{}}%
\CSLLeftMargin{5. }
\CSLRightInline{\textbf{Adaptation mechanism of the adult zebrafish respiratory organ to endurance training}
\CSLBlock{Matthias Messerli, Dea Aaldijk, David Haberthür, Helena Röss, Carolina García-Poyatos, Marcos Sande-Melón, Oleksiy-Zakhar Khoma, Fluri AM Wieland, Sarya Fark, Valentin Djonov} \emph{PLOS ONE} (2020-02-05) \url{https://doi.org/grf6fj}
\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pone.0228333}{10.1371/journal.pone.0228333} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/32023296}{32023296} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7001924}{PMC7001924}}}

\leavevmode\vadjust pre{\hypertarget{ref-BDrCSu8p}{}}%
\CSLLeftMargin{6. }
\CSLRightInline{\textbf{Convergence is Only Skin Deep: Craniofacial Evolution in Electric Fishes from South America and Africa (Apteronotidae and Mormyridae)}
\CSLBlock{Kassandra L Ford, Rose Peterson, Maxwell Bernt, James S Albert} \emph{Integrative Organismal Biology} (2022) \url{https://doi.org/gq3gtc}
\CSLBlock{DOI: \href{https://doi.org/10.1093/iob/obac022}{10.1093/iob/obac022} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/35976714}{35976714} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC9375771}{PMC9375771}}}

\leavevmode\vadjust pre{\hypertarget{ref-3rxGCEvJ}{}}%
\CSLLeftMargin{7. }
\CSLRightInline{\url{https://osf.io/ecmz4}}

\leavevmode\vadjust pre{\hypertarget{ref-VCZPOv2f}{}}%
\CSLLeftMargin{8. }
\CSLRightInline{\textbf{OpenSCAD models}
\CSLBlock{TomoGraphics} (2022-02-28) \url{https://github.com/TomoGraphics/Hol3Drs/blob/dedca665a77fa782c103eed63b866b2cceb30de9/STL/EAWAG.Fish.stl}}

\leavevmode\vadjust pre{\hypertarget{ref-115PPSuQp}{}}%
\CSLLeftMargin{9. }
\CSLRightInline{\textbf{TomoGraphics/Hol3Drs: A release}
\CSLBlock{David Haberthür} \emph{Zenodo} (2019-03-08) \url{https://doi.org/gg9fxh}
\CSLBlock{DOI: \href{https://doi.org/10.5281/zenodo.2587555}{10.5281/zenodo.2587555}}}

\leavevmode\vadjust pre{\hypertarget{ref-ZjgrPHTa}{}}%
\CSLLeftMargin{10. }
\CSLRightInline{\textbf{Jupyter notebooks for image processing and data analysis of EAWAG Cichlids project}
\CSLBlock{David Haberthür} (2022-07-05) \url{https://github.com/habi/EAWAG/blob/1f81f8138c49ac5d111288d8b28a0f81c222cca5/rsync-fishes.sh}}

\leavevmode\vadjust pre{\hypertarget{ref-pQ6Wbz73}{}}%
\CSLLeftMargin{11. }
\CSLRightInline{\textbf{Jupyter Notebooks -- a publishing format for reproducible computational workflows}
\CSLBlock{Thomas Kluyver, Benjamin Ragan-Kelley, Fernando Pérez, Brian Granger, Matthias Bussonnier, Jonathan Frederic, Kyle Kelley, Jessica Hamrick, Jason Grout, Sylvain Corlay, \ldots{} Jupyter development team} \emph{IOS Press} (2016) \url{https://eprints.soton.ac.uk/403913/}
\CSLBlock{DOI: \href{https://doi.org/10.3233/978-1-61499-649-1-87}{10.3233/978-1-61499-649-1-87}}}

\leavevmode\vadjust pre{\hypertarget{ref-1HteOscVd}{}}%
\CSLLeftMargin{12. }
\CSLRightInline{\textbf{habi/EAWAG: First release, for minting a Zenodo DOI}
\CSLBlock{David Haberthür} \emph{Zenodo} (2022-07-05) \url{https://doi.org/gqgdtp}
\CSLBlock{DOI: \href{https://doi.org/10.5281/zenodo.6798632}{10.5281/zenodo.6798632}}}

\leavevmode\vadjust pre{\hypertarget{ref-19qQOHlFN}{}}%
\CSLLeftMargin{13. }
\CSLRightInline{\textbf{pandas-dev/pandas: Pandas}
\CSLBlock{The Pandas Development Team} \emph{Zenodo} (2022-09-19) \url{https://doi.org/gqw4db}
\CSLBlock{DOI: \href{https://doi.org/10.5281/zenodo.7093122}{10.5281/zenodo.7093122}}}

\leavevmode\vadjust pre{\hypertarget{ref-hj1CnyWB}{}}%
\CSLLeftMargin{14. }
\CSLRightInline{\textbf{Dask: Library for dynamic task scheduling}
\CSLBlock{Dask Development Team} (2016) \url{https://dask.org}}

\leavevmode\vadjust pre{\hypertarget{ref-OsCpHsJH}{}}%
\CSLLeftMargin{15. }
\CSLRightInline{\textbf{3D Slicer as an image computing platform for the Quantitative Imaging Network}
\CSLBlock{Andriy Fedorov, Reinhard Beichel, Jayashree Kalpathy-Cramer, Julien Finet, Jean-Christophe Fillion-Robin, Sonia Pujol, Christian Bauer, Dominique Jennings, Fiona Fennessy, Milan Sonka, \ldots{} Ron Kikinis} \emph{Magnetic Resonance Imaging} (2012-11) \url{https://doi.org/gfghgd}
\CSLBlock{DOI: \href{https://doi.org/10.1016/j.mri.2012.05.001}{10.1016/j.mri.2012.05.001} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/22770690}{22770690} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3466397}{PMC3466397}}}

\leavevmode\vadjust pre{\hypertarget{ref-MwdN6kPV}{}}%
\CSLLeftMargin{16. }
\CSLRightInline{\textbf{SlicerMorph: An open and extensible platform to retrieve, visualize and analyse 3D morphology}
\CSLBlock{Sara Rolfe, Steve Pieper, Arthur Porto, Kelly Diamond, Julie Winchester, Shan Shan, Henry Kirveslahti, Doug Boyer, Adam Summers, AMurat Maga} \emph{Methods in Ecology and Evolution} (2021-07-22) \url{https://doi.org/gqtgv8}
\CSLBlock{DOI: \href{https://doi.org/10.1111/2041-210x.13669}{10.1111/2041-210x.13669}}}

\leavevmode\vadjust pre{\hypertarget{ref-12B4h087w}{}}%
\CSLLeftMargin{17. }
\CSLRightInline{\url{https://w.wiki/5mBK}}

\leavevmode\vadjust pre{\hypertarget{ref-15FafMZm5}{}}%
\CSLLeftMargin{18. }
\CSLRightInline{\textbf{Mosaic Evolution of Craniofacial Morphologies in Ghost Electric Fishes (Gymnotiformes: Apteronotidae)}
\CSLBlock{Kassandra L Ford, Maxwell J Bernt, Adam P Summers, James S Albert} \emph{Ichthyology \&amp; Herpetology} (2022-05-27) \url{https://doi.org/gq3gtd}
\CSLBlock{DOI: \href{https://doi.org/10.1643/i2021016}{10.1643/i2021016}}}

\leavevmode\vadjust pre{\hypertarget{ref-VPUOQA2P}{}}%
\CSLLeftMargin{19. }
\CSLRightInline{\textbf{RRPP: An
\textless scp\textgreater r\textless/scp\textgreater{}
package for fitting linear models to high‐dimensional data using residual randomization}
\CSLBlock{Michael L Collyer, Dean C Adams} \emph{Methods in Ecology and Evolution} (2018-05-29) \url{https://doi.org/gdwp9q}
\CSLBlock{DOI: \href{https://doi.org/10.1111/2041-210x.13029}{10.1111/2041-210x.13029}}}

\leavevmode\vadjust pre{\hypertarget{ref-Ziptbtib}{}}%
\CSLLeftMargin{20. }
\CSLRightInline{\textbf{Geomorph: Software for geometric morphometric analyses. R package version 4.0.4}
\CSLBlock{DC Adams, ML Collyer, A Kaliontzopoulou, EK Baken} (2022)\href{\%20https://cran.r-project.org/package=geomorph}{ https://cran.r-project.org/package=geomorph}}

\leavevmode\vadjust pre{\hypertarget{ref-EwNL0C0Y}{}}%
\CSLLeftMargin{21. }
\CSLRightInline{\textbf{RRPP: Linear model evaluation with randomized residuals in a permutation procedure, r package version 0.6.2.}
\CSLBlock{ML Collyer, DC Adams} (2021) \url{https://cran.r-project.org/package=RRPP}}

\leavevmode\vadjust pre{\hypertarget{ref-whEyWyQh}{}}%
\CSLLeftMargin{22. }
\CSLRightInline{\textbf{R: A language and environment for statistical computing}
\CSLBlock{R Core Team} \emph{R Foundation for Statistical Computing} (2018) \url{https://www.R-project.org/}}

\leavevmode\vadjust pre{\hypertarget{ref-QfVloFVu}{}}%
\CSLLeftMargin{23. }
\CSLRightInline{\textbf{RStudio: Integrated development environment for r}
\CSLBlock{RStudio Team} \emph{RStudio, PBC.} (2022) \url{https://www.rstudio.com/}}

\leavevmode\vadjust pre{\hypertarget{ref-Q20Bxdsr}{}}%
\CSLLeftMargin{24. }
\CSLRightInline{\textbf{Binder 2.0 - Reproducible, interactive, sharable environments for science at scale}
\CSLBlock{Project Jupyter, Matthias Bussonnier, Jessica Forde, Jeremy Freeman, Brian Granger, Tim Head, Chris Holdgraf, Kyle Kelley, Gladys Nalvarte, Andrew Osheroff, \ldots{} Carol Willing} \emph{Proceedings of the Python in Science Conference} (2018) \url{https://doi.org/gfwcm6}
\CSLBlock{DOI: \href{https://doi.org/10.25080/majora-4af1f417-011}{10.25080/majora-4af1f417-011}}}

\leavevmode\vadjust pre{\hypertarget{ref-a9ZL41Of}{}}%
\CSLLeftMargin{25. }
\CSLRightInline{\textbf{K3D Jupyter}
\CSLBlock{K3D-tools} (2023-02-28) \url{https://github.com/K3D-tools/K3D-jupyter}}

\leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
\CSLLeftMargin{26. }
\CSLRightInline{\textbf{Open collaborative writing with Manubot}
\CSLBlock{Daniel S Himmelstein, Vincent Rubinetti, David R Slochower, Dongbo Hu, Venkat S Malladi, Casey S Greene, Anthony Gitter} \emph{PLOS Computational Biology} (2019-06-24) \url{https://doi.org/c7np}
\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pcbi.1007128}{10.1371/journal.pcbi.1007128} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31233491}{31233491} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6611653}{PMC6611653}}}

\end{CSLReferences}

### 2023-03-03 content/images/104016.tex
Rename file, update it to feature subfigures

\documentclass[tikz]{standalone}
\usepackage{tikz}			% for drawing everything
	\usetikzlibrary{spy}	% for zooming
\usepackage{siunitx}		% for nice SI units
\usepackage{shadowtext}	    % for shadowed text on the scalebar
	\shadowoffset{1pt}	    % ideally the same as on line 13...
	\shadowcolor{black}	    % ideally the same as on line 13...
\newcommand{\imsize}{\linewidth}% default width of image
\newlength\imagewidth% needed for correct scalebar
\newlength\imagescale% needed for correct scalebar
\begin{document}%
%----------
\tikzset{shadowed/.style={preaction={transform canvas={shift={(1pt,-1pt)}},draw=black, thick}}} % shadowed drawing https://tex.stackexchange.com/a/185853/828
\pgfmathsetlength{\imagewidth}{\imsize}%
\pgfmathsetlength{\imagescale}{\imagewidth/4000}%
\def\x{1203}% scalebar-x starting at golden ratio of image width of 4000px = 2472
\def\y{2025}% scalebar-y at 90% of image height of 2250px = 2025
\def\mag{4}% magnification of inset
\def\size{75}% size of inset
\begin{tikzpicture}[x=\imagescale,y=-\imagescale,spy using outlines={rectangle,magnification=\mag,size=\size,connect spies}]
	\begin{scope}
		\clip (0,0) rectangle (4000,2250);
		%\clip (2000.0,1125.0) circle (1125.0);
		\node[anchor=north west, inner sep=0pt, outer sep=0pt] at (0,0) {\includegraphics[width=\imagewidth]{104016}};
	\end{scope}
	%\spy [red] on (3700,1950) in node at (0,0) [anchor=north west];
	% 1424.464px = 70.0mm -> 100px = 4914.129um -> 10.175px = 500um, 2.035px = 100um
	\draw[|-|,blue,thick] (105,1743) -- (1530,1756) node [sloped,midway,above,fill=white,semitransparent,text opacity=1] {\SI{70.0}{\milli\meter} (1424px) TEMPORARY!};
	\draw[|-|,white,thick,shadowed] (\x,\y) -- (\x+101.75,\y) node [midway,above] {\shadowtext{\SI{5}{\milli\meter}}};
	%\draw[color=red, anchor=south west] (0,2250) node [fill=white, semitransparent] {Legend} node {Legend};
\end{tikzpicture}%
%----------
\end{document}%

### 2023-03-03 v/7bd8c31493192617f748e772ce955747e94883e2/images/104016/pj_top_scalebar.tex
Add scale bar of top view of PJ [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/7bd8c31493192617f748e772ce955747e94883e2.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/7bd8c31493192617f748e772ce955747e94883e2/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/4323400131

\documentclass[tikz]{standalone}
\usepackage{tikz}			% for drawing everything
	\usetikzlibrary{spy}	% for zooming
\usepackage{siunitx}		% for nice SI units
\usepackage{shadowtext}	% for shadowed text on the scalebar
	\shadowoffset{1pt}	% ideally the same as on line 13...
	\shadowcolor{green}	% ideally the same as on line 13...
\newcommand{\imsize}{\linewidth}% default width of image
\newlength\imagewidth% needed for correct scalebar
\newlength\imagescale% needed for correct scalebar
\begin{document}%
%----------
\tikzset{shadowed/.style={preaction={transform canvas={shift={(1pt,-1pt)}},draw=green, thick}}} % shadowed drawing https://tex.stackexchange.com/a/185853/828
\pgfmathsetlength{\imagewidth}{\imsize}%
\pgfmathsetlength{\imagescale}{\imagewidth/710}%
\def\x{439}% scalebar-x starting at golden ratio of image width of 710px = 439
\def\y{629}% scalebar-y at 90% of image height of 699px = 629
\def\mag{4}% magnification of inset
\def\size{75}% size of inset
\begin{tikzpicture}[x=\imagescale,y=-\imagescale,spy using outlines={rectangle,magnification=\mag,size=\size,connect spies}]
	\begin{scope}
		\clip (0,0) rectangle (710,699);
		%\clip (355.0,349.5) circle (349.5);
		\node[anchor=north west, inner sep=0pt, outer sep=0pt] at (0,0) {\includegraphics[width=\imagewidth]{pj_top}};
	\end{scope}
	%\spy [red] on (410,399) in node at (0,0) [anchor=north west];
	% 762.062px = 5.475mm -> 100px = 718.446um -> 69.595px = 500um, 13.919px = 100um
	\draw[|-|,blue,thick] (692,8) -- (362,696) node [sloped,midway,above,fill=white,semitransparent,text opacity=1] {\SI{5.475}{\milli\meter} (762px) TEMPORARY!};
	\draw[|-|,white,thick,shadowed] (\x,\y) -- (\x+69.595,\y) node [midway,above] {\shadowtext{\SI{500}{\micro\meter}}};
	%\draw[color=red, anchor=south west] (0,699) node [fill=white, semitransparent] {Legend} node {Legend};
\end{tikzpicture}%
%----------
\end{document}%

### 2023-03-03 v/401e10fd5dafceb54fd6b33a37b7c721ffce1eb8/images/104016/oj_scalebar.tex
Remove wrongly/forcibly added files [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/401e10fd5dafceb54fd6b33a37b7c721ffce1eb8.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/401e10fd5dafceb54fd6b33a37b7c721ffce1eb8/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/4323430327

--- 2023-03-03 v/7bd8c31493192617f748e772ce955747e94883e2/images/104016/pj_top_scalebar.tex
@@
 \pgfmathsetlength{\imagewidth}{\imsize}%
-\pgfmathsetlength{\imagescale}{\imagewidth/710}%
-\def\x{439}% scalebar-x starting at golden ratio of image width of 710px = 439
-\def\y{629}% scalebar-y at 90% of image height of 699px = 629
+\pgfmathsetlength{\imagescale}{\imagewidth/1153}%
+\def\x{713}% scalebar-x starting at golden ratio of image width of 1153px = 713
+\def\y{734}% scalebar-y at 90% of image height of 815px = 734
 \def\mag{4}% magnification of inset
@@
 	\begin{scope}
-		\clip (0,0) rectangle (710,699);
-		%\clip (355.0,349.5) circle (349.5);
-		\node[anchor=north west, inner sep=0pt, outer sep=0pt] at (0,0) {\includegraphics[width=\imagewidth]{pj_top}};
+		\clip (0,0) rectangle (1153,815);
+		%\clip (576.5,407.5) circle (407.5);
+		\node[anchor=north west, inner sep=0pt, outer sep=0pt] at (0,0) {\includegraphics[width=\imagewidth]{oj}};
 	\end{scope}
-	%\spy [red] on (410,399) in node at (0,0) [anchor=north west];
-	% 762.062px = 5.475mm -> 100px = 718.446um -> 69.595px = 500um, 13.919px = 100um
-	\draw[|-|,blue,thick] (692,8) -- (362,696) node [sloped,midway,above,fill=white,semitransparent,text opacity=1] {\SI{5.475}{\milli\meter} (762px) TEMPORARY!};
-	\draw[|-|,white,thick,shadowed] (\x,\y) -- (\x+69.595,\y) node [midway,above] {\shadowtext{\SI{500}{\micro\meter}}};
-	%\draw[color=red, anchor=south west] (0,699) node [fill=white, semitransparent] {Legend} node {Legend};
+	%\spy [red] on (853,515) in node at (0,0) [anchor=north west];
+	% 200.664px = 0.865mm -> 100px = 431.069um -> 115.991px = 500um, 23.198px = 100um
+	\draw[|-|,blue,thick] (533,336) -- (533,536) node [sloped,midway,above,fill=white,semitransparent,text opacity=1] {\SI{0.865}{\milli\meter} (201px) TEMPORARY!};
+	\draw[|-|,white,thick,shadowed] (\x,\y) -- (\x+115.991,\y) node [midway,above] {\shadowtext{\SI{500}{\micro\meter}}};
+	%\draw[color=red, anchor=south west] (0,815) node [fill=white, semitransparent] {Legend} node {Legend};
 \end{tikzpicture}%

### 2023-03-09 images/104016/oj_scalebar.tex
Proper scalebars for Fig. 1, updated caption [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/7be560a8b59bc90da05290dfe08206d89c8c0922.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/7be560a8b59bc90da05290dfe08206d89c8c0922/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/4375801155

--- 2023-03-03 v/401e10fd5dafceb54fd6b33a37b7c721ffce1eb8/images/104016/oj_scalebar.tex
@@
 	%\spy [red] on (853,515) in node at (0,0) [anchor=north west];
-	% 200.664px = 0.865mm -> 100px = 431.069um -> 115.991px = 500um, 23.198px = 100um
-	\draw[|-|,blue,thick] (533,336) -- (533,536) node [sloped,midway,above,fill=white,semitransparent,text opacity=1] {\SI{0.865}{\milli\meter} (201px) TEMPORARY!};
-	\draw[|-|,white,thick,shadowed] (\x,\y) -- (\x+115.991,\y) node [midway,above] {\shadowtext{\SI{500}{\micro\meter}}};
+	% 834.069px = 3.24mm -> 100px = 388.457um -> 128.714px = 500um, 25.743px = 100um
+	\draw[|-|,blue,thick] (144,627) -- (978,594) node [sloped,midway,above,fill=white,semitransparent,text opacity=1] {\SI{3.24}{\milli\meter} (834px) TEMPORARY!};
+	\draw[|-|,white,thick,shadowed] (\x,\y) -- (\x+128.714,\y) node [midway,above] {\shadowtext{\SI{500}{\micro\meter}}};
 	%\draw[color=red, anchor=south west] (0,815) node [fill=white, semitransparent] {Legend} node {Legend};

### 2023-03-09 v/latest/images/104016.tex
Proper scalebars for Fig. 1, updated caption [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/7be560a8b59bc90da05290dfe08206d89c8c0922.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/7be560a8b59bc90da05290dfe08206d89c8c0922/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/4375801155

\documentclass[varwidth]{standalone} % varwidth because of https://tex.stackexchange.com/a/622526/828
\usepackage{subcaption}	% for concatenating images
\usepackage{tikz}				% for drawing everything
\usepackage{siunitx}			% for nice SI units
\newcommand{\imsize}{\linewidth}	% default width of image
\newlength\imagewidth		% needed for correct scalebar
\newlength\imagescale		% needed for correct scalebar
\pgfmathsetlength{\imagewidth}{\imsize}%
\begin{document}
\pagecolor{black}% all black page, to discard the differently sized images
\begin{figure}%
	\begin{subfigure}[c]{0.5\linewidth}%
		\pgfmathsetlength{\imagewidth}{\imsize}%
		\pgfmathsetlength{\imagescale}{\imagewidth/609}%
		\def\x{37.6}% scalebar-x starting at golden ratio of image width of 609px = 376
		\def\y{456}% scalebar-y at 90% of image height of 480px = 432
		\begin{tikzpicture}[x=\imagescale,y=-\imagescale]%
			\node[anchor=north west, inner sep=0pt, outer sep=0pt] at (0,0) {\includegraphics[width=\imagewidth]{104016/head}};
			% 475.587px = 18.486mm -> 100px = 3886.984um -> 12.863px = 500um, 2.573px = 100um
			%\draw[|-|,blue] (5,362) -- (340,25) node [sloped,midway,above,fill=white,semitransparent,text opacity=1] {\SI{18.486}{\milli\meter} (476px)};
			\draw[|-|,white] (\x,\y) -- (\x+128.63,\y) node [right] {\SI{5}{\milli\meter}};
			\draw[color=black, anchor=north west] (0,0) node [fill=white, semitransparent] {A} node {A};
		\end{tikzpicture}%
	\end{subfigure}%
	\begin{subfigure}[c]{.5\linewidth}%
		\pgfmathsetlength{\imagewidth}{\imsize}%
		\pgfmathsetlength{\imagescale}{\imagewidth/1153}%
		\def\x{547}% scalebar-x measured at the center between the two lower jaws
		\def\y{774.25}% scalebar-y at 90% of image height of 815px = 734
		\begin{tikzpicture}[x=\imagescale,y=-\imagescale]
			\node[anchor=north west, inner sep=0pt, outer sep=0pt] at (0,0) {\includegraphics[width=\imagewidth]{104016/oj}};
			% 834.069px = 3.24mm -> 100px = 388.457um -> 128.714px = 500um, 25.743px = 100um
			%\draw[|-|,blue] (144,627) -- (978,594) node [sloped,midway,above,fill=white,semitransparent,text opacity=1] {\SI{3.24}{\milli\meter} (834px)};
			\draw[|-|,white] (\x-128.714/2,\y) -- (\x+128.714/2,\y) node [midway,below] {\SI{500}{\micro\meter}};
			\draw[color=black, anchor=north west] (0,0) node [fill=white, semitransparent] {B} node {B};
		\end{tikzpicture}
	\end{subfigure}\\%
	\begin{subfigure}[c]{.33\linewidth}
		\pgfmathsetlength{\imagewidth}{\imsize}%
		\pgfmathsetlength{\imagescale}{\imagewidth/1124}%
		\def\x{695}% scalebar-x starting at golden ratio of image width of 1124px = 695
		\def\y{551}% scalebar-y at 90% of image height of 580px = 522
		\begin{tikzpicture}[x=\imagescale,y=-\imagescale]
			\node[anchor=north west, inner sep=0pt, outer sep=0pt] at (0,0) {\includegraphics[width=\imagewidth]{104016/fish}};
			% 1090.775px = 70.0mm -> 100px = 6417.455um -> 7.791px = 500um, 1.558px = 100um
			%\draw[|-|,blue] (14,298) -- (1105,281) node [sloped,midway,above,fill=white,semitransparent,text opacity=1] {\SI{70.0}{\milli\meter} (1091px)};
			\draw[|-|,white] (\x,\y) -- (\x+77.91+77.91,\y) node [right] {\SI{1}{\centi\meter}};
			\draw[color=black, anchor=north west] (0,0) node [fill=white, semitransparent] {C} node {C};
		\end{tikzpicture}%
	\end{subfigure}%
	\begin{subfigure}[c]{.33\linewidth}
		\pgfmathsetlength{\imagewidth}{\imsize}%
		\pgfmathsetlength{\imagescale}{\imagewidth/710}%
		\def\x{439}% scalebar-x starting at golden ratio of image width of 710px = 439
		\def\y{664.05}% scalebar-y at 90% of image height of 699px = 629
		\begin{tikzpicture}[x=\imagescale,y=-\imagescale]
			\node[anchor=north west, inner sep=0pt, outer sep=0pt] at (0,0) {\includegraphics[width=\imagewidth]{104016/pj_top}};
			% 762.062px = 5.475mm -> 100px = 718.446um -> 69.595px = 500um, 13.919px = 100um
			%\draw[|-|,blue] (692,8) -- (362,696) node [sloped,midway,above,fill=white,semitransparent,text opacity=1] {\SI{5.475}{\milli\meter} (762px)};
			\draw[|-|,white] (\x,\y) -- (\x+69.595+69.595,\y) node [right] {\SI{1}{\milli\meter}};
			\draw[color=black, anchor=north west] (0,0) node [fill=white, semitransparent] {D} node {D};
		\end{tikzpicture}%
	\end{subfigure}%
	\begin{subfigure}[c]{.33\linewidth}
		\pgfmathsetlength{\imagewidth}{\imsize}%
		\pgfmathsetlength{\imagescale}{\imagewidth/1112}%
		\def\x{687+100+100}% scalebar-x starting at golden ratio of image width of 1112px = 687
		\def\y{337}% scalebar-y at 90% of image height of 374px = 337
		\begin{tikzpicture}[x=\imagescale,y=-\imagescale]
			\node[anchor=north west, inner sep=0pt, outer sep=0pt] at (0,0) {\includegraphics[width=\imagewidth]{104016/pj_side}};
			% 1067.600px = 5.195mm -> 100px = 486.606um -> 102.753px = 500um, 20.551px = 100um
			%\draw[|-|,blue] (46,191) -- (1109,87) node [sloped,midway,above,fill=white,semitransparent,text opacity=1] {\SI{5.195}{\milli\meter} (1068px)};
			\draw[|-|,white] (\x,\y) -- (\x+102.753+102.753/2,\y) node [midway,below] {\SI{750}{\micro\meter}};
			\draw[color=black, anchor=north west] (0,0) node [fill=white, semitransparent] {E} node {E};
		\end{tikzpicture}%
	\end{subfigure}%
\end{figure}
%----------
\end{document}%

### 2023-04-14 build/build.sh
Also build LaTeX

@@ -19,7 +19,7 @@ DOCKER_RUNNING="$(docker info &> /dev/null && echo "true" || (true && echo "fals
 CI="${CI:-false}"
 BUILD_PDF="${BUILD_PDF:-true}"
 BUILD_DOCX="${BUILD_DOCX:-true}"
-BUILD_LATEX="${BUILD_LATEX:-false}"
+BUILD_LATEX="${BUILD_LATEX:-true}"
 SPELLCHECK="${SPELLCHECK:-false}"
 MANUBOT_USE_DOCKER="${MANUBOT_USE_DOCKER:-$DOCKER_RUNNING}"
 # Pandoc's configuration is specified via files of option defaults

### 2023-04-14 manuscript.tex
Also build LaTeX [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/3e8bdc73d50e9e237a11c9c271a26468f5a9f151.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/3e8bdc73d50e9e237a11c9c271a26468f5a9f151/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/4698484929

@@
+\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
+\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} of the manuscript to \href{https://www.reviewcommons.org/}{Review Commons}, aiming for \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...3e8bdc73d50e9e237a11c9c271a26468f5a9f151}{has been updated} since submission.}
+
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/e9be1f19a7a3e08520efc834431cde4dfe4c4d4a/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/3e8bdc73d50e9e237a11c9c271a26468f5a9f151/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/e9be1f19a7a3e08520efc834431cde4dfe4c4d4a}{habi/EAWAG-manuscript@e9be1f1}
-on February 28, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/3e8bdc73d50e9e237a11c9c271a26468f5a9f151}{habi/EAWAG-manuscript@3e8bdc7}
+on April 14, 2023.
 
@@
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187} ·
+  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/habi}{habi}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
-  \href{https://twitter.com/habi}{habi}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/mastodon.svg}
+  \href{https://mastodon.social/@habi}{habi}
   Institute of Anatomy, University of Bern, Baltzerstrasse 2, CH-3012 Bern, Switzerland
@@
   \textbf{Mikki Law}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/mlaw-migalig}{mlaw-migalig}
-  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, EAWAG, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
+  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, Eawag, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
 \item
@@
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0002-4413-2633}{0000-0002-4413-2633}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://orcid.org/0000-0002-4413-2633}{0000-0002-4413-2633} ·
+  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/kassthefish}{kassthefish}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
-  \href{https://twitter.com/kassthefish}{kassthefish}
-  Department of Biological Sciences, George Washington University; EAWAG Aquatic Research Institute, Switzerland; Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland
+  Department of Biological Sciences, George Washington University, USA; Department of Fish Ecology and Evolution, Eawag, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland; Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland
 \item
   \textbf{Marcel Häsler}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/mphaesler}{mphaesler}
-  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, EAWAG, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
+  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, Eawag, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
 \item
@@
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0001-6598-1434}{0000-0001-6598-1434}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://orcid.org/0000-0001-6598-1434}{0000-0001-6598-1434} ·
+  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/OleSeehausen}{OleSeehausen}
-  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, EAWAG, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
+  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, Eawag, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
 \item
@@
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0002-6722-8996}{0000-0002-6722-8996}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://orcid.org/0000-0002-6722-8996}{0000-0002-6722-8996} ·
+  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/RuslanHlushchuk}{RuslanHlushchuk}
   Institute of Anatomy, University of Bern, Baltzerstrasse 2, CH-3012 Bern, Switzerland
-\end{itemize}
-
-\hypertarget{technicalities-temporary}{%
-\subsection{Technicalities (temporary)}\label{technicalities-temporary}}
-
-\begin{itemize}
-\tightlist
-\item
-  The \emph{canonical} version of the manuscript are the \href{https://en.wikipedia.org/wiki/Markdown}{Markdown} files in the \href{https://github.com/habi/EAWAG-manuscript/tree/main/content}{\texttt{content} folder} of the repository.
-\item
-  These files are automatically converted to a \href{https//habi.github.io/EAWAGmanuscript/}{website} as well as a \href{https//habi.github.io/EAWAGmanuscript/manuscript.pdf}{PDF} and \href{https//github.com/habi/EAWAGmanuscript/raw/output/manuscript.docx}{DOC} file through \href{https//manubot.org/}{\texttt{manubot}}.
-  You can read whichever file is most convenient for you.
-  Each version/file contains a link to the version in the header just below the title.
-  This version string is the so-called git hash of the repository.
-\item
-  On January 26, 2023 I've sent an email to the co-authors with \href{https//en.wikipedia.org/wiki/Request_for_Comments}{RFC}.
-  This version of the manuscript was \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v0.618}{tagged as version 0.618}, and there have been some changes since then.
-  You can visualize the changes made since then \href{https://github.com/habi/EAWAG-manuscript/compare/v0.618...main}{here}.
 \end{itemize}
@@
 
-A large collection of cichlids from Lake Victoria in Africa spanning a size range of 6 to 20 cm was nondestructively imaged using micro-computed tomography.
-We describe our method to efficiently obtain three-dimensional tomographic data sets of the oral and pharyngeal jaws and the whole skull of these fishes for accurately describing their morphology.
-The tomographic data we acquired (9.5 TB projection images) was reconstructed into 1.4 TB of three-dimensional images used for extracting the relevant features of interest.
-Herein we present our method and an outlook on analyzing the acquired data; a morphological description of the oral and pharyngeal jaws of the fishes, a principal component analysis of landmark features on the fish skulls and a robust method to automatically extract the otoliths of the fishes from the tomographic data.
+A large collection of cichlids from Lake Victoria in Africa spanning a length range of 6 to 18 cm was nondestructively imaged using micro-computed tomography.
+We describe our method to efficiently obtain three-dimensional tomographic datasets of the oral and pharyngeal jaws and the whole skull of these fishes for accurately describing their morphology.
+The tomographic data we acquired (9.5 TB of projection images) yielded 1.4 TB of three-dimensional image stacks used for extracting the relevant features of interest.
+Herein we present our method and an outlook on analyzing the acquired data; a morphological description of the oral and pharyngeal jaws of the fishes, a three-dimensional geometric morphometrics analysis of landmark features on the fish skulls, and a robust method to automatically extract the otoliths of the fishes from the tomographic data.
 
@@
 
-Cichlid fish in African lakes are a powerful model systems in speciation and adaptive evolutionary radiation research {[}\protect\hyperlink{ref-TUQFenhc}{1},\protect\hyperlink{ref-W2f2SDjn}{2}{]}.
-The functional decoupling of their oral and pharyngeal jaws is hypothesized to be a factor in making cichlids unusually versatile in their feeding and making it possible for making them able to adapt to a wide range of environmental factors {[}\protect\hyperlink{ref-1GEljkDsf}{3}{]}.
-The hypothesis is that the fusion of the lower pharyngeal jaws makes them powerful food processing tools, and this in turn releases the oral jaws from functional constraint.
+Cichlid fish in African lakes are powerful model systems in speciation and adaptive evolutionary radiation research {[}\protect\hyperlink{ref-TUQFenhc}{1},\protect\hyperlink{ref-W2f2SDjn}{2}{]}.
+The functional decoupling of their oral and pharyngeal jaws is hypothesized to be a factor in making cichlids unusually versatile in their feeding and allowing them the ability to adapt to a wide range of environmental factors {[}\protect\hyperlink{ref-1GEljkDsf}{3}{]}.
+The hypothesis is that the fusion of the lower pharyngeal jaws makes that jaw system a powerful food processing tool, in turn releasing the oral jaws from functional constraint.
 The oral jaws no longer need to process prey and can therefore specialize on prey capture.
 
-The group of Ole Seehausen has studied the evolutionary diversification of cichlid fish radiations in Lake Victoria in Africa since a long time {[}\protect\hyperlink{ref-W2f2SDjn}{2},\protect\hyperlink{ref-c3poTogo}{4}{]}.
-We aim to to better understand the functional anatomy of the skulls and jaws in these fishes in order to test the functional decoupling and other hypotheses about what may facilitate exceptionally high rates of morphological evolution.
+Even though the evolutionary diversification of cichlid fish radiations in Lake Victoria in Africa is a well-researched issue it remains a complex system in need of further study {[}\protect\hyperlink{ref-W2f2SDjn}{2},\protect\hyperlink{ref-c3poTogo}{4}{]}.
+We aim to better understand the functional anatomy of the skulls and jaws in these fish in order to test the functional decoupling and other hypotheses about what may facilitate exceptionally high rates of morphological evolution.
 
 The collection of cichlid fish available is extremely valuable, hence a nondestructive imaging method is paramount for studying these samples.
-Since micro--computed tomography can be regarded as nondestructive method for biological samples, it is a very well suited method for investigating the oral and pharyngeal jaws as well as the skull features of the fishes presented in this study.
+Since micro--computed tomography can be regarded as nondestructive method for biological samples, it is the ideal imaging method for investigating the oral and pharyngeal jaws as well as the skull features of the fish presented in this study {[}\protect\hyperlink{ref-19h9vxsYG}{5}{]}.
 
@@
 
-X-ray microtomography is a valuable tool to gain insights into the inner structure of very diverse samples, namely for specimens related to research done in the biomedical sciences.
-Microtomographic imaging has been employed as a method of choice to nondestructively assess the morphology of different kind of fishes, large and small.
-For a small overview of analyses which are possible with X-ray microtomographic imaging in relation to fish biology and morphology, see prior work of the authors of this manuscript {[}\protect\hyperlink{ref-8Pmc2mI8}{5},\protect\hyperlink{ref-BDrCSu8p}{6}{]} or other authors {[}\protect\hyperlink{ref-3rxGCEvJ}{7}{]}\footnote{For which David made a tomographic scan of an adult zebrafish in 2016.}.
+X-ray microtomography is a valuable tool to gain insights into the inner structure of highly diverse samples, namely for specimens related to research done in the biomedical sciences.
+Microtomographic imaging has been employed as a method of choice to nondestructively assess the morphology of different fish species, large and small {[}\protect\hyperlink{ref-19h9vxsYG}{5}{]}.
+For a small overview of analyses which are possible with X-ray microtomographic imaging in relation to fish biology and morphology, see prior work of the authors of this manuscript {[}\protect\hyperlink{ref-19h9vxsYG}{5}--\protect\hyperlink{ref-BDrCSu8p}{7}{]} as well as other studies {[}\protect\hyperlink{ref-3rxGCEvJ}{8}{]}.
 
-Depending on the structures of interest, biomedical samples are often tomographically scanned after the tissue/sample has been stained with a contrast agent, most often employing contrast agents containing heavy metals.
+Depending on the structures of interest, biomedical samples are often only tomographically scanned after being stained with a contrast agent, most often employing contrast agents containing heavy metals.
 Since the structures of interest for the two studies we touch upon in this manuscript (cichlid teeth and skulls) display large enough contrast to the surrounding tissue we did not stain our samples prior to the tomographic imaging presented here.
@@
 
-The fishes were kept in 75\% Ethanol for long-term storage in the EAWAG fish collection.
-They were delivered to the Institute of Anatomy for micro-CT imaging sorted into several batches by approximately equal length.
+The fish were kept in 75\% ethanol for long-term storage at the Swiss Federal Institute of Aquatic Science and Technology (Eawag).
+They were delivered to the Institute of Anatomy for micro-CT imaging sorted into batches of approximately equal length.
 
@@
 
-The fishes were sorted into `bins' based on their physical size.
+The fish were sorted into `bins' based on their physical size.
 We used a custom-made sample-holder to scan each of the fish in our machines.
-It was 3D-printed on a Form 2 desktop stereolithography printer (Formlabs, Somerville, Massachusetts, USA) and is freely available online {[}\protect\hyperlink{ref-VCZPOv2f}{8}{]} as part of a library of sample holders for tomographic scanning of biomedical samples {[}\protect\hyperlink{ref-115PPSuQp}{9}{]}.
-The sample holder was custom-made for this project and is easily parametrized to the different width, height and length classes of the fishes we scanned.
+It was 3D-printed on a Form 2 desktop stereolithography printer (Formlabs, Somerville, Massachusetts, USA), the file for printing the holder is available online {[}\protect\hyperlink{ref-VCZPOv2f}{9}{]} as part of a library of sample holders for tomographic scanning of biomedical samples {[}\protect\hyperlink{ref-115PPSuQp}{10}{]}.
+The original \emph{OpenSCAD} {[}\protect\hyperlink{ref-wsjdcTeC}{11}{]} file {[}\protect\hyperlink{ref-f7OzrzUv}{12}{]} is parametrized to effortlessly generate a file for 3D-printing sample holders to accommodate the varying width, height and length classes of the fish.
 
-In total, we acquired 362 tomographic scans of 129 different fishes.
-All the scanning parameters are collected in a table in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}, a generalized rundown is given below.
+In total, we acquired 362 tomographic scans of 129 different specimens.
+All the scanning parameters are collected in a table in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}; a generalized rundown is given below.
 
-Since the fishes greatly varied in their length, the voxel sizes of each of the acquired datasets also varies greatly.
-We acquired datasets with (isometric) voxel sizes ranging from 3.5--50 μm.
+Since the fish greatly varied in their length (specimen length varied between 6 cm and 18 cm), the voxel sizes of each of the acquired datasets also varies greatly.
+We acquired datasets with (isometric) voxel sizes ranging from 3.5 to 50 μm.
 
-Depending on the size of the specimen we set the x-ray source voltage to 50--80 kV and---depending on the voltage---to a current between 107 and 200 μA.
-Also depending on the size of the fishes, the x-ray spectrum was filtered either by an Aluminum filter of varying thickness (either 0.25, 0.5 or 1 mm) before digitization to projection images or recorded in an unfiltered way.
-In total we recorded 9.5 TB of projections images (\texttt{*.tif} and \texttt{*.iif} files, where the \texttt{*.iif} files are for the so-called alignment scans).
+Depending on the size of the specimen we set the X-ray source voltage to 50--80 kV and---depending on the voltage---to a current between 107 and 200 μA.
+The X-ray spectrum was filtered either by an aluminum filter of varying thickness (either 0.25, 0.5 or 1 mm for increasing specimen size) before digitization to projection images or recorded in an unfiltered way (for smaller specimen).
+In total we recorded 9.5 TB of projection images (\texttt{TIFF} and \texttt{*.iif} files, where the \texttt{*.iif} files are for the so-called alignment scans).
 
-All the recorded projection images were subsequently reconstructed into a 3D stack of axial images spanning the regions of interest of each fish.
+All the recorded projection images were subsequently reconstructed into virtual 3D stacks of axial \texttt{PNG} images spanning the regions of interest of each fish.
 All the specimens were scanned with their mouths facing downward in the sample holder and rotating along their long axis.
 We thus manually aligned each of the reconstructed datasets so that the lateral axis of the fish was horizontal in relation to the x and y direction of the reconstructed slices.
-We reconstructed the projection images with NRecon (Version 1.7.4.6, Bruker microCT, Kontich Belgium) with varying ring artifact and beam hardening correction values, depending on each fish (again, all relevant values are listed in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}).
+We reconstructed the projection images with NRecon (Version 1.7.4.6, Bruker microCT, Kontich, Belgium) with varying ring artifact and beam hardening correction values, depending on each fish (again, all relevant values are listed in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}).
 In total, this resulted in 1.4 TB of reconstruction images (nearly one million \texttt{*rec*.png} files).
@@
 While performing the work, a subset of the data was always present on the production system, for working with it (see \protect\hyperlink{preparation-for-analysis}{Preparation for analysis} below).
-A small bash script {[}\protect\hyperlink{ref-ZjgrPHTa}{10}{]} was used to generate redundant (archival) copies of the raw projection images and copy all the files to a shared network drive on the \texttt{Research\ Storage} infrastructure of the University of Bern, enabling easy collaboration on the data by all authorized persons at the same time.
+A small bash script {[}\protect\hyperlink{ref-ZjgrPHTa}{13}{]} was used to generate redundant (archival) copies of the raw projection images and copy all the files to a shared network drive on the `Research Storage' infrastructure of the University of Bern, enabling collaboration on the data by all authorized persons at the same time.
 
@@
 
-We wrote a set of \emph{Jupyter} {[}\protect\hyperlink{ref-pQ6Wbz73}{11}{]} notebooks with \emph{Python} code to work with the images and wrangle the acquired data.
+We wrote a set of \emph{Jupyter} {[}\protect\hyperlink{ref-pQ6Wbz73}{14}{]} notebooks with \emph{Python} code to work with the images and wrangle the acquired data.
 The notebooks were written at the start of the project, to be able to process new scans as soon as they were reconstructed.
-Re-runs of the notebook added newly scanned and reconstructed fishes to the analysis, facilitating an efficient quality check of the scans and batched processing of the data.
+Re-runs of the notebook added newly scanned and reconstructed data to the analysis, facilitating an efficient quality check of the scans and batched processing of the data.
 
-All analysis notebooks for this work are available online {[}\protect\hyperlink{ref-1HteOscVd}{12}{]}.
+All analysis notebooks for this work are available online {[}\protect\hyperlink{ref-1HteOscVd}{15}{]}.
 
@@
 
-The \href{https//github.com/habi/EAWAG/blob/master/DisplayFishes.ipynb}{main Jupyter notebook} for this manuscript dealt with reading all log and image files and preparing images for quality checking and further analysis.
-Briefly summarized the below process was implemented.
+The \href{https://github.com/habi/EAWAG/blob/master/DisplayFishes.ipynb}{main \emph{Jupyter} notebook} for this manuscript dealt with reading all log and image files and preparing images for quality checking and further analysis.
 
-At first, \emph{all} log files of \emph{all} the data present in the processed folder were read into a \emph{pandas} {[}\protect\hyperlink{ref-19qQOHlFN}{13}{]} dataframe.
-This already enabled us to extract the specimen name and scan, since we performed several scans for each specimen, i.e.~a low resolution scan with large field of view for the whole head and one or several scans in high resolution focusing on the oral and pharyngeal jaws.
+At first, \emph{all} log files of \emph{all} the data present in the processed folder were read into a \emph{pandas} {[}\protect\hyperlink{ref-19qQOHlFN}{16},\protect\hyperlink{ref-U5AcoDOX}{17}{]} dataframe.
+This already enabled us to extract the specimen name and scan, since we performed multiple scans for each specimen, i.e.~a low resolution scan with large field of view for the whole head and one or two scans in high resolution focusing on the region of the oral and pharyngeal jaws.
 From the log files we extracted the relevant values for double-checking the necessary parameters of each scan.
@@
 
-After several `sanity checks' of the data, we used \emph{Dask} {[}\protect\hyperlink{ref-hj1CnyWB}{14}{]} to efficiently access the very large total amount of axial reconstructions for this project (in the end amounting to a total of nearly a million single images).
-On average, each of the tomographic datasets contains around 2700 slices, so the total amount of data is much too large to keep in memory.
-The use of the Dask library facilitated efficient access to the huge amount of data on disk.
+After performing `sanity checks' of the data and reconstruction parameters, we used \emph{Dask} {[}\protect\hyperlink{ref-hj1CnyWB}{18}{]} to efficiently access the tomographic data on disk (in the end amounting to a total of nearly a million single images).
+On average, each of the tomographic datasets contains around 2700 slices, so the total size of the acquired data exceeds the RAM size available on an average high-end workstation.
 
@@
 
-To extract the oral jaw (OJ) and pharyngeal jaw (PJ) of the fishes, we used \href{https://www.slicer.org}{3DSlicer} (Version 4.11.20210226) {[}\protect\hyperlink{ref-OsCpHsJH}{15}{]} extended with the \emph{SlicerMorph} tools {[}\protect\hyperlink{ref-MwdN6kPV}{16}{]} which aim to help biologists work with 3D specimen data.
-The reconstructed PNG stacks were loaded into \emph{ImageStacks}, depending on their size we reduced the image resolution (i.e.~downscaled the images) for this first step.
+To extract the oral jaw (OJ) and pharyngeal jaw (PJ) of the fish, we used \href{https://www.slicer.org}{\emph{3D Slicer}} (Version 4.11.20210226) {[}\protect\hyperlink{ref-OsCpHsJH}{19}{]} extended with the \emph{SlicerMorph} tools {[}\protect\hyperlink{ref-MwdN6kPV}{20}{]} which aim to help biologists work with 3D specimen data.
+The reconstructed image stacks were loaded into \href{https://www.slicer.org/wiki/Documentation/Labs/ImageStacks}{\emph{ImageStacks}}, depending on their size we reduced the image resolution (i.e.~downscaled the images) for this first step.
 The three-dimensional volume was rendered via \href{https://slicer.readthedocs.io/en/latest/user_guide/modules/volumerendering.html}{\emph{VTK GPU Ray Casting}}.
@@
 These ROIs were then extracted in their native resolution from the original dataset for further processing.
-Using the gray value thresholding function in 3DSlicer's \href{https://slicer.readthedocs.io/en/latest/user_guide/modules/segmenteditor.html}{\emph{Segment Editor}}, the teeth in both the oral and pharyngeal jaws were extracted.
-We used the \emph{Scissor} and \emph{Island} tools of the Segment Editor to isolate single regions.
+Using the gray value thresholding function in \emph{3D Slicer}'s \href{https://slicer.readthedocs.io/en/latest/user_guide/modules/segmenteditor.html}{\emph{Segment Editor}}, the teeth in both the oral and pharyngeal jaws were extracted.
+We used the \emph{Scissor} and \emph{Island} tools of the \emph{Segment Editor} to isolate single regions.
 
-Processed regions of interest were exported as NRRD {[}\protect\hyperlink{ref-12B4h087w}{17}{]} files.
+Processed regions of interest were exported as \texttt{Nrrd} {[}\protect\hyperlink{ref-uYuz0opI}{21}, =Nrrd\&oldid=1085264080{]} files.
 The three-dimensional visualizations of all regions of interest for each specimen were compiled into overview images (see Figure \ref{fig:104016} for an example from the compilation document).
@@
 \includegraphics{images/104016.png}
-\caption{Overview of data from sample 104016,~\emph{Enterochromis I cinctus} (St.~E)}\label{fig:104016}
+\caption{Overview of data from sample 104016,~\emph{Enterochromis I cinctus} (St.~E).
+Panel A: Three-dimensional visualization of the head scan.
+Panel B: Three-dimensional visualization of the oral jaw scan.
+Panel C: Photograph of the specimen.
+Panels D and E: Three-dimensional visualization of the pharyngeal jaw, dorsoventral and lateral view, respectively.}\label{fig:104016}
 }
@@
 
-\hypertarget{principal-component-analysis-of-skull-landmarks}{%
-\paragraph{Principal component analysis of skull landmarks}\label{principal-component-analysis-of-skull-landmarks}}
+\hypertarget{principal-components-analysis-of-skull-landmarks}{%
+\paragraph{Principal components analysis of skull landmarks}\label{principal-components-analysis-of-skull-landmarks}}
 
 Current studies are using 3D geometric morphometrics to compare the morphological shape of these scanned cichlids using statistical analysis.
-A homologous landmark scheme was produced {[}\protect\hyperlink{ref-BDrCSu8p}{6},\protect\hyperlink{ref-15FafMZm5}{18}{]}, and landmarks were placed on each specimen using 3DSlicer.
-To examine differences in shape across the species sampled, we performed a Generalized Procrustes Superimposition on the landmark data to remove the effects of location, size, and rotation from the analysis using the \emph{geomorph} package in \emph{R} (Version 4.2.1) with \emph{RStudio} (Version 2022.07.2+576) {[}\protect\hyperlink{ref-VPUOQA2P}{19},\protect\hyperlink{ref-Ziptbtib}{20},\protect\hyperlink{ref-EwNL0C0Y}{21},\protect\hyperlink{ref-whEyWyQh}{22},\protect\hyperlink{ref-QfVloFVu}{23}{]}.
+We used a homologous landmark scheme across one-half of the skull for higher density of shape information {[}\protect\hyperlink{ref-BDrCSu8p}{7},\protect\hyperlink{ref-15FafMZm5}{22}{]}, and landmarks were placed on each specimen using \emph{3D Slicer}.
+To examine differences in shape across the species sampled, we performed a Generalized Procrustes Superimposition on the landmark data to remove the effects of location, size, and rotation from the analysis using the \emph{geomorph} package in \emph{R} (Version 4.2.1) with \emph{RStudio} (Version 2022.07.2+576) {[}\protect\hyperlink{ref-VPUOQA2P}{23}--\protect\hyperlink{ref-EwNL0C0Y}{25},\protect\hyperlink{ref-whEyWyQh}{26},\protect\hyperlink{ref-QfVloFVu}{27}{]}.
 This process brings all specimens to a common origin, scales the landmarks to a unit centroid size, and rotates specimens to reduce distances between landmarks.
-A principal component analysis was then performed on the superimposed landmark data to visualize the major axes of shape change across sampled species.
+A principal components analysis was then performed in \emph{geomorph} on the superimposed landmark data to visualize the major axes of shape change across sampled species.
 We then used phylogenetic information to identify instances of repeated evolution of trophic adaptations in these cichlids.
@@
 Otoliths are structures made up of mostly calcium carbonate located in the head of fishes.
-Due to their composition they show up nicely on the X-ray images we acquired.
-We devised a very robust image processing method to automatically detect the location of the otoliths in the heads of the fishes and extract them from the original data.
-The whole method is implemented in its own \href{https://github.com/habi/EAWAG/blob/master/ExtractOtoliths.ipynb}{Jupyter notebook} (part of the aforementioned analysis repository {[}\protect\hyperlink{ref-1HteOscVd}{12}{]}) and is briefly explained below.
-The notebook performing the otolith extraction can be run without installation of any software in a web browser, thanks to the help of Binder {[}\protect\hyperlink{ref-Q20Bxdsr}{24}{]}; to do this, one can start the notebook \href{https://mybinder.org/v2/gh/habi/EAWAG/HEAD?labpath=ExtractOtoliths.ipynb}{here}.
+Due to their composition, they are easily distinguished in the X-ray images we acquired.
+We devised an image processing method to automatically and robustly detect the location of the otoliths in the heads of the cichlids we scanned and to extract them from the original data.
+The whole method is implemented in its own \href{https://github.com/habi/EAWAG/blob/master/ExtractOtoliths.ipynb}{\emph{Jupyter} notebook} (part of the aforementioned analysis repository {[}\protect\hyperlink{ref-1HteOscVd}{15}{]}).
 
-Since we took great care to scan the fishes parallel to their \emph{anteroposterior} direction and reconstructed the tomographic datasets parallel to the \emph{lateral} and \emph{dorsoventral} direction of the fishes we could use this `preparation' for automatically extracting the otoliths in scans of the full heads of the fishes.
+Since we took great care to scan the fish parallel to their anteroposterior direction and reconstructed the tomographic datasets parallel to the lateral and dorsoventral direction of the fish we could use this `preparation' for automatically extracting the otoliths the tomographic datasets of the whole fish heads.
 By extracting both the peaks and the peak widths of the gray values along both the horizontal and vertical direction of the MIP (generated above) we robustly detected the position of the otoliths in the datasets.
@@
 The white bars show the mean of the to detected positions, which was used for extracting the otoliths from the original datasets.
-Making use of the \texttt{dask} library facilitated efficient access to all the data on disk and writing out small, cropped copies of the datasets around the otolith positions.
+Making use of the \emph{Dask} library facilitated efficient access to all the data on disk and writing out small, cropped copies of the datasets around the otolith positions.
 
 By detecting the largest components in the cropped copies of the datasets we can easily extract and visualize the otoliths in 3D, as shown in Figure \ref{fig:otolith3d}.
-The extracted otoliths are thus prepared for further analysis and display.
-The simple three-dimensional visualization is integrated in the aforementiones Jupyter notebook through an integrated visualization library {[}\protect\hyperlink{ref-a9ZL41Of}{25}{]} and is also shown in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}.
+The extracted otoliths are thus prepared for further analysis and visualization.
+The simple three-dimensional visualization is integrated in the aforementioned \emph{Jupyter} notebook through an integrated visualization library {[}\protect\hyperlink{ref-a9ZL41Of}{28}{]} and is also shown in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}.
 
@@
 \includegraphics{images/104016.head.rec.otolith.region.3D.png}
-\caption{Static three-dimensional view of extracted otolith of specimen 104016.
-The specimen was scanned with a voxel size of 13 μm.
+\caption{Static three-dimensional view of extracted otoliths of specimen 104016.
+The specimen was scanned with an isotropic voxel size of 13 μm.
 The extracted otolith has a size of approximately 250 x 350 x 150 pixels.
@@
 
+The notebook for extracting the otoliths can be run in your browser without installing any additional software (via \emph{Binder} {[}\protect\hyperlink{ref-Q20Bxdsr}{29}{]}).
+To do this, one starts the notebook by \href{https://mybinder.org/v2/gh/habi/eawag/HEAD?labpath=ExtractOtoliths.ipynb}{clicking a single button} in the \href{https://github.com/habi/EAWAG/blob/master/README.md}{README file} of the \href{https://github.com/habi/EAWAG}{project repository} {[}\protect\hyperlink{ref-1HteOscVd}{15}{]}.
+This starts a computing environment in the cloud, downloads the tomographic data we acquired of \emph{one} specimen, and performs both the otolith extraction and visualization in your browser.
+
 \hypertarget{discussion}{%
@@
 
-We acquired high resolution tomographic datasets of a large collection of Cichlids.
-The acquired datasets were imaged over a wide-spanning range of voxel size (3.5--50 μm) permitting both the analysis of finest details we wanted to resolve (i.e.~the structure of the teeth) and having datasets spanning the whole region of interest of the fishes (i.e.~the whole head for principle component analysis)
+We acquired high resolution tomographic datasets of a large collection of cichlids.
+The acquired datasets were imaged over a wide-spanning range of voxel size (3.5--50 μm) permitting both the analysis of finest details we wanted to resolve (i.e.~the structure of the teeth) and having datasets spanning the whole region of interest of the fish (i.e.~the whole head for principle components analysis).
 
@@
 The whole study we presented here spanned a \emph{long} time frame.
-It was thus paramount to make the imaging process and preparation of the tomographic datasets able to run in batch-mode.
-The Jupyter notebook written to prepare the datasets for quality control and analysis were facilitating a short turnaround time for feedback on single scans.
+It was thus paramount to run the imaging process and the preparation of the tomographic datasets in a batched mode.
+The \emph{Jupyter} notebook written to prepare the datasets for quality control and analysis were facilitating a short turnaround time for feedback on single scans and such a batched analysis.
 
@@
 
-The method to extract the otoliths of the fishes from the tomographic dataset works robustly for all of the different fish sizes and shapes.
-The extraction is robust because it is based on a combination of several intricate details of the gray value curve over the different anatomical directions.
-The details of the otolith extraction method have been tuned extensively by us and it now runs completely automatically, allowing for highly reproducible and completely unbiased extraction of the otoliths from the tomographic datasets.
-This is even the case for one fish which was scanned with still a hook in his mouth, where the otolihts were nonetheless extracted automatically.
+The method to extract the otoliths from the tomographic dataset works robustly for all of the different fish sizes and shapes.
+The extraction is robust because it is based on a combination of distinct details of the gray value curve over the different anatomical directions.
+The details of the otolith extraction method have been extensively tuned and run in a fully automatic way.
+This allows a highly reproducible and unbiased extraction of the otoliths from the tomographic datasets.
+This is even the case for one fish which was scanned with still a hook in his mouth, where the otoliths were nonetheless extracted automatically.
 
-Data on such automatically extracted otoliths, like volume and geometric information like eccentricity and moments of inertia could be biologically really interesting as the otoliths grow with the age of the fish.
-However, one would first have to calibrate the data on the otolits length or volume with otoliths of fish of known age but this could help to estimate the age of wild fishes.
-Estimation of age of tropical fishes is not as simple as for fishes from temperate regions where one can distinguish summer and winter layers within the otolith.
+Data on such automatically extracted otoliths, like volume and geometric information like eccentricity and moments of inertia is biologically interesting as the otoliths grow with the age of the fish.
+One could help estimate the age of wild fishes using a calibration based on the otolith measurements of a fish of known age.
+It is worth nothing that estimation of age of tropical fishes is not as simple as for fishes from temperate regions where one can distinguish summer and winter layers within the otolith.
 
@@
 
-The acquired tomographic datasets are the basis for several additional analysis of fish morphology.
+The acquired tomographic datasets are the basis for multiple additional analyses of fish morphology.
 
-The presented method offers an insight and algorithm on how to perform tomographic scans, preview and analyze micro-computer tomographic datasets of a large collection of fishes.
+The presented method offers an insight and algorithm on how to perform tomographic scans, preview and analyze micro-computer tomographic datasets of a large collection of fish.
 The workflow is relying only on free and open-source software and can thus be used and verified independently by any interested reader.
-All the Jupyter notebook described herein is also freely available online {[}\protect\hyperlink{ref-1HteOscVd}{12}{]}.
+All the \emph{Jupyter} notebook described herein is also freely available online {[}\protect\hyperlink{ref-1HteOscVd}{15}{]}.
+
+\hypertarget{author-contributions}{%
+\subsection{Author Contributions}\label{author-contributions}}
+
+\href{https://credit.niso.org/}{Contributor Roles Taxonomy}, as defined by the \href{https://credit.niso.org/contributor-roles-defined/}{National Information Standards Organization}.
+
+\begin{tablenos:no-prefix-table-caption}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+Author
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Contributions
+\end{minipage} \\
+\midrule
+\endhead
+David Haberthür & Conceptualization, Data curation, Formal Analysis, Investigation, Methodology, Project administration, Software, Visualization, Writing -- original draft, Writing -- review \& editing \\
+Mikki Law & Data curation, Investigation, Methodology, Project administration, Visualization, Writing -- review \& editing \\
+Kassandra Ford & Investigation, Methodology, Visualization, Writing -- review \& editing \\
+Marcel Häsler & Investigation, Project administration, Resources, Writing -- review \& editing \\
+Ole Seehausen & Conceptualization, Investigation, Resources, Supervision, Writing -- review \& editing \\
+Ruslan Hlushchuk & Conceptualization, Resources, Supervision, Writing -- review \& editing \\
+\bottomrule
+\end{longtable}
+
+\end{tablenos:no-prefix-table-caption}
 
@@
 
-We thank Salome Mwaiko for taking care of the fish collection at EAWAG and Mark Charran for helping to find suitable specimens to represent each species.
-We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{26}{]} for helping us write this manuscript collaboratively.
+We thank Salome Mwaiko for taking care of the fish collection at Eawag and Mark Charran for helping to find suitable specimens to represent each species.
+We are grateful to the \href{https//www.mic.unibe.ch/}{Microscopy Imaging Center} of the University of Bern for the infrastructural support.
+We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{30}{]} for helping us write this manuscript collaboratively.
 
@@
 
-The three-dimensional view of sample 104016 was generated in \href{https://github.com/habi/EAWAG/blob/master/ExtractOtoliths.ipynb}{the otolith extraction notebook} and saved as \href{https://github.com/habi/EAWAG-manuscript/blob/main/content/data/104016.head.rec.otolith.region.3D.html}{104016.head.rec.otolith.region.3D.html} file.
-A fully functional copy can be viewed through the \href{https://htmlpreview.github.io/?https://github.com/habi/EAWAG-manuscript/blob/main/content/data/104016.head.rec.otolith.region.3D.html}{GitHub HTML preview}.
+The three-dimensional view of sample 104016 was generated in \href{https://github.com/habi/EAWAG/blob/master/ExtractOtoliths.ipynb}{the otolith extraction notebook} and saved as a \href{https://github.com/habi/EAWAG-manuscript/blob/main/content/data/104016.head.rec.otolith.region.3D.html}{self-contained \texttt{HTML} file} with \href{https://github.com/K3D-tools/K3D-jupyter}{\emph{K3D-jupyter}}.
+A copy of this \texttt{HTML} file can be viewed and interacted with through the \href{https://htmlpreview.github.io/?https://github.com/habi/EAWAG-manuscript/blob/main/content/data/104016.head.rec.otolith.region.3D.html}{GitHub HTML preview}.
 
@@
 \CSLLeftMargin{1. }
-\CSLRightInline{\textbf{Adaptive evolution and explosive speciation: the cichlid fish model}
-\CSLBlock{Thomas D Kocher} \emph{Nature Reviews Genetics} (2004-04-01) \url{https://doi.org/dkgf93}
-\CSLBlock{DOI: \href{https://doi.org/10.1038/nrg1316}{10.1038/nrg1316} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/15131652}{15131652}}}
+\CSLRightInline{Kocher TD. Adaptive evolution and explosive speciation: the cichlid fish model. Nat Rev Genet. 2004;5: 288--298. doi:\href{https://doi.org/10.1038/nrg1316}{10.1038/nrg1316}}
 
@@
 \CSLLeftMargin{2. }
-\CSLRightInline{\textbf{African cichlid fish: a model system in adaptive radiation research}
-\CSLBlock{Ole Seehausen} \emph{Proceedings of the Royal Society B: Biological Sciences} (2006-05-09) \url{https://doi.org/frrhbq}
-\CSLBlock{DOI: \href{https://doi.org/10.1098/rspb.2006.3539}{10.1098/rspb.2006.3539} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/16846905}{16846905} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1635482}{PMC1635482}}}
+\CSLRightInline{Seehausen O.
+African cichlid fish: a model system in adaptive radiation research.
+Proc R Soc B.
+2006;273: 1987--1998.
+doi:\href{https://doi.org/10.1098/rspb.2006.3539}{10.1098/rspb.2006.3539}}
 
@@
 \CSLLeftMargin{3. }
-\CSLRightInline{\textbf{Evolutionary Strategies and Morphological Innovations: Cichlid Pharyngeal Jaws}
-\CSLBlock{Karel F Liem} \emph{Systematic Zoology} (1973-12) \url{https://doi.org/b969fp}
-\CSLBlock{DOI: \href{https://doi.org/10.2307/2412950}{10.2307/2412950}}}
+\CSLRightInline{Liem KF. Evolutionary Strategies and Morphological Innovations: Cichlid Pharyngeal Jaws. Systematic Zoology. 1973;22: 425. doi:\href{https://doi.org/10.2307/2412950}{10.2307/2412950}}
 
@@
 \CSLLeftMargin{4. }
-\CSLRightInline{\textbf{Process and pattern in cichlid radiations -- inferences for understanding unusually high rates of evolutionary diversification}
-\CSLBlock{Ole Seehausen} \emph{New Phytologist} (2015-05-13) \url{https://doi.org/f7gczg}
-\CSLBlock{DOI: \href{https://doi.org/10.1111/nph.13450}{10.1111/nph.13450} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/25983053}{25983053}}}
+\CSLRightInline{Seehausen O.
+Process and pattern in cichlid radiations -- inferences for understanding unusually high rates of evolutionary diversification.
+New Phytol.
+2015;207: 304--312.
+doi:\href{https://doi.org/10.1111/nph.13450}{10.1111/nph.13450}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-19h9vxsYG}{}}%
+\CSLLeftMargin{5. }
+\CSLRightInline{Ford KL, Albert JS, Summers AP, Hedrick BP, Schachner ER, Jones AS, et al.
+A New Era of Morphological Investigations: Reviewing Methods for Comparative Anatomical Studies.
+Integrative Organismal Biology.
+2023;5.
+doi:\href{https://doi.org/10.1093/iob/obad008}{10.1093/iob/obad008}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-8Pmc2mI8}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{\textbf{Adaptation mechanism of the adult zebrafish respiratory organ to endurance training}
-\CSLBlock{Matthias Messerli, Dea Aaldijk, David Haberthür, Helena Röss, Carolina García-Poyatos, Marcos Sande-Melón, Oleksiy-Zakhar Khoma, Fluri AM Wieland, Sarya Fark, Valentin Djonov} \emph{PLOS ONE} (2020-02-05) \url{https://doi.org/grf6fj}
-\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pone.0228333}{10.1371/journal.pone.0228333} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/32023296}{32023296} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7001924}{PMC7001924}}}
+\CSLLeftMargin{6. }
+\CSLRightInline{Messerli M, Aaldijk D, Haberthür D, Röss H, García-Poyatos C, Sande-Melón M, et al.
+Adaptation mechanism of the adult zebrafish respiratory organ to endurance training.
+Shelden EA, editor.
+PLoS ONE.
+2020;15: e0228333.
+doi:\href{https://doi.org/10.1371/journal.pone.0228333}{10.1371/journal.pone.0228333}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-BDrCSu8p}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{\textbf{Convergence is Only Skin Deep: Craniofacial Evolution in Electric Fishes from South America and Africa (Apteronotidae and Mormyridae)}
-\CSLBlock{Kassandra L Ford, Rose Peterson, Maxwell Bernt, James S Albert} \emph{Integrative Organismal Biology} (2022) \url{https://doi.org/gq3gtc}
-\CSLBlock{DOI: \href{https://doi.org/10.1093/iob/obac022}{10.1093/iob/obac022} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/35976714}{35976714} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC9375771}{PMC9375771}}}
+\CSLLeftMargin{7. }
+\CSLRightInline{Ford KL, Peterson R, Bernt M, Albert JS.
+Convergence is Only Skin Deep: Craniofacial Evolution in Electric Fishes from South America and Africa (Apteronotidae and Mormyridae).
+Integrative Organismal Biology.
+2022;4.
+doi:\href{https://doi.org/10.1093/iob/obac022}{10.1093/iob/obac022}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-3rxGCEvJ}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{\url{https://osf.io/ecmz4}}
+\CSLLeftMargin{8. }
+\CSLRightInline{Available: \url{https://osf.io/ecmz4}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-VCZPOv2f}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{\textbf{OpenSCAD models}
-\CSLBlock{TomoGraphics} (2022-02-28) \url{https://github.com/TomoGraphics/Hol3Drs/blob/dedca665a77fa782c103eed63b866b2cceb30de9/STL/EAWAG.Fish.stl}}
+\CSLLeftMargin{9. }
+\CSLRightInline{OpenSCAD models. TomoGraphics; 2022. Available: \url{https://github.com/TomoGraphics/Hol3Drs/blob/dedca665a77fa782c103eed63b866b2cceb30de9/STL/EAWAG.Fish.stl}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-115PPSuQp}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{\textbf{TomoGraphics/Hol3Drs: A release}
-\CSLBlock{David Haberthür} \emph{Zenodo} (2019-03-08) \url{https://doi.org/gg9fxh}
-\CSLBlock{DOI: \href{https://doi.org/10.5281/zenodo.2587555}{10.5281/zenodo.2587555}}}
+\CSLLeftMargin{10. }
+\CSLRightInline{Haberthür D. TomoGraphics/Hol3Drs: A release. Zenodo; 2019. doi:\href{https://doi.org/10.5281/zenodo.2587555}{10.5281/zenodo.2587555}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
+\CSLLeftMargin{11. }
+\CSLRightInline{OpenSCAD. {[}cited 14 Apr 2023{]}. Available: \url{https://openscad.org}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-f7OzrzUv}{}}%
+\CSLLeftMargin{12. }
+\CSLRightInline{OpenSCAD models. TomoGraphics; 2022. Available: \url{https://github.com/TomoGraphics/Hol3Drs/blob/dedca665a77fa782c103eed63b866b2cceb30de9/EAWAG.Fish.scad}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-ZjgrPHTa}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{\textbf{Jupyter notebooks for image processing and data analysis of EAWAG Cichlids project}
-\CSLBlock{David Haberthür} (2022-07-05) \url{https://github.com/habi/EAWAG/blob/1f81f8138c49ac5d111288d8b28a0f81c222cca5/rsync-fishes.sh}}
+\CSLLeftMargin{13. }
+\CSLRightInline{Haberthür D.
+Jupyter notebooks for image processing and data analysis of EAWAG Cichlids project.
+2023.
+Available: \url{https://github.com/habi/EAWAG/blob/e5d6be6b416b7c66eaf72a563b0ce5648569f54d/rsync-fishes.sh}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-pQ6Wbz73}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{\textbf{Jupyter Notebooks -- a publishing format for reproducible computational workflows}
-\CSLBlock{Thomas Kluyver, Benjamin Ragan-Kelley, Fernando Pérez, Brian Granger, Matthias Bussonnier, Jonathan Frederic, Kyle Kelley, Jessica Hamrick, Jason Grout, Sylvain Corlay, \ldots{} Jupyter development team} \emph{IOS Press} (2016) \url{https://eprints.soton.ac.uk/403913/}
-\CSLBlock{DOI: \href{https://doi.org/10.3233/978-1-61499-649-1-87}{10.3233/978-1-61499-649-1-87}}}
+\CSLLeftMargin{14. }
+\CSLRightInline{Kluyver T, Ragan-Kelley B, Pérez F, Granger B, Bussonnier M, Frederic J, et al.
+Jupyter Notebooks -- a publishing format for reproducible computational workflows.
+In: Loizides F, Scmidt B, editors.
+IOS Press; 2016.
+pp.
+87--90.
+doi:\href{https://doi.org/10.3233/978-1-61499-649-1-87}{10.3233/978-1-61499-649-1-87}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-1HteOscVd}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{\textbf{habi/EAWAG: First release, for minting a Zenodo DOI}
-\CSLBlock{David Haberthür} \emph{Zenodo} (2022-07-05) \url{https://doi.org/gqgdtp}
-\CSLBlock{DOI: \href{https://doi.org/10.5281/zenodo.6798632}{10.5281/zenodo.6798632}}}
+\CSLLeftMargin{15. }
+\CSLRightInline{Haberthür D.
+habi/EAWAG: Jupyter notebooks for preparing tomographic scans of a collection of cichlids for analysis.
+Zenodo; 2022.
+doi:\href{https://doi.org/10.5281/zenodo.6798632}{10.5281/zenodo.6798632}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-19qQOHlFN}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{\textbf{pandas-dev/pandas: Pandas}
-\CSLBlock{The Pandas Development Team} \emph{Zenodo} (2022-09-19) \url{https://doi.org/gqw4db}
-\CSLBlock{DOI: \href{https://doi.org/10.5281/zenodo.7093122}{10.5281/zenodo.7093122}}}
+\CSLLeftMargin{16. }
+\CSLRightInline{Team TPD. pandas-dev/pandas: Pandas. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.7093122}{10.5281/zenodo.7093122}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-U5AcoDOX}{}}%
+\CSLLeftMargin{17. }
+\CSLRightInline{McKinney W.
+Data Structures for Statistical Computing in Python.
+Proceedings of the Python in Science Conference.
+SciPy; 2010.
+doi:\href{https://doi.org/10.25080/majora-92bf1922-00a}{10.25080/majora-92bf1922-00a}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-hj1CnyWB}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{\textbf{Dask: Library for dynamic task scheduling}
-\CSLBlock{Dask Development Team} (2016) \url{https://dask.org}}
+\CSLLeftMargin{18. }
+\CSLRightInline{Dask Development Team. Dask: Library for dynamic task scheduling. 2016. Available: \url{https://dask.org}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-OsCpHsJH}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{\textbf{3D Slicer as an image computing platform for the Quantitative Imaging Network}
-\CSLBlock{Andriy Fedorov, Reinhard Beichel, Jayashree Kalpathy-Cramer, Julien Finet, Jean-Christophe Fillion-Robin, Sonia Pujol, Christian Bauer, Dominique Jennings, Fiona Fennessy, Milan Sonka, \ldots{} Ron Kikinis} \emph{Magnetic Resonance Imaging} (2012-11) \url{https://doi.org/gfghgd}
-\CSLBlock{DOI: \href{https://doi.org/10.1016/j.mri.2012.05.001}{10.1016/j.mri.2012.05.001} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/22770690}{22770690} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3466397}{PMC3466397}}}
+\CSLLeftMargin{19. }
+\CSLRightInline{Fedorov A, Beichel R, Kalpathy-Cramer J, Finet J, Fillion-Robin J-C, Pujol S, et al.
+3D Slicer as an image computing platform for the Quantitative Imaging Network.
+Magnetic Resonance Imaging.
+2012;30: 1323--1341.
+doi:\href{https://doi.org/10.1016/j.mri.2012.05.001}{10.1016/j.mri.2012.05.001}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-MwdN6kPV}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{\textbf{SlicerMorph: An open and extensible platform to retrieve, visualize and analyse 3D morphology}
-\CSLBlock{Sara Rolfe, Steve Pieper, Arthur Porto, Kelly Diamond, Julie Winchester, Shan Shan, Henry Kirveslahti, Doug Boyer, Adam Summers, AMurat Maga} \emph{Methods in Ecology and Evolution} (2021-07-22) \url{https://doi.org/gqtgv8}
-\CSLBlock{DOI: \href{https://doi.org/10.1111/2041-210x.13669}{10.1111/2041-210x.13669}}}
+\CSLLeftMargin{20. }
+\CSLRightInline{Rolfe S, Pieper S, Porto A, Diamond K, Winchester J, Shan S, et al.
+SlicerMorph: An open and extensible platform to retrieve, visualize and analyse 3D morphology.
+Methods Ecol Evol.
+2021;12: 1816--1825.
+doi:\href{https://doi.org/10.1111/2041-210x.13669}{10.1111/2041-210x.13669}}
 
-\leavevmode\vadjust pre{\hypertarget{ref-12B4h087w}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{\url{https://w.wiki/5mBK}}
+\leavevmode\vadjust pre{\hypertarget{ref-uYuz0opI}{}}%
+\CSLLeftMargin{21. }
+\CSLRightInline{Main Page. Wikipedia, the free encyclopedia. 2022. Available: \url{https://en.wikipedia.org/w/index.php?title=Main_Page\&oldid=1114291180}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-15FafMZm5}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{\textbf{Mosaic Evolution of Craniofacial Morphologies in Ghost Electric Fishes (Gymnotiformes: Apteronotidae)}
-\CSLBlock{Kassandra L Ford, Maxwell J Bernt, Adam P Summers, James S Albert} \emph{Ichthyology \&amp; Herpetology} (2022-05-27) \url{https://doi.org/gq3gtd}
-\CSLBlock{DOI: \href{https://doi.org/10.1643/i2021016}{10.1643/i2021016}}}
+\CSLLeftMargin{22. }
+\CSLRightInline{Ford KL, Bernt MJ, Summers AP, Albert JS.
+Mosaic Evolution of Craniofacial Morphologies in Ghost Electric Fishes (Gymnotiformes: Apteronotidae).
+Ichthyology \&amp; Herpetology.
+2022;110.
+doi:\href{https://doi.org/10.1643/i2021016}{10.1643/i2021016}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-VPUOQA2P}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{\textbf{RRPP: An
+\CSLLeftMargin{23. }
+\CSLRightInline{Collyer ML, Adams DC. RRPP: An
 \textless scp\textgreater r\textless/scp\textgreater{}
-package for fitting linear models to high‐dimensional data using residual randomization}
-\CSLBlock{Michael L Collyer, Dean C Adams} \emph{Methods in Ecology and Evolution} (2018-05-29) \url{https://doi.org/gdwp9q}
-\CSLBlock{DOI: \href{https://doi.org/10.1111/2041-210x.13029}{10.1111/2041-210x.13029}}}
+package for fitting linear models to high‐dimensional data using residual randomization.
+Freckleton R, editor.
+Methods Ecol Evol.
+2018;9: 1772--1779.
+doi:\href{https://doi.org/10.1111/2041-210x.13029}{10.1111/2041-210x.13029}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Ziptbtib}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{\textbf{Geomorph: Software for geometric morphometric analyses. R package version 4.0.4}
-\CSLBlock{DC Adams, ML Collyer, A Kaliontzopoulou, EK Baken} (2022)\href{\%20https://cran.r-project.org/package=geomorph}{ https://cran.r-project.org/package=geomorph}}
+\CSLLeftMargin{24. }
+\CSLRightInline{Adams DC, Collyer ML, Kaliontzopoulou A, Baken EK.
+Geomorph: Software for geometric morphometric analyses.
+R package version 4.0.4.
+2022.
+Available:\href{\%20https://cran.r-project.org/package=geomorph}{ https://cran.r-project.org/package=geomorph}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-EwNL0C0Y}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{\textbf{RRPP: Linear model evaluation with randomized residuals in a permutation procedure, r package version 0.6.2.}
-\CSLBlock{ML Collyer, DC Adams} (2021) \url{https://cran.r-project.org/package=RRPP}}
+\CSLLeftMargin{25. }
+\CSLRightInline{Collyer ML, Adams DC.
+RRPP: Linear model evaluation with randomized residuals in a permutation procedure, r package version 0.6.2.
+2021.
+Available: \url{https://cran.r-project.org/package=RRPP}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-whEyWyQh}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{\textbf{R: A language and environment for statistical computing}
-\CSLBlock{R Core Team} \emph{R Foundation for Statistical Computing} (2018) \url{https://www.R-project.org/}}
+\CSLLeftMargin{26. }
+\CSLRightInline{R Core Team. R: A language and environment for statistical computing. Vienna, Austria: R Foundation for Statistical Computing; 2018. Available: \url{https://www.R-project.org/}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-QfVloFVu}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{\textbf{RStudio: Integrated development environment for r}
-\CSLBlock{RStudio Team} \emph{RStudio, PBC.} (2022) \url{https://www.rstudio.com/}}
+\CSLLeftMargin{27. }
+\CSLRightInline{RStudio Team. RStudio: Integrated development environment for r. Boston, MA: RStudio, PBC.; 2022. Available: \url{https://www.rstudio.com/}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-a9ZL41Of}{}}%
+\CSLLeftMargin{28. }
+\CSLRightInline{K3D Jupyter. K3D-tools; 2023. Available: \url{https://github.com/K3D-tools/K3D-jupyter}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Q20Bxdsr}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{\textbf{Binder 2.0 - Reproducible, interactive, sharable environments for science at scale}
-\CSLBlock{Project Jupyter, Matthias Bussonnier, Jessica Forde, Jeremy Freeman, Brian Granger, Tim Head, Chris Holdgraf, Kyle Kelley, Gladys Nalvarte, Andrew Osheroff, \ldots{} Carol Willing} \emph{Proceedings of the Python in Science Conference} (2018) \url{https://doi.org/gfwcm6}
-\CSLBlock{DOI: \href{https://doi.org/10.25080/majora-4af1f417-011}{10.25080/majora-4af1f417-011}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-a9ZL41Of}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{\textbf{K3D Jupyter}
-\CSLBlock{K3D-tools} (2023-02-28) \url{https://github.com/K3D-tools/K3D-jupyter}}
+\CSLLeftMargin{29. }
+\CSLRightInline{Jupyter P, Bussonnier M, Forde J, Freeman J, Granger B, Head T, et al.
+Binder 2.0 - Reproducible, interactive, sharable environments for science at scale.
+Proceedings of the Python in Science Conference.
+SciPy; 2018.
+doi:\href{https://doi.org/10.25080/majora-4af1f417-011}{10.25080/majora-4af1f417-011}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{\textbf{Open collaborative writing with Manubot}
-\CSLBlock{Daniel S Himmelstein, Vincent Rubinetti, David R Slochower, Dongbo Hu, Venkat S Malladi, Casey S Greene, Anthony Gitter} \emph{PLOS Computational Biology} (2019-06-24) \url{https://doi.org/c7np}
-\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pcbi.1007128}{10.1371/journal.pcbi.1007128} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31233491}{31233491} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6611653}{PMC6611653}}}
+\CSLLeftMargin{30. }
+\CSLRightInline{Himmelstein DS, Rubinetti V, Slochower DR, Hu D, Malladi VS, Greene CS, et al.
+Open collaborative writing with Manubot.
+Schneidman-Duhovny D, editor.
+PLoS Comput Biol.
+2019;15: e1007128.
+doi:\href{https://doi.org/10.1371/journal.pcbi.1007128}{10.1371/journal.pcbi.1007128}}
 

### 2023-04-14 manuscript.tex
Place holder for 'ethics statement' [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/460de55a8763ac5b835ecc6e7c55af3d489d4d93.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/460de55a8763ac5b835ecc6e7c55af3d489d4d93/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/4700963193

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} of the manuscript to \href{https://www.reviewcommons.org/}{Review Commons}, aiming for \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...3e8bdc73d50e9e237a11c9c271a26468f5a9f151}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...460de55a8763ac5b835ecc6e7c55af3d489d4d93}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/3e8bdc73d50e9e237a11c9c271a26468f5a9f151/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/460de55a8763ac5b835ecc6e7c55af3d489d4d93/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/3e8bdc73d50e9e237a11c9c271a26468f5a9f151}{habi/EAWAG-manuscript@3e8bdc7}
+from \href{https://github.com/habi/EAWAG-manuscript/tree/460de55a8763ac5b835ecc6e7c55af3d489d4d93}{habi/EAWAG-manuscript@460de55}
 on April 14, 2023.
@@
 They were delivered to the Institute of Anatomy for micro-CT imaging sorted into batches of approximately equal length.
+
+\hypertarget{ethics-statement}{%
+\subsubsection{Ethics statement}\label{ethics-statement}}
 

### 2023-04-24 manuscript.tex
Update ethics statement [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/d2e34990ccf22adba0dd011d640baf961cfecd6e.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/d2e34990ccf22adba0dd011d640baf961cfecd6e/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/4785277578

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} of the manuscript to \href{https://www.reviewcommons.org/}{Review Commons}, aiming for \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...460de55a8763ac5b835ecc6e7c55af3d489d4d93}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...d2e34990ccf22adba0dd011d640baf961cfecd6e}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/460de55a8763ac5b835ecc6e7c55af3d489d4d93/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/d2e34990ccf22adba0dd011d640baf961cfecd6e/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/460de55a8763ac5b835ecc6e7c55af3d489d4d93}{habi/EAWAG-manuscript@460de55}
-on April 14, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/d2e34990ccf22adba0dd011d640baf961cfecd6e}{habi/EAWAG-manuscript@d2e3499}
+on April 24, 2023.
 
@@
 \subsubsection{Ethics statement}\label{ethics-statement}}
+
+The study used specimens from an already existing fish collectionm, built over decades of research led by Ole Seehausen and continuing until today.
+All relevant permits for research, the permits for export from the respective country and import to Switzerland were given and the research has followed modern ethical guidelines for scientific research.
 
@@
 \CSLLeftMargin{11. }
-\CSLRightInline{OpenSCAD. {[}cited 14 Apr 2023{]}. Available: \url{https://openscad.org}}
+\CSLRightInline{OpenSCAD. {[}cited 24 Apr 2023{]}. Available: \url{https://openscad.org}}
 

### 2023-04-24 manuscript.tex
Update ethics statement [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/e1e2ef76a476174a4115937d77457037ddec95df.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/e1e2ef76a476174a4115937d77457037ddec95df/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/4786483649

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} of the manuscript to \href{https://www.reviewcommons.org/}{Review Commons}, aiming for \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...d2e34990ccf22adba0dd011d640baf961cfecd6e}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...e1e2ef76a476174a4115937d77457037ddec95df}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/d2e34990ccf22adba0dd011d640baf961cfecd6e/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/d2e34990ccf22adba0dd011d640baf961cfecd6e}{habi/EAWAG-manuscript@d2e3499}
+from \href{https://github.com/habi/EAWAG-manuscript/tree/e1e2ef76a476174a4115937d77457037ddec95df}{habi/EAWAG-manuscript@e1e2ef7}
 on April 24, 2023.
@@
 
-The study used specimens from an already existing fish collectionm, built over decades of research led by Ole Seehausen and continuing until today.
+The study used specimens from an already existing fish collection, built over decades of research led by Ole Seehausen and continuing until today.
 All relevant permits for research, the permits for export from the respective country and import to Switzerland were given and the research has followed modern ethical guidelines for scientific research.
@@
 \CSLLeftMargin{8. }
-\CSLRightInline{Available: \url{https://osf.io/ecmz4}}
+\CSLRightInline{Summers AP. CT Scans - \#ScanAllFish. 2015 {[}cited 24 Apr 2023{]}. Available: \url{https://osf.io/ecmz4/}}
 

### 2023-05-24 manuscript.tex
Update otolith view and export [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/0ae560e58ee5d82015d11abc2962e5875d2d41fe.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/0ae560e58ee5d82015d11abc2962e5875d2d41fe/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5066077464

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} of the manuscript to \href{https://www.reviewcommons.org/}{Review Commons}, aiming for \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...e1e2ef76a476174a4115937d77457037ddec95df}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...0ae560e58ee5d82015d11abc2962e5875d2d41fe}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/0ae560e58ee5d82015d11abc2962e5875d2d41fe/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/e1e2ef76a476174a4115937d77457037ddec95df}{habi/EAWAG-manuscript@e1e2ef7}
-on April 24, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/0ae560e58ee5d82015d11abc2962e5875d2d41fe}{habi/EAWAG-manuscript@0ae560e}
+on May 24, 2023.
 
@@
 \CSLLeftMargin{8. }
-\CSLRightInline{Summers AP. CT Scans - \#ScanAllFish. 2015 {[}cited 24 Apr 2023{]}. Available: \url{https://osf.io/ecmz4/}}
+\CSLRightInline{Summers AP. CT Scans - \#ScanAllFish. 2015 {[}cited 24 May 2023{]}. Available: \url{https://osf.io/ecmz4/}}
 
@@
 \CSLLeftMargin{11. }
-\CSLRightInline{OpenSCAD. {[}cited 24 Apr 2023{]}. Available: \url{https://openscad.org}}
+\CSLRightInline{OpenSCAD. {[}cited 24 May 2023{]}. Available: \url{https://openscad.org}}
 
@@
 2023.
-Available: \url{https://github.com/habi/EAWAG/blob/e5d6be6b416b7c66eaf72a563b0ce5648569f54d/rsync-fishes.sh}}
+Available: \url{https://github.com/habi/EAWAG/blob/48197e8f6e7add0d3610ea1b2820f29c9a536bdf/rsync-fishes.sh}}
 

### 2023-07-03 content/submission/plos_revision1/answer_to_reviewers.md
Document for answering the reviewers
*This* version is a (name-redacted) copy of the email we got from PLOS.

PONE-D-23-10896
Microtomographic investigation of a large corpus of cichlids
PLOS ONE

Dear Dr. Haberthür,

Thank you for submitting your manuscript to PLOS ONE. After careful consideration, we feel that it has merit but does not fully meet PLOS ONE’s publication criteria as it currently stands. Therefore, we invite you to submit a revised version of the manuscript that addresses the points raised during the review process.

Please submit your revised manuscript by Aug 14 2023 11:59PM. If you will need more time than this to complete your revisions, please reply to this message or contact the journal office at plosone@plos.org. When you're ready to submit your revision, log on to https://www.editorialmanager.com/pone/ and select the 'Submissions Needing Revision' folder to locate your manuscript file.

Please include the following items when submitting your revised manuscript:

    A rebuttal letter that responds to each point raised by the academic editor and reviewer(s). You should upload this letter as a separate file labeled 'Response to Reviewers'.
    A marked-up copy of your manuscript that highlights changes made to the original version. You should upload this as a separate file labeled 'Revised Manuscript with Track Changes'.
    An unmarked version of your revised paper without tracked changes. You should upload this as a separate file labeled 'Manuscript'.

If you would like to make changes to your financial disclosure, please include your updated statement in your cover letter. Guidelines for resubmitting your figure files are available below the reviewer comments at the end of this letter.

If applicable, we recommend that you deposit your laboratory protocols in protocols.io to enhance the reproducibility of your results. Protocols.io assigns your protocol its own identifier (DOI) so that it can be cited independently in the future. For instructions see: https://journals.plos.org/plosone/s/submission-guidelines#loc-laboratory-protocols. Additionally, PLOS ONE offers an option for publishing peer-reviewed Lab Protocol articles, which describe protocols hosted on protocols.io. Read more information on sharing protocols at https://plos.org/protocols?utm_medium=editorial-email&utm_source=authorletters&utm_campaign=protocols.

We look forward to receiving your revised manuscript.

Kind regards,

[REDACTED]

Journal requirements:

When submitting your revision, we need you to address these additional requirements.

1. Please ensure that your manuscript meets PLOS ONE's style requirements, including those for file naming. The PLOS ONE style templates can be found at

https://journals.plos.org/plosone/s/file?id=wjVg/PLOSOne_formatting_sample_main_body.pdf and

https://journals.plos.org/plosone/s/file?id=ba62/PLOSOne_formatting_sample_title_authors_affiliations.pdf

2. In your Data Availability statement, you have not specified where the minimal data set underlying the results described in your manuscript can be found. PLOS defines a study's minimal data set as the underlying data used to reach the conclusions drawn in the manuscript and any additional data required to replicate the reported study findings in their entirety. All PLOS journals require that the minimal data set be made fully available. For more information about our data policy, please see http://journals.plos.org/plosone/s/data-availability.

Upon re-submitting your revised manuscript, please upload your study’s minimal underlying data set as either Supporting Information files or to a stable, public repository and include the relevant URLs, DOIs, or accession numbers within your revised cover letter. For a list of acceptable repositories, please see http://journals.plos.org/plosone/s/data-availability#loc-recommended-repositories. Any potentially identifying patient information must be fully anonymized.

Important: If there are ethical or legal restrictions to sharing your data publicly, please explain these restrictions in detail. Please see our guidelines for more information on what we consider unacceptable restrictions to publicly sharing data: http://journals.plos.org/plosone/s/data-availability#loc-unacceptable-data-access-restrictions. Note that it is not acceptable for the authors to be the sole named individuals responsible for ensuring data access.

We will update your Data Availability statement to reflect the information you provide in your cover letter.

[Note: HTML markup is below. Please do not edit.]

Reviewers' comments:

Reviewer's Responses to Questions

Comments to the Author

1. Is the manuscript technically sound, and do the data support the conclusions?

The manuscript must describe a technically sound piece of scientific research with data that supports the conclusions. Experiments must have been conducted rigorously, with appropriate controls, replication, and sample sizes. The conclusions must be drawn appropriately based on the data presented.

Reviewer #1: Yes

Reviewer #2: Yes

2. Has the statistical analysis been performed appropriately and rigorously?

Reviewer #1: Yes

Reviewer #2: I Don't Know

3. Have the authors made all data underlying the findings in their manuscript fully available?

The PLOS Data policy requires authors to make all data underlying the findings described in their manuscript fully available without restriction, with rare exception (please refer to the Data Availability Statement in the manuscript PDF file). The data should be provided as part of the manuscript or its supporting information, or deposited to a public repository. For example, in addition to summary statistics, the data points behind means, medians and variance measures should be available. If there are restrictions on publicly sharing data—e.g. participant privacy or use of data from a third party—those must be specified.

Reviewer #1: Yes

Reviewer #2: Yes

4. Is the manuscript presented in an intelligible fashion and written in standard English?

PLOS ONE does not copyedit accepted manuscripts, so the language in submitted articles must be clear, correct, and unambiguous. Any typographical or grammatical errors should be corrected at revision, so please note any specific errors here.

Reviewer #1: Yes

Reviewer #2: No

5. Review Comments to the Author

Please use the space provided to explain your answers to the questions above. You may also include additional comments for the author, including concerns about dual publication, research ethics, or publication ethics. (Please upload your review as an attachment if it exceeds 20,000 characters)

Reviewer #1: Excellent paper. It was not clear if you could discern daily rings on the otoliths. You might want to discuss if you can use rings on otoliths to age the fish without removing them. Also, do you have to stain the fish to use these rings?

Reviewer #2: I have carefully evaluated the manuscript titled "Microtomographic investigation of a large corpus of cichlids". The authors present a substantial collection of tomographic images from cichlids collected in Lake Victoria, Africa. They showcase significant cranial, maxillary, and otolith images from 362 specimens and provide open-source Python notebooks to facilitate the manipulation and extraction of specific parts. I believe that this work represents a significant contribution to the understanding of cichlids and the application of Micro-CT imaging in fish studies. However, I have some suggestions to improve the manuscript:

The introduction section needs improvement. It is too simplistic and lacks informative details about the state of the art and the justification for the work.

Merging the Materials and Methods section with the Results is not a reasonable way to present the work. It would be better to separate them for clarity.

The section on Micro-computed tomographic imaging should be the core of the paper and explained in more detail. The authors have extensive experience scanning 362 fish specimens of different species and sizes. Therefore, a detailed imaging protocol that can assist readers in obtaining new images should be provided. For example, what criteria did the authors use to select the best set of parameters? It is clear and expected that larger fish would have lower resolution (larger voxel size), but how does the relationship between size and parameters work? How was the filter thickness chosen?

The first sentence of the last paragraph of the subsection Micro-computed tomographic imaging is unclear: "While performing the work, a subset of the data was always present on the production system, for working with it (see Preparation for analysis below)". Please provide more precise information.

The authors should revise the entire "Data analysis" subsection to present a more didactic version that helps any reader use the notebooks. Currently, it seems that only Python users with some expertise can understand what needs to be done. Perhaps the authors could provide a guide or tutorial in the GitHub repository.

How was the sanity check performed (as mentioned in the second paragraph of the subsection "Preparation for Analysis")?

In the same paragraph, the authors mentioned that each tomographic dataset contains around 2700 slices, exceeding the available RAM size on an average high-end workstation. Could you clarify if this limitation affected the analysis and its implications?

The Wikipedia citation in the second paragraph of the subsection "Extraction of oral and pharyngeal jaws..." is not clear. Please provide more specific information or replace the citation with a more appropriate reference.

Regarding the sentence "In total, we compiled an overview of 125 specimens with full head morphology, oral jaw, and lower pharyngeal jaw profiles," why was this done only for a subset of the sample? Please explain the rationale.

The results of the subsection "Principal components analysis of skull landmarks" should be presented in a more accessible manner. Consider providing a tutorial or guide for readers to better understand and apply the analysis. As it currently stands, this subsection may be considered irrelevant for the paper.

The procedure for detecting and extracting otoliths in the subsection "Automatic extraction of otoliths" is not clear. Please provide clearer instructions or guidelines for readers using the notebook.

Use the full words, rather than abbreviations, in figure legends for clarity.

In the discussion section, the authors mentioned acquiring high-resolution tomographic datasets of a large collection of cichlids. However, the statement that "the acquired datasets were imaged over a wide-spanning range of voxel size (3.5–50 μm)" is incorrect. The voxel size is specimen-specific, depending on the size of the fish and the chosen parameters. Please clarify this point to accurately represent the imaging process. The finest resolution was obtained only for small fishes, so specific structures of a fish will have the same image resolution throughout the entire specimen.

It would be beneficial to include references in the discussion section to support the arguments and provide a broader context for the findings.

Overall, the study seems to have spanned a considerable time frame. However, the manuscript's content and structure need improvement to reach a wider audience and effectively communicate the significance of the work. The authors have provided a valuable set of open-source Python notebooks, which is commendable and will be highly useful for the scientific community. However, the workflow needs to be better explained to enable readers to follow the procedures accurately.

By addressing these suggestions, the manuscript will become more comprehensive, accessible, and representative of the valuable contribution made by the authors.

6. PLOS authors have the option to publish the peer review history of their article (what does this mean?). If published, this will include your full peer review and any attached files.

If you choose “no”, your identity will remain anonymous but your review may still be made public.

Do you want your identity to be public for this peer review? For information about this choice, including consent withdrawal, please see our Privacy Policy.

Reviewer #1: Yes: [REDACTED]

Reviewer #2: No

[NOTE: If reviewer comments were submitted as an attachment file, they will be attached to this email and accessible via the submission site. Please log into your account, locate the manuscript record, and check for the action link "View Attachments". If this link does not appear, there are no attachment files.]

While revising your submission, please upload your figure files to the Preflight Analysis and Conversion Engine (PACE) digital diagnostic tool, https://pacev2.apexcovantage.com/. PACE helps ensure that figures meet PLOS requirements. To use PACE, you must first register as a user. Registration is free. Then, login and navigate to the UPLOAD tab, where you will find detailed instructions on how to use the tool. If you encounter any issues or have any questions when using PACE, please email PLOS at figures@plos.org. Please note that Supporting Information files do not need this step.

In compliance with data protection regulations, you may request that we remove your personal registration details at any time. (Remove my information/details). Please contact the publication office if you have any questions.

### 2023-07-03 content/submission/submission/CoverLetter.Cichlids.PLOSONE.tex
Add cover letter

\documentclass[color,english,personal]{ubletter}

\begin{document} 
\begin{letter}{}
\subject{Submission of manuscript for publication}
\opening{To whom it may concern}

Herewith we submit our manuscript on the \emph{Microtomographic investigation of a large
corpus of cichlids} as an original contribution to PLOS ONE.

The manuscript presents how we efficiently and non-destructively acquired three-dimensional tomographic data from a large collection of cichlids from Lake Victoria in Africa.
We imaged the oral and pharyngeal jaws and the whole skull of these fishes as a preparation work for in-depth morphological description.
In the manuscript we describe our method and an present an outlook on analyzing the acquired data; a morphological description of the oral and pharyngeal jaws of the fishes, a three-dimensional geometric morphometrics analysis of landmark features on the skulls, and a robust method to automatically extract the otoliths of the fishes from the tomographic data.

A preprint of the manuscript is available on biorR\(\chi\)iv with the \href{https://doi.org/10.1101/2023.03.30.534917}{DOI:10.1101/2023.03.30.534917}.

We are looking forward to your positive feedback.

\addtolength{\medskipamount}{-\medskipamount} % skip some space with imported image
\closing{Yours sincerely\\\includegraphics[scale=0.618]{_Signature}}
\end{letter}
\end{document}

### 2023-07-03 content/submission/plos_revision1/answer_to_reviewers.md
Make more markdowny
So that we can write into the document and `make` it into a PDF later
with `pandoc`

@@
-PONE-D-23-10896
-Microtomographic investigation of a large corpus of cichlids
-PLOS ONE
+---
+title: Answer to reviewers of PONE-D-23-10896 (Microtomographic investigation of a large corpus of cichlids)
+author: David Haberthür
+date: 3.7.2023
+---
 
-Dear Dr. Haberthür,
+# Review Comments to the Author
 
-Thank you for submitting your manuscript to PLOS ONE.
-After careful consideration, we feel that it has merit but does not fully meet PLOS ONE’s publication criteria as it currently stands.
-Therefore, we invite you to submit a revised version of the manuscript that addresses the points raised during the review process.
-
-Please submit your revised manuscript by Aug 14 2023 11:59PM.
-If you will need more time than this to complete your revisions, please reply to this message or contact the journal office at plosone@plos.org.
-When you're ready to submit your revision, log on to https://www.editorialmanager.com/pone/ and select the 'Submissions Needing Revision' folder to locate your manuscript file.
-
-Please include the following items when submitting your revised manuscript:
-
-    A rebuttal letter that responds to each point raised by the academic editor and reviewer(s). You should upload this letter as a separate file labeled 'Response to Reviewers'.
-    A marked-up copy of your manuscript that highlights changes made to the original version. You should upload this as a separate file labeled 'Revised Manuscript with Track Changes'.
-    An unmarked version of your revised paper without tracked changes. You should upload this as a separate file labeled 'Manuscript'.
-
-If you would like to make changes to your financial disclosure, please include your updated statement in your cover letter.
-Guidelines for resubmitting your figure files are available below the reviewer comments at the end of this letter.
-
-If applicable, we recommend that you deposit your laboratory protocols in protocols.io to enhance the reproducibility of your results.
-Protocols.io assigns your protocol its own identifier (DOI) so that it can be cited independently in the future.
-For instructions see: https://journals.plos.org/plosone/s/submission-guidelines#loc-laboratory-protocols.
-Additionally, PLOS ONE offers an option for publishing peer-reviewed Lab Protocol articles, which describe protocols hosted on protocols.io.
-Read more information on sharing protocols at https://plos.org/protocols?utm_medium=editorial-email&utm_source=authorletters&utm_campaign=protocols.
-
-We look forward to receiving your revised manuscript.
-
-Kind regards,
-
-[REDACTED]
-
-Journal requirements:
-
-When submitting your revision, we need you to address these additional requirements.
-
-1. Please ensure that your manuscript meets PLOS ONE's style requirements, including those for file naming. The PLOS ONE style templates can be found at
-
-https://journals.plos.org/plosone/s/file?id=wjVg/PLOSOne_formatting_sample_main_body.pdf and
-
-https://journals.plos.org/plosone/s/file?id=ba62/PLOSOne_formatting_sample_title_authors_affiliations.pdf
-
-2.
-In your Data Availability statement, you have not specified where the minimal data set underlying the results described in your manuscript can be found.
-PLOS defines a study's minimal data set as the underlying data used to reach the conclusions drawn in the manuscript and any additional data required to replicate the reported study findings in their entirety.
-All PLOS journals require that the minimal data set be made fully available.
-For more information about our data policy, please see http://journals.plos.org/plosone/s/data-availability.
-
-Upon re-submitting your revised manuscript, please upload your study’s minimal underlying data set as either Supporting Information files or to a stable, public repository and include the relevant URLs, DOIs, or accession numbers within your revised cover letter.
-For a list of acceptable repositories, please see http://journals.plos.org/plosone/s/data-availability#loc-recommended-repositories.
-Any potentially identifying patient information must be fully anonymized.
-
-Important: If there are ethical or legal restrictions to sharing your data publicly, please explain these restrictions in detail.
-Please see our guidelines for more information on what we consider unacceptable restrictions to publicly sharing data: http://journals.plos.org/plosone/s/data-availability#loc-unacceptable-data-access-restrictions.
-Note that it is not acceptable for the authors to be the sole named individuals responsible for ensuring data access.
-
-We will update your Data Availability statement to reflect the information you provide in your cover letter.
-
-[Note: HTML markup is below. Please do not edit.]
-
-Reviewers' comments:
-
-Reviewer's Responses to Questions
-
-Comments to the Author
-
-1. Is the manuscript technically sound, and do the data support the conclusions?
-
-The manuscript must describe a technically sound piece of scientific research with data that supports the conclusions.
-Experiments must have been conducted rigorously, with appropriate controls, replication, and sample sizes.
-The conclusions must be drawn appropriately based on the data presented.
-
-Reviewer #1: Yes
-
-Reviewer #2: Yes
-
-2. Has the statistical analysis been performed appropriately and rigorously?
-
-Reviewer #1: Yes
-
-Reviewer #2: I Don't Know
-
-3. Have the authors made all data underlying the findings in their manuscript fully available?
-
-The PLOS Data policy requires authors to make all data underlying the findings described in their manuscript fully available without restriction, with rare exception (please refer to the Data Availability Statement in the manuscript PDF file).
-The data should be provided as part of the manuscript or its supporting information, or deposited to a public repository.
-For example, in addition to summary statistics, the data points behind means, medians and variance measures should be available.
-If there are restrictions on publicly sharing data—e.g.
-participant privacy or use of data from a third party—those must be specified.
-
-Reviewer #1: Yes
-
-Reviewer #2: Yes
-
-4. Is the manuscript presented in an intelligible fashion and written in standard English?
-
-PLOS ONE does not copyedit accepted manuscripts, so the language in submitted articles must be clear, correct, and unambiguous.
-Any typographical or grammatical errors should be corrected at revision, so please note any specific errors here.
-
-Reviewer #1: Yes
-
-Reviewer #2: No
-
-5. Review Comments to the Author
-
-Please use the space provided to explain your answers to the questions above.
-You may also include additional comments for the author, including concerns about dual publication, research ethics, or publication ethics.
-(Please upload your review as an attachment if it exceeds 20,000 characters)
-
-Reviewer #1: Excellent paper.
+> Reviewer #1: Excellent paper.
 It was not clear if you could discern daily rings on the otoliths.
@@
 
-Reviewer #2: I have carefully evaluated the manuscript titled "Microtomographic investigation of a large corpus of cichlids".
+> Reviewer #2: I have carefully evaluated the manuscript titled "Microtomographic investigation of a large corpus of cichlids".
 The authors present a substantial collection of tomographic images from cichlids collected in Lake Victoria, Africa.
@@
 
-The introduction section needs improvement. It is too simplistic and lacks informative details about the state of the art and the justification for the work.
+> The introduction section needs improvement. It is too simplistic and lacks informative details about the state of the art and the justification for the work.
 
-Merging the Materials and Methods section with the Results is not a reasonable way to present the work. It would be better to separate them for clarity.
+> Merging the Materials and Methods section with the Results is not a reasonable way to present the work. It would be better to separate them for clarity.
 
-The section on Micro-computed tomographic imaging should be the core of the paper and explained in more detail.
+> The section on Micro-computed tomographic imaging should be the core of the paper and explained in more detail.
 The authors have extensive experience scanning 362 fish specimens of different species and sizes.
@@
 
-The first sentence of the last paragraph of the subsection Micro-computed tomographic imaging is unclear: "While performing the work, a subset of the data was always present on the production system, for working with it (see Preparation for analysis below)".
+> The first sentence of the last paragraph of the subsection Micro-computed tomographic imaging is unclear: "While performing the work, a subset of the data was always present on the production system, for working with it (see Preparation for analysis below)".
 Please provide more precise information.
 
-The authors should revise the entire "Data analysis" subsection to present a more didactic version that helps any reader use the notebooks.
+> The authors should revise the entire "Data analysis" subsection to present a more didactic version that helps any reader use the notebooks.
 Currently, it seems that only Python users with some expertise can understand what needs to be done.
@@
 
-How was the sanity check performed (as mentioned in the second paragraph of the subsection "Preparation for Analysis")?
+> How was the sanity check performed (as mentioned in the second paragraph of the subsection "Preparation for Analysis")?
 
-In the same paragraph, the authors mentioned that each tomographic dataset contains around 2700 slices, exceeding the available RAM size on an average high-end workstation.
+> In the same paragraph, the authors mentioned that each tomographic dataset contains around 2700 slices, exceeding the available RAM size on an average high-end workstation.
 Could you clarify if this limitation affected the analysis and its implications?
 
-The Wikipedia citation in the second paragraph of the subsection "Extraction of oral and pharyngeal jaws..." is not clear.
+> The Wikipedia citation in the second paragraph of the subsection "Extraction of oral and pharyngeal jaws..." is not clear.
 Please provide more specific information or replace the citation with a more appropriate reference.
 
-Regarding the sentence "In total, we compiled an overview of 125 specimens with full head morphology, oral jaw, and lower pharyngeal jaw profiles," why was this done only for a subset of the sample?
+> Regarding the sentence "In total, we compiled an overview of 125 specimens with full head morphology, oral jaw, and lower pharyngeal jaw profiles," why was this done only for a subset of the sample?
 Please explain the rationale.
 
-The results of the subsection "Principal components analysis of skull landmarks" should be presented in a more accessible manner.
+> The results of the subsection "Principal components analysis of skull landmarks" should be presented in a more accessible manner.
 Consider providing a tutorial or guide for readers to better understand and apply the analysis.
@@
 
-The procedure for detecting and extracting otoliths in the subsection "Automatic extraction of otoliths" is not clear. Please provide clearer instructions or guidelines for readers using the notebook.
+> The procedure for detecting and extracting otoliths in the subsection "Automatic extraction of otoliths" is not clear.
+Please provide clearer instructions or guidelines for readers using the notebook.
 
-Use the full words, rather than abbreviations, in figure legends for clarity.
+> Use the full words, rather than abbreviations, in figure legends for clarity.
 
-In the discussion section, the authors mentioned acquiring high-resolution tomographic datasets of a large collection of cichlids.
+All figure captions have been 'expanded', thanks for noticing this.
+
+> In the discussion section, the authors mentioned acquiring high-resolution tomographic datasets of a large collection of cichlids.
 However, the statement that "the acquired datasets were imaged over a wide-spanning range of voxel size (3.5–50 μm)" is incorrect.
@@
 
-It would be beneficial to include references in the discussion section to support the arguments and provide a broader context for the findings.
+> It would be beneficial to include references in the discussion section to support the arguments and provide a broader context for the findings.
 
-Overall, the study seems to have spanned a considerable time frame.
+> Overall, the study seems to have spanned a considerable time frame.
 However, the manuscript's content and structure need improvement to reach a wider audience and effectively communicate the significance of the work.
@@
 
-By addressing these suggestions, the manuscript will become more comprehensive, accessible, and representative of the valuable contribution made by the authors.
-
-6. PLOS authors have the option to publish the peer review history of their article (what does this mean?). If published, this will include your full peer review and any attached files.
-
-If you choose “no”, your identity will remain anonymous but your review may still be made public.
-
-Do you want your identity to be public for this peer review? For information about this choice, including consent withdrawal, please see our Privacy Policy.
-
-Reviewer #1: Yes: [REDACTED]
-
-Reviewer #2: No
-
-[NOTE: If reviewer comments were submitted as an attachment file, they will be attached to this email and accessible via the submission site.
-Please log into your account, locate the manuscript record, and check for the action link "View Attachments".
-If this link does not appear, there are no attachment files.]
-
-While revising your submission, please upload your figure files to the Preflight Analysis and Conversion Engine (PACE) digital diagnostic tool, https://pacev2.apexcovantage.com/.
-PACE helps ensure that figures meet PLOS requirements.
-To use PACE, you must first register as a user.
-Registration is free.
-Then, login and navigate to the UPLOAD tab, where you will find detailed instructions on how to use the tool.
-If you encounter any issues or have any questions when using PACE, please email PLOS at figures@plos.org.
-Please note that Supporting Information files do not need this step.
-
-In compliance with data protection regulations, you may request that we remove your personal registration details at any time.
-(Remove my information/details).
-Please contact the publication office if you have any questions.
+> By addressing these suggestions, the manuscript will become more comprehensive, accessible, and representative of the valuable contribution made by the authors.

### 2023-07-03 manuscript.tex
Add submitted version to header [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/ced46ab1b2fbda07ed353d379d6530b9405eee43.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/ced46ab1b2fbda07ed353d379d6530b9405eee43/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5445925753

@@
 \emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
-\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} of the manuscript to \href{https://www.reviewcommons.org/}{Review Commons}, aiming for \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...0ae560e58ee5d82015d11abc2962e5875d2d41fe}{has been updated} since submission.}
+\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...ced46ab1b2fbda07ed353d379d6530b9405eee43}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/0ae560e58ee5d82015d11abc2962e5875d2d41fe/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/ced46ab1b2fbda07ed353d379d6530b9405eee43/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/0ae560e58ee5d82015d11abc2962e5875d2d41fe}{habi/EAWAG-manuscript@0ae560e}
-on May 24, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/ced46ab1b2fbda07ed353d379d6530b9405eee43}{habi/EAWAG-manuscript@ced46ab}
+on July 3, 2023.
 
@@
 
-Cichlid fish in African lakes are powerful model systems in speciation and adaptive evolutionary radiation research {[}\protect\hyperlink{ref-TUQFenhc}{1},\protect\hyperlink{ref-W2f2SDjn}{2}{]}.
-The functional decoupling of their oral and pharyngeal jaws is hypothesized to be a factor in making cichlids unusually versatile in their feeding and allowing them the ability to adapt to a wide range of environmental factors {[}\protect\hyperlink{ref-1GEljkDsf}{3}{]}.
+Cichlid fish in African lakes are powerful model systems in speciation and adaptive evolutionary radiation research {[}\protect\hyperlink{ref-TUQFenhc}{1}--\protect\hyperlink{ref-WVIa4CH0}{3}{]}.
+The functional decoupling of their oral and pharyngeal jaws is hypothesized to be a factor in making cichlids unusually versatile in their feeding and allowing them the ability to adapt to a wide range of environmental factors {[}\protect\hyperlink{ref-1GEljkDsf}{4}{]}.
 The hypothesis is that the fusion of the lower pharyngeal jaws makes that jaw system a powerful food processing tool, in turn releasing the oral jaws from functional constraint.
@@
 
-Even though the evolutionary diversification of cichlid fish radiations in Lake Victoria in Africa is a well-researched issue it remains a complex system in need of further study {[}\protect\hyperlink{ref-W2f2SDjn}{2},\protect\hyperlink{ref-c3poTogo}{4}{]}.
+Even though the evolutionary diversification of cichlid fish radiations in Lake Victoria in Africa is a well researched issue it remains a complex system in need of further study {[}\protect\hyperlink{ref-W2f2SDjn}{2},\protect\hyperlink{ref-c3poTogo}{5}{]}.
 We aim to better understand the functional anatomy of the skulls and jaws in these fish in order to test the functional decoupling and other hypotheses about what may facilitate exceptionally high rates of morphological evolution.
@@
 The collection of cichlid fish available is extremely valuable, hence a nondestructive imaging method is paramount for studying these samples.
-Since micro--computed tomography can be regarded as nondestructive method for biological samples, it is the ideal imaging method for investigating the oral and pharyngeal jaws as well as the skull features of the fish presented in this study {[}\protect\hyperlink{ref-19h9vxsYG}{5}{]}.
+Since micro--computed tomography can be regarded as nondestructive method for biological samples, it is the ideal imaging method for investigating the oral and pharyngeal jaws as well as the skull features of the fish presented in this study {[}\protect\hyperlink{ref-19h9vxsYG}{6}{]}.
 
@@
 X-ray microtomography is a valuable tool to gain insights into the inner structure of highly diverse samples, namely for specimens related to research done in the biomedical sciences.
-Microtomographic imaging has been employed as a method of choice to nondestructively assess the morphology of different fish species, large and small {[}\protect\hyperlink{ref-19h9vxsYG}{5}{]}.
-For a small overview of analyses which are possible with X-ray microtomographic imaging in relation to fish biology and morphology, see prior work of the authors of this manuscript {[}\protect\hyperlink{ref-19h9vxsYG}{5}--\protect\hyperlink{ref-BDrCSu8p}{7}{]} as well as other studies {[}\protect\hyperlink{ref-3rxGCEvJ}{8}{]}.
+Microtomographic imaging has been employed as a method of choice to nondestructively assess the morphology of different fish species, large and small {[}\protect\hyperlink{ref-19h9vxsYG}{6}{]}.
+For a small overview of analyses which are possible with X-ray microtomographic imaging in relation to fish biology and morphology, see prior work of the authors of this manuscript {[}\protect\hyperlink{ref-19h9vxsYG}{6}--\protect\hyperlink{ref-BDrCSu8p}{8}{]} as well as other studies {[}\protect\hyperlink{ref-3rxGCEvJ}{9}{]}.
 
@@
 We used a custom-made sample-holder to scan each of the fish in our machines.
-It was 3D-printed on a Form 2 desktop stereolithography printer (Formlabs, Somerville, Massachusetts, USA), the file for printing the holder is available online {[}\protect\hyperlink{ref-VCZPOv2f}{9}{]} as part of a library of sample holders for tomographic scanning of biomedical samples {[}\protect\hyperlink{ref-115PPSuQp}{10}{]}.
-The original \emph{OpenSCAD} {[}\protect\hyperlink{ref-wsjdcTeC}{11}{]} file {[}\protect\hyperlink{ref-f7OzrzUv}{12}{]} is parametrized to effortlessly generate a file for 3D-printing sample holders to accommodate the varying width, height and length classes of the fish.
+It was 3D-printed on a Form 2 desktop stereolithography printer (Formlabs, Somerville, Massachusetts, USA), the file for printing the holder is available online {[}\protect\hyperlink{ref-VCZPOv2f}{10}{]} as part of a library of sample holders for tomographic scanning of biomedical samples {[}\protect\hyperlink{ref-115PPSuQp}{11}{]}.
+The original \emph{OpenSCAD} {[}\protect\hyperlink{ref-wsjdcTeC}{12}{]} file {[}\protect\hyperlink{ref-f7OzrzUv}{13}{]} is parametrized to effortlessly generate a file for 3D-printing sample holders to accommodate the varying width, height and length classes of the fish.
 
@@
 While performing the work, a subset of the data was always present on the production system, for working with it (see \protect\hyperlink{preparation-for-analysis}{Preparation for analysis} below).
-A small bash script {[}\protect\hyperlink{ref-ZjgrPHTa}{13}{]} was used to generate redundant (archival) copies of the raw projection images and copy all the files to a shared network drive on the `Research Storage' infrastructure of the University of Bern, enabling collaboration on the data by all authorized persons at the same time.
+A small bash script {[}\protect\hyperlink{ref-ZjgrPHTa}{14}{]} was used to generate redundant (archival) copies of the raw projection images and copy all the files to a shared network drive on the `Research Storage' infrastructure of the University of Bern, enabling collaboration on the data by all authorized persons at the same time.
 
@@
 
-We wrote a set of \emph{Jupyter} {[}\protect\hyperlink{ref-pQ6Wbz73}{14}{]} notebooks with \emph{Python} code to work with the images and wrangle the acquired data.
+We wrote a set of \emph{Jupyter} {[}\protect\hyperlink{ref-pQ6Wbz73}{15}{]} notebooks with \emph{Python} code to work with the images and wrangle the acquired data.
 The notebooks were written at the start of the project, to be able to process new scans as soon as they were reconstructed.
@@
 
-All analysis notebooks for this work are available online {[}\protect\hyperlink{ref-1HteOscVd}{15}{]}.
+All analysis notebooks for this work are available online {[}\protect\hyperlink{ref-1HteOscVd}{16}{]}.
 
@@
 
-At first, \emph{all} log files of \emph{all} the data present in the processed folder were read into a \emph{pandas} {[}\protect\hyperlink{ref-19qQOHlFN}{16},\protect\hyperlink{ref-U5AcoDOX}{17}{]} dataframe.
+At first, \emph{all} log files of \emph{all} the data present in the processed folder were read into a \emph{pandas} {[}\protect\hyperlink{ref-19qQOHlFN}{17},\protect\hyperlink{ref-U5AcoDOX}{18}{]} dataframe.
 This already enabled us to extract the specimen name and scan, since we performed multiple scans for each specimen, i.e.~a low resolution scan with large field of view for the whole head and one or two scans in high resolution focusing on the region of the oral and pharyngeal jaws.
@@
 
-After performing `sanity checks' of the data and reconstruction parameters, we used \emph{Dask} {[}\protect\hyperlink{ref-hj1CnyWB}{18}{]} to efficiently access the tomographic data on disk (in the end amounting to a total of nearly a million single images).
+After performing `sanity checks' of the data and reconstruction parameters, we used \emph{Dask} {[}\protect\hyperlink{ref-hj1CnyWB}{19}{]} to efficiently access the tomographic data on disk (in the end amounting to a total of nearly a million single images).
 On average, each of the tomographic datasets contains around 2700 slices, so the total size of the acquired data exceeds the RAM size available on an average high-end workstation.
@@
 
-To extract the oral jaw (OJ) and pharyngeal jaw (PJ) of the fish, we used \href{https://www.slicer.org}{\emph{3D Slicer}} (Version 4.11.20210226) {[}\protect\hyperlink{ref-OsCpHsJH}{19}{]} extended with the \emph{SlicerMorph} tools {[}\protect\hyperlink{ref-MwdN6kPV}{20}{]} which aim to help biologists work with 3D specimen data.
+To extract the oral jaw (OJ) and pharyngeal jaw (PJ) of the fish, we used \href{https://www.slicer.org}{\emph{3D Slicer}} (Version 4.11.20210226) {[}\protect\hyperlink{ref-OsCpHsJH}{20}{]} extended with the \emph{SlicerMorph} tools {[}\protect\hyperlink{ref-MwdN6kPV}{21}{]} which aim to help biologists work with 3D specimen data.
 The reconstructed image stacks were loaded into \href{https://www.slicer.org/wiki/Documentation/Labs/ImageStacks}{\emph{ImageStacks}}, depending on their size we reduced the image resolution (i.e.~downscaled the images) for this first step.
@@
 
-Processed regions of interest were exported as \texttt{Nrrd} {[}\protect\hyperlink{ref-uYuz0opI}{21}, =Nrrd\&oldid=1085264080{]} files.
+Processed regions of interest were exported as \texttt{Nrrd} {[}\protect\hyperlink{ref-uYuz0opI}{22}, =Nrrd\&oldid=1085264080{]} files.
 The three-dimensional visualizations of all regions of interest for each specimen were compiled into overview images (see Figure \ref{fig:104016} for an example from the compilation document).
@@
 Current studies are using 3D geometric morphometrics to compare the morphological shape of these scanned cichlids using statistical analysis.
-We used a homologous landmark scheme across one-half of the skull for higher density of shape information {[}\protect\hyperlink{ref-BDrCSu8p}{7},\protect\hyperlink{ref-15FafMZm5}{22}{]}, and landmarks were placed on each specimen using \emph{3D Slicer}.
-To examine differences in shape across the species sampled, we performed a Generalized Procrustes Superimposition on the landmark data to remove the effects of location, size, and rotation from the analysis using the \emph{geomorph} package in \emph{R} (Version 4.2.1) with \emph{RStudio} (Version 2022.07.2+576) {[}\protect\hyperlink{ref-VPUOQA2P}{23}--\protect\hyperlink{ref-EwNL0C0Y}{25},\protect\hyperlink{ref-whEyWyQh}{26},\protect\hyperlink{ref-QfVloFVu}{27}{]}.
+We used a homologous landmark scheme across one-half of the skull for higher density of shape information {[}\protect\hyperlink{ref-BDrCSu8p}{8},\protect\hyperlink{ref-15FafMZm5}{23}{]}, and landmarks were placed on each specimen using \emph{3D Slicer}.
+To examine differences in shape across the species sampled, we performed a Generalized Procrustes Superimposition on the landmark data to remove the effects of location, size, and rotation from the analysis using the \emph{geomorph} package in \emph{R} (Version 4.2.1) with \emph{RStudio} (Version 2022.07.2+576) {[}\protect\hyperlink{ref-VPUOQA2P}{24}--\protect\hyperlink{ref-EwNL0C0Y}{26},\protect\hyperlink{ref-whEyWyQh}{27},\protect\hyperlink{ref-QfVloFVu}{28}{]}.
 This process brings all specimens to a common origin, scales the landmarks to a unit centroid size, and rotates specimens to reduce distances between landmarks.
@@
 We devised an image processing method to automatically and robustly detect the location of the otoliths in the heads of the cichlids we scanned and to extract them from the original data.
-The whole method is implemented in its own \href{https://github.com/habi/EAWAG/blob/master/ExtractOtoliths.ipynb}{\emph{Jupyter} notebook} (part of the aforementioned analysis repository {[}\protect\hyperlink{ref-1HteOscVd}{15}{]}).
+The whole method is implemented in its own \href{https://github.com/habi/EAWAG/blob/master/ExtractOtoliths.ipynb}{\emph{Jupyter} notebook} (part of the aforementioned analysis repository {[}\protect\hyperlink{ref-1HteOscVd}{16}{]}).
 
@@
 The extracted otoliths are thus prepared for further analysis and visualization.
-The simple three-dimensional visualization is integrated in the aforementioned \emph{Jupyter} notebook through an integrated visualization library {[}\protect\hyperlink{ref-a9ZL41Of}{28}{]} and is also shown in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}.
+The simple three-dimensional visualization is integrated in the aforementioned \emph{Jupyter} notebook through an integrated visualization library {[}\protect\hyperlink{ref-a9ZL41Of}{29}{]} and is also shown in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}.
 
@@
 
-The notebook for extracting the otoliths can be run in your browser without installing any additional software (via \emph{Binder} {[}\protect\hyperlink{ref-Q20Bxdsr}{29}{]}).
-To do this, one starts the notebook by \href{https://mybinder.org/v2/gh/habi/eawag/HEAD?labpath=ExtractOtoliths.ipynb}{clicking a single button} in the \href{https://github.com/habi/EAWAG/blob/master/README.md}{README file} of the \href{https://github.com/habi/EAWAG}{project repository} {[}\protect\hyperlink{ref-1HteOscVd}{15}{]}.
+The notebook for extracting the otoliths can be run in your browser without installing any additional software (via \emph{Binder} {[}\protect\hyperlink{ref-Q20Bxdsr}{30}{]}).
+To do this, one starts the notebook by \href{https://mybinder.org/v2/gh/habi/eawag/HEAD?labpath=ExtractOtoliths.ipynb}{clicking a single button} in the \href{https://github.com/habi/EAWAG/blob/master/README.md}{README file} of the \href{https://github.com/habi/EAWAG}{project repository} {[}\protect\hyperlink{ref-1HteOscVd}{16}{]}.
 This starts a computing environment in the cloud, downloads the tomographic data we acquired of \emph{one} specimen, and performs both the otolith extraction and visualization in your browser.
@@
 The workflow is relying only on free and open-source software and can thus be used and verified independently by any interested reader.
-All the \emph{Jupyter} notebook described herein is also freely available online {[}\protect\hyperlink{ref-1HteOscVd}{15}{]}.
+All the \emph{Jupyter} notebook described herein is also freely available online {[}\protect\hyperlink{ref-1HteOscVd}{16}{]}.
 
@@
 We are grateful to the \href{https//www.mic.unibe.ch/}{Microscopy Imaging Center} of the University of Bern for the infrastructural support.
-We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{30}{]} for helping us write this manuscript collaboratively.
+We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{31}{]} for helping us write this manuscript collaboratively.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-WVIa4CH0}{}}%
+\CSLLeftMargin{3. }
+\CSLRightInline{Konings AF, Wisor JM, Stauffer JR Jr.
+Microcomputed tomography used to link head morphology and observed feeding behavior in cichlids of Lake Malaŵi.
+Ecol Evol.
+2021;11: 4605--4615.
+doi:\href{https://doi.org/10.1002/ece3.7359}{10.1002/ece3.7359}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-1GEljkDsf}{}}%
-\CSLLeftMargin{3. }
+\CSLLeftMargin{4. }
 \CSLRightInline{Liem KF. Evolutionary Strategies and Morphological Innovations: Cichlid Pharyngeal Jaws. Systematic Zoology. 1973;22: 425. doi:\href{https://doi.org/10.2307/2412950}{10.2307/2412950}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-c3poTogo}{}}%
-\CSLLeftMargin{4. }
+\CSLLeftMargin{5. }
 \CSLRightInline{Seehausen O.
 Process and pattern in cichlid radiations -- inferences for understanding unusually high rates of evolutionary diversification.
-New Phytol.
+New Phytologist.
 2015;207: 304--312.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-19h9vxsYG}{}}%
-\CSLLeftMargin{5. }
+\CSLLeftMargin{6. }
 \CSLRightInline{Ford KL, Albert JS, Summers AP, Hedrick BP, Schachner ER, Jones AS, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-8Pmc2mI8}{}}%
-\CSLLeftMargin{6. }
+\CSLLeftMargin{7. }
 \CSLRightInline{Messerli M, Aaldijk D, Haberthür D, Röss H, García-Poyatos C, Sande-Melón M, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-BDrCSu8p}{}}%
-\CSLLeftMargin{7. }
+\CSLLeftMargin{8. }
 \CSLRightInline{Ford KL, Peterson R, Bernt M, Albert JS.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3rxGCEvJ}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Summers AP. CT Scans - \#ScanAllFish. 2015 {[}cited 24 May 2023{]}. Available: \url{https://osf.io/ecmz4/}}
+\CSLLeftMargin{9. }
+\CSLRightInline{Available: \url{https://osf.io/ecmz4}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-VCZPOv2f}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{OpenSCAD models. TomoGraphics; 2022. Available: \url{https://github.com/TomoGraphics/Hol3Drs/blob/dedca665a77fa782c103eed63b866b2cceb30de9/STL/EAWAG.Fish.stl}}
+\CSLLeftMargin{10. }
+\CSLRightInline{Available: \url{https://github.com/TomoGraphics/Hol3Drs/blob/master/STL/EAWAG.Fish.stl}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-115PPSuQp}{}}%
-\CSLLeftMargin{10. }
+\CSLLeftMargin{11. }
 \CSLRightInline{Haberthür D. TomoGraphics/Hol3Drs: A release. Zenodo; 2019. doi:\href{https://doi.org/10.5281/zenodo.2587555}{10.5281/zenodo.2587555}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{OpenSCAD. {[}cited 24 May 2023{]}. Available: \url{https://openscad.org}}
+\CSLLeftMargin{12. }
+\CSLRightInline{OpenSCAD. {[}cited 3 Jul 2023{]}. Available: \url{https://openscad.org}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-f7OzrzUv}{}}%
-\CSLLeftMargin{12. }
+\CSLLeftMargin{13. }
 \CSLRightInline{OpenSCAD models. TomoGraphics; 2022. Available: \url{https://github.com/TomoGraphics/Hol3Drs/blob/dedca665a77fa782c103eed63b866b2cceb30de9/EAWAG.Fish.scad}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZjgrPHTa}{}}%
-\CSLLeftMargin{13. }
+\CSLLeftMargin{14. }
 \CSLRightInline{Haberthür D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pQ6Wbz73}{}}%
-\CSLLeftMargin{14. }
+\CSLLeftMargin{15. }
 \CSLRightInline{Kluyver T, Ragan-Kelley B, Pérez F, Granger B, Bussonnier M, Frederic J, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1HteOscVd}{}}%
-\CSLLeftMargin{15. }
+\CSLLeftMargin{16. }
 \CSLRightInline{Haberthür D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-19qQOHlFN}{}}%
-\CSLLeftMargin{16. }
+\CSLLeftMargin{17. }
 \CSLRightInline{Team TPD. pandas-dev/pandas: Pandas. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.7093122}{10.5281/zenodo.7093122}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-U5AcoDOX}{}}%
-\CSLLeftMargin{17. }
+\CSLLeftMargin{18. }
 \CSLRightInline{McKinney W.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hj1CnyWB}{}}%
-\CSLLeftMargin{18. }
+\CSLLeftMargin{19. }
 \CSLRightInline{Dask Development Team. Dask: Library for dynamic task scheduling. 2016. Available: \url{https://dask.org}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-OsCpHsJH}{}}%
-\CSLLeftMargin{19. }
+\CSLLeftMargin{20. }
 \CSLRightInline{Fedorov A, Beichel R, Kalpathy-Cramer J, Finet J, Fillion-Robin J-C, Pujol S, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MwdN6kPV}{}}%
-\CSLLeftMargin{20. }
+\CSLLeftMargin{21. }
 \CSLRightInline{Rolfe S, Pieper S, Porto A, Diamond K, Winchester J, Shan S, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-uYuz0opI}{}}%
-\CSLLeftMargin{21. }
+\CSLLeftMargin{22. }
 \CSLRightInline{Main Page. Wikipedia, the free encyclopedia. 2022. Available: \url{https://en.wikipedia.org/w/index.php?title=Main_Page\&oldid=1114291180}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-15FafMZm5}{}}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{23. }
 \CSLRightInline{Ford KL, Bernt MJ, Summers AP, Albert JS.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-VPUOQA2P}{}}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{24. }
 \CSLRightInline{Collyer ML, Adams DC. RRPP: An
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Ziptbtib}{}}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{25. }
 \CSLRightInline{Adams DC, Collyer ML, Kaliontzopoulou A, Baken EK.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-EwNL0C0Y}{}}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{26. }
 \CSLRightInline{Collyer ML, Adams DC.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-whEyWyQh}{}}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{27. }
 \CSLRightInline{R Core Team. R: A language and environment for statistical computing. Vienna, Austria: R Foundation for Statistical Computing; 2018. Available: \url{https://www.R-project.org/}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-QfVloFVu}{}}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{28. }
 \CSLRightInline{RStudio Team. RStudio: Integrated development environment for r. Boston, MA: RStudio, PBC.; 2022. Available: \url{https://www.rstudio.com/}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-a9ZL41Of}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{29. }
 \CSLRightInline{K3D Jupyter. K3D-tools; 2023. Available: \url{https://github.com/K3D-tools/K3D-jupyter}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Q20Bxdsr}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Jupyter P, Bussonnier M, Forde J, Freeman J, Granger B, Head T, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Himmelstein DS, Rubinetti V, Slochower DR, Hu D, Malladi VS, Greene CS, et al.

### 2023-07-03 manuscript.tex
Add submitted version to header [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/0dada243d2d4e03345245209804557977c66c438.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/0dada243d2d4e03345245209804557977c66c438/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5445961425

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...ced46ab1b2fbda07ed353d379d6530b9405eee43}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...0dada243d2d4e03345245209804557977c66c438}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/ced46ab1b2fbda07ed353d379d6530b9405eee43/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/0dada243d2d4e03345245209804557977c66c438/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/ced46ab1b2fbda07ed353d379d6530b9405eee43}{habi/EAWAG-manuscript@ced46ab}
+from \href{https://github.com/habi/EAWAG-manuscript/tree/0dada243d2d4e03345245209804557977c66c438}{habi/EAWAG-manuscript@0dada24}
 on July 3, 2023.

### 2023-07-03 manuscript.tex
Add submitted version to header [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/c614d1218708bc438846661ff5c8ed6f15d3469b.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/c614d1218708bc438846661ff5c8ed6f15d3469b/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5445980821

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...0dada243d2d4e03345245209804557977c66c438}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...c614d1218708bc438846661ff5c8ed6f15d3469b}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/0dada243d2d4e03345245209804557977c66c438/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/c614d1218708bc438846661ff5c8ed6f15d3469b/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/0dada243d2d4e03345245209804557977c66c438}{habi/EAWAG-manuscript@0dada24}
+from \href{https://github.com/habi/EAWAG-manuscript/tree/c614d1218708bc438846661ff5c8ed6f15d3469b}{habi/EAWAG-manuscript@c614d12}
 on July 3, 2023.

### 2023-07-04 manuscript.tex
Expand abbreviations and information in figure legends [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/a9633de5317eab4c8df584555033c6c11e4d89c5.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/a9633de5317eab4c8df584555033c6c11e4d89c5/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5453497733

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...c614d1218708bc438846661ff5c8ed6f15d3469b}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...a9633de5317eab4c8df584555033c6c11e4d89c5}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/c614d1218708bc438846661ff5c8ed6f15d3469b/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/a9633de5317eab4c8df584555033c6c11e4d89c5/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/c614d1218708bc438846661ff5c8ed6f15d3469b}{habi/EAWAG-manuscript@c614d12}
-on July 3, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/a9633de5317eab4c8df584555033c6c11e4d89c5}{habi/EAWAG-manuscript@a9633de}
+on July 4, 2023.
 
@@
 \includegraphics{images/104016.png}
-\caption{Overview of data from sample 104016,~\emph{Enterochromis I cinctus} (St.~E).
+\caption{Overview of data from sample 104016,~\emph{Enterochromis I cinctus}, from `Station E' in the transect of Mwanza Bay at the southern edge of Lake Victoria.
+A map showing the detailed location of `Station E' is shown in Fig. 1 of {[}\protect\hyperlink{ref-JtHcU2O2}{23}{]}.
 Panel A: Three-dimensional visualization of the head scan.
@@
 Current studies are using 3D geometric morphometrics to compare the morphological shape of these scanned cichlids using statistical analysis.
-We used a homologous landmark scheme across one-half of the skull for higher density of shape information {[}\protect\hyperlink{ref-BDrCSu8p}{8},\protect\hyperlink{ref-15FafMZm5}{23}{]}, and landmarks were placed on each specimen using \emph{3D Slicer}.
-To examine differences in shape across the species sampled, we performed a Generalized Procrustes Superimposition on the landmark data to remove the effects of location, size, and rotation from the analysis using the \emph{geomorph} package in \emph{R} (Version 4.2.1) with \emph{RStudio} (Version 2022.07.2+576) {[}\protect\hyperlink{ref-VPUOQA2P}{24}--\protect\hyperlink{ref-EwNL0C0Y}{26},\protect\hyperlink{ref-whEyWyQh}{27},\protect\hyperlink{ref-QfVloFVu}{28}{]}.
+We used a homologous landmark scheme across one-half of the skull for higher density of shape information {[}\protect\hyperlink{ref-BDrCSu8p}{8},\protect\hyperlink{ref-15FafMZm5}{24}{]}, and landmarks were placed on each specimen using \emph{3D Slicer}.
+To examine differences in shape across the species sampled, we performed a Generalized Procrustes Superimposition on the landmark data to remove the effects of location, size, and rotation from the analysis using the \emph{geomorph} package in \emph{R} (Version 4.2.1) with \emph{RStudio} (Version 2022.07.2+576) {[}\protect\hyperlink{ref-VPUOQA2P}{25}--\protect\hyperlink{ref-EwNL0C0Y}{27},\protect\hyperlink{ref-whEyWyQh}{28},\protect\hyperlink{ref-QfVloFVu}{29}{]}.
 This process brings all specimens to a common origin, scales the landmarks to a unit centroid size, and rotates specimens to reduce distances between landmarks.
@@
 The top row shows the found location of the otolith center in each of the three anatomical directions.
-The bottom row shows a MIP of each of the three anatomical directions of the extracted otolith region.}\label{fig:otolithextraction}
+The bottom row shows a maximum intensity projection of each of the three anatomical directions of the extracted otolith region.}\label{fig:otolithextraction}
 }
@@
 The extracted otoliths are thus prepared for further analysis and visualization.
-The simple three-dimensional visualization is integrated in the aforementioned \emph{Jupyter} notebook through an integrated visualization library {[}\protect\hyperlink{ref-a9ZL41Of}{29}{]} and is also shown in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}.
+The simple three-dimensional visualization is integrated in the aforementioned \emph{Jupyter} notebook through an integrated visualization library {[}\protect\hyperlink{ref-a9ZL41Of}{30}{]} and is also shown in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}.
 
@@
 \includegraphics{images/104016.head.rec.otolith.region.3D.png}
-\caption{Static three-dimensional view of extracted otoliths of specimen 104016.
+\caption{Three-dimensional view of extracted otoliths of specimen 104016.
 The specimen was scanned with an isotropic voxel size of 13 μm.
 The extracted otolith has a size of approximately 250 x 350 x 150 pixels.
-The axes are labeled in mm steps.
+The axes labels correspond to mm.
 A dynamic view of the visualization is available in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}.}\label{fig:otolith3d}
@@
 
-The notebook for extracting the otoliths can be run in your browser without installing any additional software (via \emph{Binder} {[}\protect\hyperlink{ref-Q20Bxdsr}{30}{]}).
+The notebook for extracting the otoliths can be run in your browser without installing any additional software (via \emph{Binder} {[}\protect\hyperlink{ref-Q20Bxdsr}{31}{]}).
 To do this, one starts the notebook by \href{https://mybinder.org/v2/gh/habi/eawag/HEAD?labpath=ExtractOtoliths.ipynb}{clicking a single button} in the \href{https://github.com/habi/EAWAG/blob/master/README.md}{README file} of the \href{https://github.com/habi/EAWAG}{project repository} {[}\protect\hyperlink{ref-1HteOscVd}{16}{]}.
@@
 We are grateful to the \href{https//www.mic.unibe.ch/}{Microscopy Imaging Center} of the University of Bern for the infrastructural support.
-We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{31}{]} for helping us write this manuscript collaboratively.
+We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{32}{]} for helping us write this manuscript collaboratively.
 
@@
 \CSLLeftMargin{12. }
-\CSLRightInline{OpenSCAD. {[}cited 3 Jul 2023{]}. Available: \url{https://openscad.org}}
+\CSLRightInline{OpenSCAD. {[}cited 4 Jul 2023{]}. Available: \url{https://openscad.org}}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-JtHcU2O2}{}}%
+\CSLLeftMargin{23. }
+\CSLRightInline{Kishe-Machumu MA, van Rijssel JC, Poste A, Hecky RE, Witte F.
+Stable isotope evidence from formalin--ethanol-preserved specimens indicates dietary shifts and increasing diet overlap in Lake Victoria cichlids.
+Hydrobiologia.
+2016;791: 155--173.
+doi:\href{https://doi.org/10.1007/s10750-016-2925-1}{10.1007/s10750-016-2925-1}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-15FafMZm5}{}}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{24. }
 \CSLRightInline{Ford KL, Bernt MJ, Summers AP, Albert JS.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-VPUOQA2P}{}}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{25. }
 \CSLRightInline{Collyer ML, Adams DC. RRPP: An
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Ziptbtib}{}}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{26. }
 \CSLRightInline{Adams DC, Collyer ML, Kaliontzopoulou A, Baken EK.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-EwNL0C0Y}{}}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{27. }
 \CSLRightInline{Collyer ML, Adams DC.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-whEyWyQh}{}}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{28. }
 \CSLRightInline{R Core Team. R: A language and environment for statistical computing. Vienna, Austria: R Foundation for Statistical Computing; 2018. Available: \url{https://www.R-project.org/}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-QfVloFVu}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{29. }
 \CSLRightInline{RStudio Team. RStudio: Integrated development environment for r. Boston, MA: RStudio, PBC.; 2022. Available: \url{https://www.rstudio.com/}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-a9ZL41Of}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{30. }
 \CSLRightInline{K3D Jupyter. K3D-tools; 2023. Available: \url{https://github.com/K3D-tools/K3D-jupyter}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Q20Bxdsr}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Jupyter P, Bussonnier M, Forde J, Freeman J, Granger B, Head T, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{32. }
 \CSLRightInline{Himmelstein DS, Rubinetti V, Slochower DR, Hu D, Malladi VS, Greene CS, et al.

### 2023-07-04 content/submission/plos_revision1/answer_to_reviewers.md
Expand abbreviations and information in figure legends
Fixes suggestion #11 from Reviewer2
Improvements to paragraph

@@
 > The first sentence of the last paragraph of the subsection Micro-computed tomographic imaging is unclear: "While performing the work, a subset of the data was always present on the production system, for working with it (see Preparation for analysis below)".
-Please provide more precise information.
+> Please provide more precise information.
+
+We are sorry for the imprecise description of the data archival and copying process.
+The last paragraph of [this section](https://habi.github.io/EAWAG-manuscript/#micro-computed-tomographic-imaging) was expanded and hopefully improved.
 
@@
 
-All figure captions have been 'expanded', thanks for noticing this.
+Abbreviations in the legends have been written-out (except SI units).
+Additionally we added a bit of background information on the specimen to the legend of Fig. 1.
 

### 2023-07-04 content/submission/plos_revision1/answer_to_reviewers.md
We refuse to split M&M and Results section

@@
 
+The data shown in this manuscript is from unstained specimen.
+They have been stored in ethanol and scanned in wet foam, but *no* staining was applied.
+Since we here only focus on the morphology of the skull and teeth such a staining was not necessary to extract the needed data from the tomographic images.
+
 > Reviewer #2: I have carefully evaluated the manuscript titled "Microtomographic investigation of a large corpus of cichlids".
@@
 
-> Merging the Materials and Methods section with the Results is not a reasonable way to present the work. It would be better to separate them for clarity.
+> Merging the Materials and Methods section with the Results is not a reasonable way to present the work.
+> It would be better to separate them for clarity.
+
+The manuscript is focused on the method on how to acquire and assess tomographic datasets of a large corpus of cichlids.
+Especially for the image processing part, the method and results are highly intertwined as the Python code directly delivers the results.
+We believe that the approach we chose here here is the most appropriate way to present the whole data data acquisition and analysis pipeline and kindly ask the reviewer to accept our choice.
 

### 2023-07-04 content/submission/plos_revision1/answer_to_reviewers.md
Explain link correction

@@
 
+<!-- Not that *one* single dataset exceeds the RAM on a workstation, but *all* datasets together do -->
+
 > The Wikipedia citation in the second paragraph of the subsection "Extraction of oral and pharyngeal jaws..." is not clear.
-Please provide more specific information or replace the citation with a more appropriate reference.
+>Please provide more specific information or replace the citation with a more appropriate reference.
+
+The Wikipedia citation to a date-specific version of the Nrrd article on Wikipedia (https://w.wiki/5mBK) was not correctly expanded by our manuscript preparation system.
+We replaced the Wikipedia link with a more appropriate link to https://teem.sourceforge.net/nrrd/.
 

### 2023-07-04 manuscript.tex
Merge branch 'main' of github.com:habi/EAWAG-manuscript into main [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/6c4f87bee2147650a1535161b854bdb77b43e6a3.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/6c4f87bee2147650a1535161b854bdb77b43e6a3/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5456488875

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...a9633de5317eab4c8df584555033c6c11e4d89c5}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...6c4f87bee2147650a1535161b854bdb77b43e6a3}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/a9633de5317eab4c8df584555033c6c11e4d89c5/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/6c4f87bee2147650a1535161b854bdb77b43e6a3/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/a9633de5317eab4c8df584555033c6c11e4d89c5}{habi/EAWAG-manuscript@a9633de}
+from \href{https://github.com/habi/EAWAG-manuscript/tree/6c4f87bee2147650a1535161b854bdb77b43e6a3}{habi/EAWAG-manuscript@6c4f87b}
 on July 4, 2023.
@@
 
-While performing the work, a subset of the data was always present on the production system, for working with it (see \protect\hyperlink{preparation-for-analysis}{Preparation for analysis} below).
-A small bash script {[}\protect\hyperlink{ref-ZjgrPHTa}{14}{]} was used to generate redundant (archival) copies of the raw projection images and copy all the files to a shared network drive on the `Research Storage' infrastructure of the University of Bern, enabling collaboration on the data by all authorized persons at the same time.
+A small script {[}\protect\hyperlink{ref-ZjgrPHTa}{14}{]} was used to generate redundant (archival) copies of the raw projection images and copy all the files to a shared network drive on the `Research Storage' infrastructure of the University of Bern, enabling collaboration on the data by all authorized persons at the same time.
+This automated archival and copying process made it possible to delete the raw projection images on the production system shortly after acquisition, freeing resources and easing data handling.
+A subset of the data, namely the log files and reconstructed image stacks were kept on the production system for working with it (as described in \protect\hyperlink{preparation-for-analysis}{Preparation for analysis} below).
 
@@
 
-Processed regions of interest were exported as \texttt{Nrrd} {[}\protect\hyperlink{ref-uYuz0opI}{22}, =Nrrd\&oldid=1085264080{]} files.
+Processed regions of interest were exported as \texttt{Nrrd} {[}\protect\hyperlink{ref-11Rw8FsGY}{22}/{]} files.
 The three-dimensional visualizations of all regions of interest for each specimen were compiled into overview images (see Figure \ref{fig:104016} for an example from the compilation document).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-uYuz0opI}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-11Rw8FsGY}{}}%
 \CSLLeftMargin{22. }
-\CSLRightInline{Main Page. Wikipedia, the free encyclopedia. 2022. Available: \url{https://en.wikipedia.org/w/index.php?title=Main_Page\&oldid=1114291180}}
+\CSLRightInline{Teem: nrrd. {[}cited 4 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/}}
 

### 2023-07-05 content/submission/plos_revision1/answer_to_reviewers.md
Link to Nrrd format definition

@@
 
-The Wikipedia citation to a date-specific version of the Nrrd article on Wikipedia (https://w.wiki/5mBK) was not correctly expanded by our manuscript preparation system.
-We replaced the Wikipedia link with a more appropriate link to https://teem.sourceforge.net/nrrd/.
+The Wikipedia citation to a [date-specific version of the `Nrrd` article on Wikipedia](https://w.wiki/5mBK) was not correctly expanded by our manuscript preparation system.
+We replaced the Wikipedia link with a more appropriate link to [the `Nrrd` format definition](https://teem.sourceforge.net/nrrd/format.html).
 

### 2023-07-10 content/submission/plos_revision1/answer_to_reviewers.md
Answer growth 'ring' suggestion from R1

@@
 > Reviewer #1: Excellent paper.
-It was not clear if you could discern daily rings on the otoliths.
-You might want to discuss if you can use rings on otoliths to age the fish without removing them.
-Also, do you have to stain the fish to use these rings?
+> It was not clear if you could discern daily rings on the otoliths.
+> You might want to discuss if you can use rings on otoliths to age the fish without removing them.
+> Also, do you have to stain the fish to use these rings?
 
@@
 Since we here only focus on the morphology of the skull and teeth such a staining was not necessary to extract the needed data from the tomographic images.
+Growth rings would most probably be visible in the analyzed specimens, but only if some staining is applied, e.g. by storing the fish in Lugol solution.
+Since this was *not* the focus of the present study we did not do this here.
+
+To use the data on both growth rings and volume of the otoliths one would have to calibrate this first to be able to extract age estimates.
+I.e.
+one would have to make a simple growth experiment where a number of fish with known age are euthanized, tomographically imaged and then the volume of their extracted otoliths is correlated with their age.
+Such a calibration would match size and volume of both the (lab-raised) fish and the otoliths with the age of the fish.
+This data could then be used to estimate the age of fishes collected in the wild.
 

### 2023-07-10 content/submission/plos_revision1/answer_to_reviewers.md
Explain amount of specimen and scans to reviewer
And correct old value of 125 to current value of 129.

@@
 
+Thank you very much for the kind words.
+As we state in the [imaging section](https://habi.github.io/EAWAG-manuscript/#micro-computed-tomographic-imaging) we acquired 362 single tomographic scans of 129 different specimen.
+This means that each specimen was scanned several times, usually one lower-resolution scan of the full head and two single higer-resolution scans for the oral and pharyngeal jaws.
+
 > The introduction section needs improvement. It is too simplistic and lacks informative details about the state of the art and the justification for the work.
@@
 How was the filter thickness chosen?
+
+As stated above and in the text, we acquired 362 single tomographic scans of 129 different specimen.
 
@@
 
+As stated above and in the text, we acquired 362 single tomographic scans of 129 different specimen.
+It is correct though that "125" here is wrong, since we've acquired 4 scans more since this version of the manuscript.
+This has been corrected, and we thank the reviewer for noticing this.
+
 > The results of the subsection "Principal components analysis of skull landmarks" should be presented in a more accessible manner.

### 2023-07-10 manuscript.tex
Answer growth 'ring' suggestion from R1 [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/cf174315484443289e3b288555f8ec832a6cc151.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/cf174315484443289e3b288555f8ec832a6cc151/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5506777321

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...6c4f87bee2147650a1535161b854bdb77b43e6a3}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...cf174315484443289e3b288555f8ec832a6cc151}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/6c4f87bee2147650a1535161b854bdb77b43e6a3/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/cf174315484443289e3b288555f8ec832a6cc151/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/6c4f87bee2147650a1535161b854bdb77b43e6a3}{habi/EAWAG-manuscript@6c4f87b}
-on July 4, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/cf174315484443289e3b288555f8ec832a6cc151}{habi/EAWAG-manuscript@cf17431}
+on July 10, 2023.
 
@@
 
-Processed regions of interest were exported as \texttt{Nrrd} {[}\protect\hyperlink{ref-11Rw8FsGY}{22}/{]} files.
+Processed regions of interest were exported as \texttt{Nrrd} {[}\protect\hyperlink{ref-rn6XbmFW}{22}{]} files.
 The three-dimensional visualizations of all regions of interest for each specimen were compiled into overview images (see Figure \ref{fig:104016} for an example from the compilation document).
@@
 \CSLLeftMargin{12. }
-\CSLRightInline{OpenSCAD. {[}cited 4 Jul 2023{]}. Available: \url{https://openscad.org}}
+\CSLRightInline{OpenSCAD. {[}cited 10 Jul 2023{]}. Available: \url{https://openscad.org}}
 
@@
 \CSLLeftMargin{13. }
-\CSLRightInline{OpenSCAD models. TomoGraphics; 2022. Available: \url{https://github.com/TomoGraphics/Hol3Drs/blob/dedca665a77fa782c103eed63b866b2cceb30de9/EAWAG.Fish.scad}}
+\CSLRightInline{Available: \url{https://github.com/TomoGraphics/Hol3Drs/blob/master/EAWAG.Fish.scad}}
 
@@
 \CSLLeftMargin{14. }
-\CSLRightInline{Haberthür D.
-Jupyter notebooks for image processing and data analysis of EAWAG Cichlids project.
-2023.
-Available: \url{https://github.com/habi/EAWAG/blob/48197e8f6e7add0d3610ea1b2820f29c9a536bdf/rsync-fishes.sh}}
+\CSLRightInline{Available: \url{https://github.com/habi/EAWAG/blob/master/rsync-fishes.sh}}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-11Rw8FsGY}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
 \CSLLeftMargin{22. }
-\CSLRightInline{Teem: nrrd. {[}cited 4 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/}}
+\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 10 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
 

### 2023-07-10 content/submission/plos_revision1/answer_to_reviewers.md
Explain the notebooks a bit more.
Mostly in the 'answer to the reviewers' though, since the
'didactiveness' of the notebooks is not the main focus of the manuscript

@@
 > The authors should revise the entire "Data analysis" subsection to present a more didactic version that helps any reader use the notebooks.
-Currently, it seems that only Python users with some expertise can understand what needs to be done.
-Perhaps the authors could provide a guide or tutorial in the GitHub repository.
+> Currently, it seems that only Python users with some expertise can understand what needs to be done.
+> Perhaps the authors could provide a guide or tutorial in the GitHub repository.
+
+The notebooks are written in Python, and are presented as Jupyter notebooks.
+This makes them accessible 'piecewise', e.g. each part of the code is didactically separate and somehow compartmentalized.
+The code is written in Python, so some experience with it is beneficial to thoroughly understand it.
+The code and notebooks are also prepared in a way that *no* installation of *any* software except an up-to date web browser is necessary to test it.
+This testing can be done by clicking one button in the code repository (linking to https://mybinder.org/v2/gh/habi/eawag/HEAD) to launch a Jupyter environment in the cloud, which is also already explained in the last paragraph before the [Discussion section](https://habi.github.io/EAWAG-manuscript/#discussion).
+We understand the concerns of the reviewer though, and added explanation text and comments to the notebooks guiding (first time) users of the notebooks.
+All these updates happen in [the code repository](https://github.com/habi/EAWAG) and have *not* been specifically mentioned in the manuscript text.
+Two of the notebooks ([DataWrangling](https://nbviewer.org/github/habi/EAWAG/blob/main/DataWrangling.ipynb) and [DataSize](https://nbviewer.org/github/habi/EAWAG/blob/main/DataSize.ipynb)) were used to help us generate 'checking' and 'collaboration' files (DataWrangling) or used to help us generate text for the manuscript, i.e.
+to extract exact details on sample numbers, total amount of projections and reconstructions and their exact size on disk (DataSize).
+As these notebooks are not explicitly mentioned in the manuscript they are not extensively commented (only commented).
+The two notebooks mentioned in the text ([DisplayFishes](https://nbviewer.org/github/habi/EAWAG/blob/main/DisplayFishes.ipynb)) and ([ExtractOtoliths](https://nbviewer.org/github/habi/EAWAG/blob/main/ExtractOtoliths.ipynb)) have been.
 
 > How was the sanity check performed (as mentioned in the second paragraph of the subsection "Preparation for Analysis")?
+
+The mentioned 'sanity check' was performed manually, e.g. by looking at all the values (mostly the reconstruction parameters), to exclude any operator error.
+If errors were spotted at this stage, the reconstructions were deleted and re-done with the correct parameters.
+Sometimes errors or problems were only spotted at a later stage, when either the pharyngeal or oral jaws were extracted, or when we noticed that some part of the the whole skull were out of the field of view of the tomographic scan prior to performing the PCA analysis mentioned later in the manuscript.
+This means that specifying this as 'sanity check' is more of a glorified wording of telling the readers that we manually looked at the values of each performed tomographic scan to exlude and catch operator errors.
+We reworded the sentence to hopefully make this more clear.
 

### 2023-07-10 manuscript.tex
Explain the notebooks a bit more. [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/0b19da53fc1e2392fe85070eadd10f8795fff509.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/0b19da53fc1e2392fe85070eadd10f8795fff509/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5508263410

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...cf174315484443289e3b288555f8ec832a6cc151}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...0b19da53fc1e2392fe85070eadd10f8795fff509}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/cf174315484443289e3b288555f8ec832a6cc151/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/0b19da53fc1e2392fe85070eadd10f8795fff509/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/cf174315484443289e3b288555f8ec832a6cc151}{habi/EAWAG-manuscript@cf17431}
+from \href{https://github.com/habi/EAWAG-manuscript/tree/0b19da53fc1e2392fe85070eadd10f8795fff509}{habi/EAWAG-manuscript@0b19da5}
 on July 10, 2023.
@@
 
-We wrote a set of \emph{Jupyter} {[}\protect\hyperlink{ref-pQ6Wbz73}{15}{]} notebooks with \emph{Python} code to work with the images and wrangle the acquired data.
+We wrote a set of \emph{Jupyter} {[}\protect\hyperlink{ref-pQ6Wbz73}{15}{]} notebooks with \emph{Python} code to work with the acquired images to extract the desired data.
 The notebooks were written at the start of the project, to be able to process new scans as soon as they were reconstructed.
@@
 
-All analysis notebooks for this work are available online {[}\protect\hyperlink{ref-1HteOscVd}{16}{]}.
+All notebooks written for this work are available online {[}\protect\hyperlink{ref-1HteOscVd}{16}{]} and are extensively commented.
+They are split into different task performed for this study and mentioned in their respective sections below.
 
@@
 
-The \href{https://github.com/habi/EAWAG/blob/master/DisplayFishes.ipynb}{main \emph{Jupyter} notebook} for this manuscript dealt with reading all log and image files and preparing images for quality checking and further analysis.
+The \href{https://github.com/habi/EAWAG/blob/master/DisplayFishes.ipynb}{main \emph{Jupyter} notebook} for this manuscript dealt with reading all log and image files and preparing overview images of each scan for quality checking and further analysis.
 
 At first, \emph{all} log files of \emph{all} the data present in the processed folder were read into a \emph{pandas} {[}\protect\hyperlink{ref-19qQOHlFN}{17},\protect\hyperlink{ref-U5AcoDOX}{18}{]} dataframe.
-This already enabled us to extract the specimen name and scan, since we performed multiple scans for each specimen, i.e.~a low resolution scan with large field of view for the whole head and one or two scans in high resolution focusing on the region of the oral and pharyngeal jaws.
-From the log files we extracted the relevant values for double-checking the necessary parameters of each scan.
-All relevant values for each scan were also saved into the dataframe and saved out to the aforementioned table in the \protect\hyperlink{supplementary-materials}{Supplementary Materials} at the end of each run of the notebook.
+This already enabled us to extract the specimen name and scan.
+Since we performed multiple scans for each specimen, i.e.~a low resolution scan with large field of view for the whole head and one or two scans in high resolution focusing on the region of the oral and pharyngeal jaws it was necessary to be able to efficiently find the scan to be looked at in detail.
+From the log files we extracted the scanning and reconstruction parameters of each performed scan for double-checking them and excluding (or necessarily correcting) any operator-error.
+All relevant values for each scan were also saved into the aforementioned ataframe.
+This allows for an easy collation of all the relevant values into a table (as shown in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}) at the end of each run of the notebook.
 
@@
 At the end of the notebook we performed a final sanity check on the MIP images.
-In this check we examined the mapping of the gray values of the raw projection images to gray values in the reconstructions, i.e.~checked that no overexposed pixels are present in the MIP images.
-This is an efficient way for double-checking the gray value mapping, since the MIP images have already been generated in prior steps of the notebook and contain the highest gray values present in all the reconstructed images of each scan.
+In this check we examined the mapping of the gray values of the raw projection images to gray values in the reconstructions, i.e.~checked that no overexposed pixels were present.
+This is an efficient way for double-checking the gray value mapping, since the MIP images have already been generated in prior steps of the notebook and contain the highest gray values present in all the reconstructed images for each scan.
 
@@
 The three-dimensional visualizations of all regions of interest for each specimen were compiled into overview images (see Figure \ref{fig:104016} for an example from the compilation document).
-In total we compiled overview of 125 specimens with full head morphology, oral jaw and lower pharyngeal jaw profiles.
+In total, we compiled such overview images for 129 specimens with full head morphology, oral jaw and lower pharyngeal jaw profiles.
 

### 2023-07-11 content/submission/plos_revision1/answer_to_reviewers.md
Update numbers, since we've done some more scans

@@
 Thank you very much for the kind words.
-As we state in the [imaging section](https://habi.github.io/EAWAG-manuscript/#micro-computed-tomographic-imaging) we acquired 362 single tomographic scans of 129 different specimen.
-This means that each specimen was scanned several times, usually one lower-resolution scan of the full head and two single higer-resolution scans for the oral and pharyngeal jaws.
+As we state in the [imaging section](https://habi.github.io/EAWAG-manuscript/#micro-computed-tomographic-imaging) we acquired 372 single tomographic scans of 133 different specimen (updated since submission of the manuscript, as a rest of fish relevant for the study was added).
+This means that each specimen was scanned several times, usually one lower-resolution scan of the full head and two single higher-resolution scans for the oral and pharyngeal jaws.
 
@@
 
-As stated above and in the text, we acquired 362 single tomographic scans of 129 different specimen.
+As stated above and in the text, we acquired 372 single tomographic scans of 133 different specimen.
 
@@
 
-As stated above and in the text, we acquired 362 single tomographic scans of 129 different specimen.
-It is correct though that "125" here is wrong, since we've acquired 4 scans more since this version of the manuscript.
+As stated above and in the text, we actually acquired 372 single tomographic scans of 133 different specimen.
+It is correct though that "125" here is wrong, since we've acquired more scans after submission of the manuscript.
 This has been corrected, and we thank the reviewer for noticing this.

### 2023-07-11 manuscript.tex
Spell check [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/c6b7ff7c02d5425b675ce348cd38ac7a88cbfeb3.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/c6b7ff7c02d5425b675ce348cd38ac7a88cbfeb3/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5519841905

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...0b19da53fc1e2392fe85070eadd10f8795fff509}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...c6b7ff7c02d5425b675ce348cd38ac7a88cbfeb3}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/0b19da53fc1e2392fe85070eadd10f8795fff509/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/c6b7ff7c02d5425b675ce348cd38ac7a88cbfeb3/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/0b19da53fc1e2392fe85070eadd10f8795fff509}{habi/EAWAG-manuscript@0b19da5}
-on July 10, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/c6b7ff7c02d5425b675ce348cd38ac7a88cbfeb3}{habi/EAWAG-manuscript@c6b7ff7}
+on July 11, 2023.
 
@@
 
-A large collection of cichlids from Lake Victoria in Africa spanning a length range of 6 to 18 cm was nondestructively imaged using micro-computed tomography.
+A large collection of cichlids (N=133) from Lake Victoria in Africa spanning a length range of 6 to 18 cm was nondestructively imaged using micro-computed tomography.
 We describe our method to efficiently obtain three-dimensional tomographic datasets of the oral and pharyngeal jaws and the whole skull of these fishes for accurately describing their morphology.
-The tomographic data we acquired (9.5 TB of projection images) yielded 1.4 TB of three-dimensional image stacks used for extracting the relevant features of interest.
+The tomographic data we acquired (9.8 TB of projection images) yielded 1.5 TB of three-dimensional image stacks used for extracting the relevant features of interest.
 Herein we present our method and an outlook on analyzing the acquired data; a morphological description of the oral and pharyngeal jaws of the fishes, a three-dimensional geometric morphometrics analysis of landmark features on the fish skulls, and a robust method to automatically extract the otoliths of the fishes from the tomographic data.
@@
 The collection of cichlid fish available is extremely valuable, hence a nondestructive imaging method is paramount for studying these samples.
-Since micro--computed tomography can be regarded as nondestructive method for biological samples, it is the ideal imaging method for investigating the oral and pharyngeal jaws as well as the skull features of the fish presented in this study {[}\protect\hyperlink{ref-19h9vxsYG}{6}{]}.
+Since micro--computed tomography can be regarded as nondestructive method for biological samples, it is the ideal imaging method for investigating the oral and pharyngeal jaws as well as the skull features of the fish presented in this study {[}\protect\hyperlink{ref-19h9vxsYG}{6}{]} (N=133).
 
@@
 
-In total, we acquired 362 tomographic scans of 129 different specimens.
-All the scanning parameters are collected in a table in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}; a generalized rundown is given below.
+In total, we acquired 372 tomographic scans of 133 different specimens.
+All the scanning parameters are collected in a table in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}; an overview of the parameters is given below.
 
@@
 The X-ray spectrum was filtered either by an aluminum filter of varying thickness (either 0.25, 0.5 or 1 mm for increasing specimen size) before digitization to projection images or recorded in an unfiltered way (for smaller specimen).
-In total we recorded 9.5 TB of projection images (\texttt{TIFF} and \texttt{*.iif} files, where the \texttt{*.iif} files are for the so-called alignment scans).
+Projection images spanning either 180° or 360° of sample rotation were acquired in angular steps of 0.1°, 0.15° or 0.2°, also depending on size of the fish.
+In total we recorded 9.8 TB of projection images (\texttt{TIFF} and \texttt{*.iif} files, where the \texttt{*.iif} files are for the so-called alignment scans).
 
@@
 We reconstructed the projection images with NRecon (Version 1.7.4.6, Bruker microCT, Kontich, Belgium) with varying ring artifact and beam hardening correction values, depending on each fish (again, all relevant values are listed in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}).
-In total, this resulted in 1.4 TB of reconstruction images (nearly one million \texttt{*rec*.png} files).
-Each of the 362 scans we performed has on average about 2700 reconstruction images.
+In total, this resulted in 1.5 TB of reconstruction images (a bit more than one million \texttt{*rec*.png} files).
+On average, each of the scans we performed is made up of about 2700 reconstruction images.
 
@@
 
-We wrote a set of \emph{Jupyter} {[}\protect\hyperlink{ref-pQ6Wbz73}{15}{]} notebooks with \emph{Python} code to work with the acquired images to extract the desired data.
+We wrote a set of \emph{Jupyter} {[}\protect\hyperlink{ref-pQ6Wbz73}{15}{]} notebooks with \emph{Python} code to work with the acquired images and to extract the desired data.
 The notebooks were written at the start of the project, to be able to process new scans as soon as they were reconstructed.
@@
 
-At first, \emph{all} log files of \emph{all} the data present in the processed folder were read into a \emph{pandas} {[}\protect\hyperlink{ref-19qQOHlFN}{17},\protect\hyperlink{ref-U5AcoDOX}{18}{]} dataframe.
+At first, \emph{all} log files of \emph{all} the scan present in the processed folder were read into a \emph{pandas} {[}\protect\hyperlink{ref-19qQOHlFN}{17},\protect\hyperlink{ref-U5AcoDOX}{18}{]} dataframe.
 This already enabled us to extract the specimen name and scan.
@@
 
-After performing `sanity checks' of the data and reconstruction parameters, we used \emph{Dask} {[}\protect\hyperlink{ref-hj1CnyWB}{19}{]} to efficiently access the tomographic data on disk (in the end amounting to a total of nearly a million single images).
+After displaying several parameters of both data acquisition and reconstruction for ruling out any operator error we used \emph{Dask} {[}\protect\hyperlink{ref-hj1CnyWB}{19}{]} to efficiently access the tomographic data on disk (in the end amounting to a total of nearly a million single images).
 On average, each of the tomographic datasets contains around 2700 slices, so the total size of the acquired data exceeds the RAM size available on an average high-end workstation.
@@
 The three-dimensional visualizations of all regions of interest for each specimen were compiled into overview images (see Figure \ref{fig:104016} for an example from the compilation document).
-In total, we compiled such overview images for 129 specimens with full head morphology, oral jaw and lower pharyngeal jaw profiles.
+In total, we compiled such overview images for 133 specimens with full head morphology, oral jaw and lower pharyngeal jaw profiles.
 
@@
 Due to their composition, they are easily distinguished in the X-ray images we acquired.
-We devised an image processing method to automatically and robustly detect the location of the otoliths in the heads of the cichlids we scanned and to extract them from the original data.
+We devised an image processing method to automatically and robustly detect the location of the otoliths in the tomographic scans of the skulls of the cichlids.
+Based on this detected location we were then able to efficiently extract a cropped region of interest from the original data which includes only the region of the otoliths.
 The whole method is implemented in its own \href{https://github.com/habi/EAWAG/blob/master/ExtractOtoliths.ipynb}{\emph{Jupyter} notebook} (part of the aforementioned analysis repository {[}\protect\hyperlink{ref-1HteOscVd}{16}{]}).
@@
 
-We acquired high resolution tomographic datasets of a large collection of cichlids.
-The acquired datasets were imaged over a wide-spanning range of voxel size (3.5--50 μm) permitting both the analysis of finest details we wanted to resolve (i.e.~the structure of the teeth) and having datasets spanning the whole region of interest of the fish (i.e.~the whole head for principle components analysis).
+We acquired high resolution tomographic datasets of a large collection of cichlids (N=133), several tomographic scans were performed for each specimen.
+The 372 acquired datasets were imaged over a wide-spanning range of voxel size (3.5--50 μm) permitting both the analysis of finest details we wanted to resolve (i.e.~containing only the oral and pharyngeal jaws) and having datasets (N=104) containing the whole head for principle components analysis and extraction of the otoliths.
 
@@
 \CSLLeftMargin{12. }
-\CSLRightInline{OpenSCAD. {[}cited 10 Jul 2023{]}. Available: \url{https://openscad.org}}
+\CSLRightInline{OpenSCAD. {[}cited 11 Jul 2023{]}. Available: \url{https://openscad.org}}
 
@@
 \CSLLeftMargin{22. }
-\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 10 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
+\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 11 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
 

### 2023-07-11 manuscript.tex
Merge branch 'main' of github.com:habi/EAWAG-manuscript into main [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/05e0c4de935ffd552c20ae7ff34db6d16ce5ca6d.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/05e0c4de935ffd552c20ae7ff34db6d16ce5ca6d/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5520399868

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...c6b7ff7c02d5425b675ce348cd38ac7a88cbfeb3}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...05e0c4de935ffd552c20ae7ff34db6d16ce5ca6d}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/c6b7ff7c02d5425b675ce348cd38ac7a88cbfeb3/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/05e0c4de935ffd552c20ae7ff34db6d16ce5ca6d/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/c6b7ff7c02d5425b675ce348cd38ac7a88cbfeb3}{habi/EAWAG-manuscript@c6b7ff7}
+from \href{https://github.com/habi/EAWAG-manuscript/tree/05e0c4de935ffd552c20ae7ff34db6d16ce5ca6d}{habi/EAWAG-manuscript@05e0c4d}
 on July 11, 2023.

### 2023-07-13 content/submission/plos_revision1/answer_to_reviewers.md
Answer comment about data size

@@
 > In the same paragraph, the authors mentioned that each tomographic dataset contains around 2700 slices, exceeding the available RAM size on an average high-end workstation.
-Could you clarify if this limitation affected the analysis and its implications?
+> Could you clarify if this limitation affected the analysis and its implications?
 
-<!-- Not that *one* single dataset exceeds the RAM on a workstation, but *all* datasets together do -->
+We wrote that *the total size of the acquired data exceeds the RAM* of any workstation (e.g. around 1.5 TB).
+*One* or more single datasets would fit into RAM very well, It is not possible to load *all* data concurrently for analysis.
+The use of *Dask* and more specifically [*dask-image*](@https://image.dask.org/) for loading only the currently used data for each specimen from the HD (or remote storage) into RAM on demand made working with the *all* the data feasible.
+We have updated the sentence to explain this.
 

### 2023-07-13 content/submission/plos_revision1/answer_to_reviewers.md
Increase 'didactiveness'

@@
 As these notebooks are not explicitly mentioned in the manuscript they are not extensively commented (only commented).
-The two notebooks mentioned in the text ([DisplayFishes](https://nbviewer.org/github/habi/EAWAG/blob/main/DisplayFishes.ipynb)) and ([ExtractOtoliths](https://nbviewer.org/github/habi/EAWAG/blob/main/ExtractOtoliths.ipynb)) have been.
+The two notebooks mentioned in the text ([DisplayFishes](https://nbviewer.org/github/habi/EAWAG/blob/main/DisplayFishes.ipynb)) and ([ExtractOtoliths](https://nbviewer.org/github/habi/EAWAG/blob/main/ExtractOtoliths.ipynb)) have been updated with more comments and explanatory text between the logical steps.
+These additions are [visualized in the respective GitHub repository](https://github.com/habi/EAWAG/compare/v1.1...HEAD), but not specifically mentioned in the text.
+We slightly expanded the description of the notebooks at the start of the [Data analysis section](https://habi.github.io/EAWAG-manuscript/#data-analysis) though.
 

### 2023-07-13 content/submission/plos_revision1/answer_to_reviewers.md
Increase precision in our answers

@@
 The data shown in this manuscript is from unstained specimen.
-They have been stored in ethanol and scanned in wet foam, but *no* staining was applied.
+They have been stored in ethanol and imaged in wet foam to avoid any drying during imaging, but *no* staining was applied.
 Since we here only focus on the morphology of the skull and teeth such a staining was not necessary to extract the needed data from the tomographic images.
@@
 Thank you very much for the kind words.
-As we state in the [imaging section](https://habi.github.io/EAWAG-manuscript/#micro-computed-tomographic-imaging) we acquired 372 single tomographic scans of 133 different specimen (updated since submission of the manuscript, as a rest of fish relevant for the study was added).
+As we (now) state in the [imaging section](https://habi.github.io/EAWAG-manuscript/#micro-computed-tomographic-imaging) we acquired 372 single tomographic scans of 133 different specimen (updated since submission of the manuscript, as a rest of fish relevant for the study was added).
 This means that each specimen was scanned several times, usually one lower-resolution scan of the full head and two single higher-resolution scans for the oral and pharyngeal jaws.
@@
 We are sorry for the imprecise description of the data archival and copying process.
-The last paragraph of [this section](https://habi.github.io/EAWAG-manuscript/#micro-computed-tomographic-imaging) was expanded and hopefully improved.
+The last paragraph of [this section](https://habi.github.io/EAWAG-manuscript/#micro-computed-tomographic-imaging) was expanded and improved.
 
@@
 The Wikipedia citation to a [date-specific version of the `Nrrd` article on Wikipedia](https://w.wiki/5mBK) was not correctly expanded by our manuscript preparation system.
-We replaced the Wikipedia link with a more appropriate link to [the `Nrrd` format definition](https://teem.sourceforge.net/nrrd/format.html).
+We replaced the Wikipedia link with a more appropriate link to [the `Nrrd` format definition](https://teem.sourceforge.net/nrrd/format.html) and thank the reviewer for noticing this issue.
 

### 2023-07-13 content/submission/plos_revision1/answer_to_reviewers.md
Answer some more points of the reviewer

@@
 
-> The introduction section needs improvement. It is too simplistic and lacks informative details about the state of the art and the justification for the work.
+> The introduction section needs improvement.
+> It is too simplistic and lacks informative details about the state of the art and the justification for the work.
+
+We've deliberately kept the introduction rather terse.
+The justification of the work lies in the non-desctructive imaging of unstained samples.
+We have expanded the introduction a bit and added references to manuscripts detailing microtomographic imaging in the life sciences.
+As this manuscript is not a review, we kindly refuse to add more information on the background of microtomogrpahic imaging.
 
@@
 
-> The procedure for detecting and extracting otoliths in the subsection "Automatic extraction of otoliths" is not clear.
-Please provide clearer instructions or guidelines for readers using the notebook.
+As mentioned above, the Jupyter notebook used to detect the otolith position and to extract the otoliths from the scans covering the whole skull are extensively commented.
+We have added more explanatory comments and text to the notebook on GitHub, increading their didactiveness.
 
@@
 > By addressing these suggestions, the manuscript will become more comprehensive, accessible, and representative of the valuable contribution made by the authors.
+
+We thank the reviewer for the kind words and the time spent on improving our work with relevant questions and comments.
+The manuscript has considerably improved by the updates we have performed.

### 2023-07-13 content/submission/plos_revision1/answer_to_reviewers.md
Hint on Kassandras upcoming publication

@@
 > The results of the subsection "Principal components analysis of skull landmarks" should be presented in a more accessible manner.
-Consider providing a tutorial or guide for readers to better understand and apply the analysis.
-As it currently stands, this subsection may be considered irrelevant for the paper.
+> Consider providing a tutorial or guide for readers to better understand and apply the analysis.
+> As it currently stands, this subsection may be considered irrelevant for the paper.
+
+This subsection is currently being 'expanded' into a self-contained publication.
+We deliberately only very briefly mentioned the method here, as the upcoming publication is to be submitted soon.
+
+> The procedure for detecting and extracting otoliths in the subsection "Automatic extraction of otoliths" is not clear.
+> Please provide clearer instructions or guidelines for readers using the notebook.
 

### 2023-07-13 content/submission/plos_revision1/answer_to_reviewers.md
Answer point of reviewer about voxel size range
The text still has to be adapted.

@@
 > In the discussion section, the authors mentioned acquiring high-resolution tomographic datasets of a large collection of cichlids.
-However, the statement that "the acquired datasets were imaged over a wide-spanning range of voxel size (3.5–50 μm)" is incorrect.
-The voxel size is specimen-specific, depending on the size of the fish and the chosen parameters.
-Please clarify this point to accurately represent the imaging process.
-The finest resolution was obtained only for small fishes, so specific structures of a fish will have the same image resolution throughout the entire specimen.
+> However, the statement that "the acquired datasets were imaged over a wide-spanning range of voxel size (3.5–50 μm)" is incorrect.
+> The voxel size is specimen-specific, depending on the size of the fish and the chosen parameters.
+> Please clarify this point to accurately represent the imaging process.
+> The finest resolution was obtained only for small fishes, so specific structures of a fish will have the same image resolution throughout the entire specimen.
+
+The statement over the 'wide-spanning range of voxel sizes' is *not* incorrect, at most---if applied to *one* speciment---imprecise.
+The range of voxel sizes is true for the whole study, while---as also correctly noted by the reviewer---the voxel size is specimen-specific.
+We clarified this paragraph by adding a more precise explanation.
 

### 2023-07-13 content/submission/plos_revision1/answer_to_reviewers.md
Whitespace changes only

@@
 > Overall, the study seems to have spanned a considerable time frame.
-However, the manuscript's content and structure need improvement to reach a wider audience and effectively communicate the significance of the work.
-The authors have provided a valuable set of open-source Python notebooks, which is commendable and will be highly useful for the scientific community.
-However, the workflow needs to be better explained to enable readers to follow the procedures accurately.
+> However, the manuscript's content and structure need improvement to reach a wider audience and effectively communicate the significance of the work.
+> The authors have provided a valuable set of open-source Python notebooks, which is commendable and will be highly useful for the scientific community.
+> However, the workflow needs to be better explained to enable readers to follow the procedures accurately.
 

### 2023-07-13 manuscript.tex
Whitespace changes only [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/a15f6a93f7f5b262f005c909a8fdcbdf8220da53.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/a15f6a93f7f5b262f005c909a8fdcbdf8220da53/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5542383142

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...05e0c4de935ffd552c20ae7ff34db6d16ce5ca6d}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...a15f6a93f7f5b262f005c909a8fdcbdf8220da53}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/05e0c4de935ffd552c20ae7ff34db6d16ce5ca6d/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/a15f6a93f7f5b262f005c909a8fdcbdf8220da53/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/05e0c4de935ffd552c20ae7ff34db6d16ce5ca6d}{habi/EAWAG-manuscript@05e0c4d}
-on July 11, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/a15f6a93f7f5b262f005c909a8fdcbdf8220da53}{habi/EAWAG-manuscript@a15f6a9}
+on July 13, 2023.
 
@@
 
-\hypertarget{history}{%
-\subsubsection{History}\label{history}}
+\hypertarget{history-and-rationale}{%
+\subsubsection{History and rationale}\label{history-and-rationale}}
 
@@
 
-X-ray microtomography is a valuable tool to gain insights into the inner structure of highly diverse samples, namely for specimens related to research done in the biomedical sciences.
+X-ray microtomography is a valuable tool to gain insights into the inner structure of highly diverse samples, namely for specimens related to the biomedical sciences {[}\protect\hyperlink{ref-IKVBgaCE}{7}{]}.
 Microtomographic imaging has been employed as a method of choice to nondestructively assess the morphology of different fish species, large and small {[}\protect\hyperlink{ref-19h9vxsYG}{6}{]}.
-For a small overview of analyses which are possible with X-ray microtomographic imaging in relation to fish biology and morphology, see prior work of the authors of this manuscript {[}\protect\hyperlink{ref-19h9vxsYG}{6}--\protect\hyperlink{ref-BDrCSu8p}{8}{]} as well as other studies {[}\protect\hyperlink{ref-3rxGCEvJ}{9}{]}.
+For a small overview of analyses which are possible with X-ray microtomographic imaging in relation to fish biology and morphology, see prior work of the authors of this manuscript {[}\protect\hyperlink{ref-19h9vxsYG}{6},\protect\hyperlink{ref-8Pmc2mI8}{8},\protect\hyperlink{ref-BDrCSu8p}{9}{]} as well as other studies {[}\protect\hyperlink{ref-3rxGCEvJ}{10}{]}.
 
-Depending on the structures of interest, biomedical samples are often only tomographically scanned after being stained with a contrast agent, most often employing contrast agents containing heavy metals.
-Since the structures of interest for the two studies we touch upon in this manuscript (cichlid teeth and skulls) display large enough contrast to the surrounding tissue we did not stain our samples prior to the tomographic imaging presented here.
+Depending on the structures of interest, biomedical samples are often only tomographically scanned after being stained with a contrast agent {[}\protect\hyperlink{ref-pN1S9E5p}{11}{]}, most often employing contrast agents containing heavy metals {[}\protect\hyperlink{ref-kkBa4qNV}{12}{]}.
+Due to their inherent contrast difference to the surrounding tissue, the structures of interest we touch upon in this manuscript (teeth and bones, i.e.~jaws and skull) are well visualized in native samples.
+Enhancing contrast differences by staining prior to tomographic imaging was thus not necessary to for the samples presented herein.
 
@@
 We used a custom-made sample-holder to scan each of the fish in our machines.
-It was 3D-printed on a Form 2 desktop stereolithography printer (Formlabs, Somerville, Massachusetts, USA), the file for printing the holder is available online {[}\protect\hyperlink{ref-VCZPOv2f}{10}{]} as part of a library of sample holders for tomographic scanning of biomedical samples {[}\protect\hyperlink{ref-115PPSuQp}{11}{]}.
-The original \emph{OpenSCAD} {[}\protect\hyperlink{ref-wsjdcTeC}{12}{]} file {[}\protect\hyperlink{ref-f7OzrzUv}{13}{]} is parametrized to effortlessly generate a file for 3D-printing sample holders to accommodate the varying width, height and length classes of the fish.
+It was 3D-printed on a Form 2 desktop stereolithography printer (Formlabs, Somerville, Massachusetts, USA), the file for printing the holder is available online {[}\protect\hyperlink{ref-VCZPOv2f}{13}{]} as part of a library of sample holders for tomographic scanning of biomedical samples {[}\protect\hyperlink{ref-115PPSuQp}{14}{]}.
+The original \emph{OpenSCAD} {[}\protect\hyperlink{ref-wsjdcTeC}{15}{]} file {[}\protect\hyperlink{ref-f7OzrzUv}{16}{]} is parametrized to effortlessly generate a file for 3D-printing sample holders to accommodate the varying width, height and length classes of the fish.
 
@@
 
-A small script {[}\protect\hyperlink{ref-ZjgrPHTa}{14}{]} was used to generate redundant (archival) copies of the raw projection images and copy all the files to a shared network drive on the `Research Storage' infrastructure of the University of Bern, enabling collaboration on the data by all authorized persons at the same time.
+A small script {[}\protect\hyperlink{ref-ZjgrPHTa}{17}{]} was used to generate redundant (archival) copies of the raw projection images and copy all the files to a shared network drive on the `Research Storage' infrastructure of the University of Bern, enabling collaboration on the data by all authorized persons at the same time.
 This automated archival and copying process made it possible to delete the raw projection images on the production system shortly after acquisition, freeing resources and easing data handling.
@@
 
-We wrote a set of \emph{Jupyter} {[}\protect\hyperlink{ref-pQ6Wbz73}{15}{]} notebooks with \emph{Python} code to work with the acquired images and to extract the desired data.
+We wrote a set of \emph{Jupyter} {[}\protect\hyperlink{ref-pQ6Wbz73}{18}{]} notebooks with \emph{Python} code to work with the acquired images and to extract the desired data.
 The notebooks were written at the start of the project, to be able to process new scans as soon as they were reconstructed.
@@
 
-All notebooks written for this work are available online {[}\protect\hyperlink{ref-1HteOscVd}{16}{]} and are extensively commented.
-They are split into different task performed for this study and mentioned in their respective sections below.
+All notebooks written for this work are available online {[}\protect\hyperlink{ref-1HteOscVd}{19}{]} and are extensively commented.
+The modularized and interactive format chosen for these notebooks makes them easy to adapt for any other study dealing with tomographic data.
+The first author of this study is happy to help other scientists to adapt the notebooks to their use-case.
+They notebooks are split into different task performed for this study and are specifically mentioned in the respective sections below.
 
@@
 
-At first, \emph{all} log files of \emph{all} the scan present in the processed folder were read into a \emph{pandas} {[}\protect\hyperlink{ref-19qQOHlFN}{17},\protect\hyperlink{ref-U5AcoDOX}{18}{]} dataframe.
+At first, \emph{all} log files of \emph{all} the scan present in the processed folder were read into a \emph{pandas} {[}\protect\hyperlink{ref-19qQOHlFN}{20},\protect\hyperlink{ref-U5AcoDOX}{21}{]} dataframe.
 This already enabled us to extract the specimen name and scan.
@@
 
-After displaying several parameters of both data acquisition and reconstruction for ruling out any operator error we used \emph{Dask} {[}\protect\hyperlink{ref-hj1CnyWB}{19}{]} to efficiently access the tomographic data on disk (in the end amounting to a total of nearly a million single images).
-On average, each of the tomographic datasets contains around 2700 slices, so the total size of the acquired data exceeds the RAM size available on an average high-end workstation.
+After displaying several parameters of both data acquisition and reconstruction for ruling out any operator error we used \emph{Dask} {[}\protect\hyperlink{ref-hj1CnyWB}{22}{]} to efficiently access the tomographic data on disk (in the end amounting to a total of nearly a million single images).
+On average, each of the tomographic datasets contains around 2700 slices, so the total size of the acquired data (1.5 TB) exceeds the RAM size available on an average high-end workstation.
+The use of \emph{Dask} (and more specifically \emph{dask-image} {[}\protect\hyperlink{ref-wIfTDBqd}{23}/{]}) facilitated on-demand loading of the needed data directly from disk for each of the specimen to be analyzed in each step of the notebooks.
 
@@
 
-To extract the oral jaw (OJ) and pharyngeal jaw (PJ) of the fish, we used \href{https://www.slicer.org}{\emph{3D Slicer}} (Version 4.11.20210226) {[}\protect\hyperlink{ref-OsCpHsJH}{20}{]} extended with the \emph{SlicerMorph} tools {[}\protect\hyperlink{ref-MwdN6kPV}{21}{]} which aim to help biologists work with 3D specimen data.
+To extract the oral jaw (OJ) and pharyngeal jaw (PJ) of the fish, we used \href{https://www.slicer.org}{\emph{3D Slicer}} (Version 4.11.20210226) {[}\protect\hyperlink{ref-OsCpHsJH}{24}{]} extended with the \emph{SlicerMorph} tools {[}\protect\hyperlink{ref-MwdN6kPV}{25}{]} which aim to help biologists work with 3D specimen data.
 The reconstructed image stacks were loaded into \href{https://www.slicer.org/wiki/Documentation/Labs/ImageStacks}{\emph{ImageStacks}}, depending on their size we reduced the image resolution (i.e.~downscaled the images) for this first step.
@@
 
-Processed regions of interest were exported as \texttt{Nrrd} {[}\protect\hyperlink{ref-rn6XbmFW}{22}{]} files.
+Processed regions of interest were exported as \texttt{Nrrd} {[}\protect\hyperlink{ref-rn6XbmFW}{26}{]} files.
 The three-dimensional visualizations of all regions of interest for each specimen were compiled into overview images (see Figure \ref{fig:104016} for an example from the compilation document).
@@
 \caption{Overview of data from sample 104016,~\emph{Enterochromis I cinctus}, from `Station E' in the transect of Mwanza Bay at the southern edge of Lake Victoria.
-A map showing the detailed location of `Station E' is shown in Fig. 1 of {[}\protect\hyperlink{ref-JtHcU2O2}{23}{]}.
+A map showing the detailed location of `Station E' is shown in Fig. 1 of {[}\protect\hyperlink{ref-JtHcU2O2}{27}{]}.
 Panel A: Three-dimensional visualization of the head scan.
@@
 Current studies are using 3D geometric morphometrics to compare the morphological shape of these scanned cichlids using statistical analysis.
-We used a homologous landmark scheme across one-half of the skull for higher density of shape information {[}\protect\hyperlink{ref-BDrCSu8p}{8},\protect\hyperlink{ref-15FafMZm5}{24}{]}, and landmarks were placed on each specimen using \emph{3D Slicer}.
-To examine differences in shape across the species sampled, we performed a Generalized Procrustes Superimposition on the landmark data to remove the effects of location, size, and rotation from the analysis using the \emph{geomorph} package in \emph{R} (Version 4.2.1) with \emph{RStudio} (Version 2022.07.2+576) {[}\protect\hyperlink{ref-VPUOQA2P}{25}--\protect\hyperlink{ref-EwNL0C0Y}{27},\protect\hyperlink{ref-whEyWyQh}{28},\protect\hyperlink{ref-QfVloFVu}{29}{]}.
+We used a homologous landmark scheme across one-half of the skull for higher density of shape information {[}\protect\hyperlink{ref-BDrCSu8p}{9},\protect\hyperlink{ref-15FafMZm5}{28}{]}, and landmarks were placed on each specimen using \emph{3D Slicer}.
+To examine differences in shape across the species sampled, we performed a Generalized Procrustes Superimposition on the landmark data to remove the effects of location, size, and rotation from the analysis using the \emph{geomorph} package in \emph{R} (Version 4.2.1) with \emph{RStudio} (Version 2022.07.2+576) {[}\protect\hyperlink{ref-VPUOQA2P}{29}--\protect\hyperlink{ref-EwNL0C0Y}{31},\protect\hyperlink{ref-whEyWyQh}{32},\protect\hyperlink{ref-QfVloFVu}{33}{]}.
 This process brings all specimens to a common origin, scales the landmarks to a unit centroid size, and rotates specimens to reduce distances between landmarks.
@@
 Based on this detected location we were then able to efficiently extract a cropped region of interest from the original data which includes only the region of the otoliths.
-The whole method is implemented in its own \href{https://github.com/habi/EAWAG/blob/master/ExtractOtoliths.ipynb}{\emph{Jupyter} notebook} (part of the aforementioned analysis repository {[}\protect\hyperlink{ref-1HteOscVd}{16}{]}).
+The whole method is implemented in its own \href{https://github.com/habi/EAWAG/blob/master/ExtractOtoliths.ipynb}{\emph{Jupyter} notebook} (part of the aforementioned analysis repository {[}\protect\hyperlink{ref-1HteOscVd}{19}{]}).
 
@@
 The extracted otoliths are thus prepared for further analysis and visualization.
-The simple three-dimensional visualization is integrated in the aforementioned \emph{Jupyter} notebook through an integrated visualization library {[}\protect\hyperlink{ref-a9ZL41Of}{30}{]} and is also shown in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}.
+The simple three-dimensional visualization is integrated in the aforementioned \emph{Jupyter} notebook through an integrated visualization library {[}\protect\hyperlink{ref-a9ZL41Of}{34}{]} and is also shown in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}.
 
@@
 
-The notebook for extracting the otoliths can be run in your browser without installing any additional software (via \emph{Binder} {[}\protect\hyperlink{ref-Q20Bxdsr}{31}{]}).
-To do this, one starts the notebook by \href{https://mybinder.org/v2/gh/habi/eawag/HEAD?labpath=ExtractOtoliths.ipynb}{clicking a single button} in the \href{https://github.com/habi/EAWAG/blob/master/README.md}{README file} of the \href{https://github.com/habi/EAWAG}{project repository} {[}\protect\hyperlink{ref-1HteOscVd}{16}{]}.
+The notebook for extracting the otoliths can be run in your browser without installing any additional software (via \emph{Binder} {[}\protect\hyperlink{ref-Q20Bxdsr}{35}{]}).
+To do this, one starts the notebook by \href{https://mybinder.org/v2/gh/habi/eawag/HEAD?labpath=ExtractOtoliths.ipynb}{clicking a single button} in the \href{https://github.com/habi/EAWAG/blob/master/README.md}{README file} of the \href{https://github.com/habi/EAWAG}{project repository} {[}\protect\hyperlink{ref-1HteOscVd}{19}{]}.
 This starts a computing environment in the cloud, downloads the tomographic data we acquired of \emph{one} specimen, and performs both the otolith extraction and visualization in your browser.
@@
 The workflow is relying only on free and open-source software and can thus be used and verified independently by any interested reader.
-All the \emph{Jupyter} notebook described herein is also freely available online {[}\protect\hyperlink{ref-1HteOscVd}{16}{]}.
+All the \emph{Jupyter} notebook described herein is also freely available online {[}\protect\hyperlink{ref-1HteOscVd}{19}{]}.
 
@@
 We are grateful to the \href{https//www.mic.unibe.ch/}{Microscopy Imaging Center} of the University of Bern for the infrastructural support.
-We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{32}{]} for helping us write this manuscript collaboratively.
+We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{36}{]} for helping us write this manuscript collaboratively.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-IKVBgaCE}{}}%
+\CSLLeftMargin{7. }
+\CSLRightInline{Rawson SD, Maksimcuka J, Withers PJ, Cartmell SH.
+X-ray computed tomography in life sciences.
+BMC Biol.
+2020;18.
+doi:\href{https://doi.org/10.1186/s12915-020-0753-2}{10.1186/s12915-020-0753-2}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-8Pmc2mI8}{}}%
-\CSLLeftMargin{7. }
+\CSLLeftMargin{8. }
 \CSLRightInline{Messerli M, Aaldijk D, Haberthür D, Röss H, García-Poyatos C, Sande-Melón M, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-BDrCSu8p}{}}%
-\CSLLeftMargin{8. }
+\CSLLeftMargin{9. }
 \CSLRightInline{Ford KL, Peterson R, Bernt M, Albert JS.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3rxGCEvJ}{}}%
-\CSLLeftMargin{9. }
+\CSLLeftMargin{10. }
 \CSLRightInline{Available: \url{https://osf.io/ecmz4}}
 
+\leavevmode\vadjust pre{\hypertarget{ref-pN1S9E5p}{}}%
+\CSLLeftMargin{11. }
+\CSLRightInline{Descamps E, Sochacka A, De Kegel B, Van Loo D, Van Hoorebeke L, Adriaens D.
+Soft tissue discrimination with contrast agents using micro-CT scanning.
+Belg J Zool.
+2020;144.
+doi:\href{https://doi.org/10.26496/bjz.2014.63}{10.26496/bjz.2014.63}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kkBa4qNV}{}}%
+\CSLLeftMargin{12. }
+\CSLRightInline{Babaei F, Hong TLC, Yeung K, Cheng SH, Lam YW.
+Contrast-Enhanced X-Ray Micro-Computed Tomography as a Versatile Method for Anatomical Studies of Adult Zebrafish.
+Zebrafish.
+2016;13: 310--316.
+doi:\href{https://doi.org/10.1089/zeb.2016.1245}{10.1089/zeb.2016.1245}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-VCZPOv2f}{}}%
-\CSLLeftMargin{10. }
+\CSLLeftMargin{13. }
 \CSLRightInline{Available: \url{https://github.com/TomoGraphics/Hol3Drs/blob/master/STL/EAWAG.Fish.stl}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-115PPSuQp}{}}%
-\CSLLeftMargin{11. }
+\CSLLeftMargin{14. }
 \CSLRightInline{Haberthür D. TomoGraphics/Hol3Drs: A release. Zenodo; 2019. doi:\href{https://doi.org/10.5281/zenodo.2587555}{10.5281/zenodo.2587555}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{OpenSCAD. {[}cited 11 Jul 2023{]}. Available: \url{https://openscad.org}}
+\CSLLeftMargin{15. }
+\CSLRightInline{OpenSCAD. {[}cited 13 Jul 2023{]}. Available: \url{https://openscad.org}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-f7OzrzUv}{}}%
-\CSLLeftMargin{13. }
+\CSLLeftMargin{16. }
 \CSLRightInline{Available: \url{https://github.com/TomoGraphics/Hol3Drs/blob/master/EAWAG.Fish.scad}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZjgrPHTa}{}}%
-\CSLLeftMargin{14. }
+\CSLLeftMargin{17. }
 \CSLRightInline{Available: \url{https://github.com/habi/EAWAG/blob/master/rsync-fishes.sh}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pQ6Wbz73}{}}%
-\CSLLeftMargin{15. }
+\CSLLeftMargin{18. }
 \CSLRightInline{Kluyver T, Ragan-Kelley B, Pérez F, Granger B, Bussonnier M, Frederic J, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1HteOscVd}{}}%
-\CSLLeftMargin{16. }
+\CSLLeftMargin{19. }
 \CSLRightInline{Haberthür D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-19qQOHlFN}{}}%
-\CSLLeftMargin{17. }
+\CSLLeftMargin{20. }
 \CSLRightInline{Team TPD. pandas-dev/pandas: Pandas. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.7093122}{10.5281/zenodo.7093122}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-U5AcoDOX}{}}%
-\CSLLeftMargin{18. }
+\CSLLeftMargin{21. }
 \CSLRightInline{McKinney W.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hj1CnyWB}{}}%
-\CSLLeftMargin{19. }
+\CSLLeftMargin{22. }
 \CSLRightInline{Dask Development Team. Dask: Library for dynamic task scheduling. 2016. Available: \url{https://dask.org}}
 
+\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
+\CSLLeftMargin{23. }
+\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.03.0+6.g08d1f74.dirty documentation. {[}cited 13 Jul 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-OsCpHsJH}{}}%
-\CSLLeftMargin{20. }
+\CSLLeftMargin{24. }
 \CSLRightInline{Fedorov A, Beichel R, Kalpathy-Cramer J, Finet J, Fillion-Robin J-C, Pujol S, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MwdN6kPV}{}}%
-\CSLLeftMargin{21. }
+\CSLLeftMargin{25. }
 \CSLRightInline{Rolfe S, Pieper S, Porto A, Diamond K, Winchester J, Shan S, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 11 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
+\CSLLeftMargin{26. }
+\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 13 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-JtHcU2O2}{}}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{27. }
 \CSLRightInline{Kishe-Machumu MA, van Rijssel JC, Poste A, Hecky RE, Witte F.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-15FafMZm5}{}}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{28. }
 \CSLRightInline{Ford KL, Bernt MJ, Summers AP, Albert JS.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-VPUOQA2P}{}}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Collyer ML, Adams DC. RRPP: An
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Ziptbtib}{}}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Adams DC, Collyer ML, Kaliontzopoulou A, Baken EK.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-EwNL0C0Y}{}}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Collyer ML, Adams DC.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-whEyWyQh}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{32. }
 \CSLRightInline{R Core Team. R: A language and environment for statistical computing. Vienna, Austria: R Foundation for Statistical Computing; 2018. Available: \url{https://www.R-project.org/}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-QfVloFVu}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{33. }
 \CSLRightInline{RStudio Team. RStudio: Integrated development environment for r. Boston, MA: RStudio, PBC.; 2022. Available: \url{https://www.rstudio.com/}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-a9ZL41Of}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{34. }
 \CSLRightInline{K3D Jupyter. K3D-tools; 2023. Available: \url{https://github.com/K3D-tools/K3D-jupyter}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Q20Bxdsr}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{35. }
 \CSLRightInline{Jupyter P, Bussonnier M, Forde J, Freeman J, Granger B, Head T, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{36. }
 \CSLRightInline{Himmelstein DS, Rubinetti V, Slochower DR, Hu D, Malladi VS, Greene CS, et al.

### 2023-07-13 content/submission/plos_revision1/answer_to_reviewers.md
Spell check

@@
 Sometimes errors or problems were only spotted at a later stage, when either the pharyngeal or oral jaws were extracted, or when we noticed that some part of the the whole skull were out of the field of view of the tomographic scan prior to performing the PCA analysis mentioned later in the manuscript.
-This means that specifying this as 'sanity check' is more of a glorified wording of telling the readers that we manually looked at the values of each performed tomographic scan to exlude and catch operator errors.
+This means that specifying this as 'sanity check' is more of a glorified wording of telling the readers that we manually looked at the values of each performed tomographic scan to exclude and catch operator errors.
 We reworded the sentence to hopefully make this more clear.

### 2023-07-14 content/submission/plos_revision1/answer_to_reviewers.md
Specify details of stacked scans
Now that we parse them correctly: https://github.com/habi/BrukerSkyScanLogfileRuminator/commit/d2a3ac39c7bfc029d26b789e9ea7e2f149520541

@@
 
-The statement over the 'wide-spanning range of voxel sizes' is *not* incorrect, at most---if applied to *one* speciment---imprecise.
-The range of voxel sizes is true for the whole study, while---as also correctly noted by the reviewer---the voxel size is specimen-specific.
-We clarified this paragraph by adding a more precise explanation.
+The statement over the 'wide-spanning range of voxel sizes' is *not* incorrect, at most---if applied to *one* specimen---imprecise.
+The range of voxel sizes is true for the whole study, while---as also correctly noted by the reviewer---the voxel size is specimen- or scan-specific.
+We have added a bit of explanatory text to the discussion section.
 

### 2023-07-14 manuscript.tex
Specify details of stacked scans [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/e3778df7e37340d9ba95d4eabfe433cd259fef1f.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/e3778df7e37340d9ba95d4eabfe433cd259fef1f/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5554621680

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...a15f6a93f7f5b262f005c909a8fdcbdf8220da53}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...e3778df7e37340d9ba95d4eabfe433cd259fef1f}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/a15f6a93f7f5b262f005c909a8fdcbdf8220da53/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/e3778df7e37340d9ba95d4eabfe433cd259fef1f/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/a15f6a93f7f5b262f005c909a8fdcbdf8220da53}{habi/EAWAG-manuscript@a15f6a9}
-on July 13, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/e3778df7e37340d9ba95d4eabfe433cd259fef1f}{habi/EAWAG-manuscript@e3778df}
+on July 14, 2023.
 
@@
 Projection images spanning either 180° or 360° of sample rotation were acquired in angular steps of 0.1°, 0.15° or 0.2°, also depending on size of the fish.
+Since the region of interest (either oral or pharyngeal jaws or the complete skulls of the fish) often did not fit into a single field of view at the voxel size needed to resolve the details needed, we often scanned several stacks along the rotation axis of the specimen in the machine.
+These so-called stacked scans are automatically merged to one stack of reconstructions images by the reconstruction software.
 In total we recorded 9.8 TB of projection images (\texttt{TIFF} and \texttt{*.iif} files, where the \texttt{*.iif} files are for the so-called alignment scans).
@@
 \CSLLeftMargin{15. }
-\CSLRightInline{OpenSCAD. {[}cited 13 Jul 2023{]}. Available: \url{https://openscad.org}}
+\CSLRightInline{OpenSCAD. {[}cited 14 Jul 2023{]}. Available: \url{https://openscad.org}}
 
@@
 \CSLLeftMargin{23. }
-\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.03.0+6.g08d1f74.dirty documentation. {[}cited 13 Jul 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
+\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.03.0+7.g44908b3.dirty documentation. {[}cited 14 Jul 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
 
@@
 \CSLLeftMargin{26. }
-\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 13 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
+\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 14 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
 

### 2023-07-14 manuscript.tex
Explain details of voxel size and stacked scans [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/a690fe23582f53c283f038e12d0f163b7ffa128a.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/a690fe23582f53c283f038e12d0f163b7ffa128a/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5554735504

--- 2023-07-13 manuscript.tex
@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...a15f6a93f7f5b262f005c909a8fdcbdf8220da53}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...a690fe23582f53c283f038e12d0f163b7ffa128a}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/a15f6a93f7f5b262f005c909a8fdcbdf8220da53/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/a690fe23582f53c283f038e12d0f163b7ffa128a/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/a15f6a93f7f5b262f005c909a8fdcbdf8220da53}{habi/EAWAG-manuscript@a15f6a9}
-on July 13, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/a690fe23582f53c283f038e12d0f163b7ffa128a}{habi/EAWAG-manuscript@a690fe2}
+on July 14, 2023.
 
@@
 We acquired datasets with (isometric) voxel sizes ranging from 3.5 to 50 μm.
+Due to the geometric magnification employed by the Bruker SkyScan microCT machines, the voxel size of the resulting dataset is depending on the position of the specimen in the machine.
+Natually, the field of view of the resulting dataset also depends on the chosen voxel size.
+The chosen voxel size is thus scan-specific.
+It was always chosen in a way that the region of interest to be images fit into the available lateral field of view of the microCT machine at the smallest necessary voxel size to resolve the structures of interest.
+Since the region of interest (either oral or pharyngeal jaws or the complete skulls of the fish) often did not fit into a single field of view \emph{along} the anteroposterior axis of the fish, we often performed several tomographic scans along the rotation axis of the specimen in the machine (since the specimen were all scanned rotating around the anteroposterior axis).
+The projection images from those so-called stacked scans are subsequently automatically merged to one stack of reconstructions images by the reconstruction software.
 
 Depending on the size of the specimen we set the X-ray source voltage to 50--80 kV and---depending on the voltage---to a current between 107 and 200 μA.
+The different voltages and currents were chosen according to the Bruker guidelines for ideal image acquisition.
 The X-ray spectrum was filtered either by an aluminum filter of varying thickness (either 0.25, 0.5 or 1 mm for increasing specimen size) before digitization to projection images or recorded in an unfiltered way (for smaller specimen).
@@
 
-All the recorded projection images were subsequently reconstructed into virtual 3D stacks of axial \texttt{PNG} images spanning the regions of interest of each fish.
+All the recorded projection images were subsequently reconstructed into three-dimensional stacks of axial \texttt{PNG} images spanning the desired regions of interest of each specimen.
 All the specimens were scanned with their mouths facing downward in the sample holder and rotating along their long axis.
@@
 The 372 acquired datasets were imaged over a wide-spanning range of voxel size (3.5--50 μm) permitting both the analysis of finest details we wanted to resolve (i.e.~containing only the oral and pharyngeal jaws) and having datasets (N=104) containing the whole head for principle components analysis and extraction of the otoliths.
+In our microCT imaging setup the resulting voxel size is directly correlated with the sample diameter, i.e.~smaller specimen were scanned with the smallest voxel size, in the range of several μm.
+The skulls of larger specimen were scanned with the largest voxel sizes, in the range of several tens of μm.
+The chosen voxel size is thus specimen- or scan-specific and was always selected such that the desired region of interest fits into the available lateral field of view of the microCT machine at the minimally necessary voxel size to resolve the structures of interest.
 

### 2023-07-17 content/submission/plos_revision1/answer_to_reviewers.md
Explain details of voxel size and stacked scans
Discuss otolith extraction

@@
 The range of voxel sizes is true for the whole study, while---as also correctly noted by the reviewer---the voxel size is specimen- or scan-specific.
-We have added a bit of explanatory text to the discussion section.
+We have added a bit of explanatory text to both the materials and discussion section.
 
 > It would be beneficial to include references in the discussion section to support the arguments and provide a broader context for the findings.
+
+The main scientific 'use case' of the method focuses on the automated, non-destructive extraction of the otolith volume from the tomographic data.
+To the best of our knowledge, our manuscript is the first to describe such a method.
+We have found two references describing otoliths or otolith structure, both on explanted otoliths.
+We have added those to the discussion section.
 

### 2023-07-17 content/submission/plos_revision1/answer_to_reviewers.md
Update date

@@
 author: David Haberthür
-date: 3.7.2023
+date: 17.7.2023
 ---

### 2023-07-17 manuscript.tex
Comment otolith extraction notebook [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/1f10c12e87d556170c61c2bcd4900dcecb5035ed.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/1f10c12e87d556170c61c2bcd4900dcecb5035ed/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5577126248

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...a690fe23582f53c283f038e12d0f163b7ffa128a}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...1f10c12e87d556170c61c2bcd4900dcecb5035ed}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/a690fe23582f53c283f038e12d0f163b7ffa128a/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/1f10c12e87d556170c61c2bcd4900dcecb5035ed/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/a690fe23582f53c283f038e12d0f163b7ffa128a}{habi/EAWAG-manuscript@a690fe2}
-on July 14, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/1f10c12e87d556170c61c2bcd4900dcecb5035ed}{habi/EAWAG-manuscript@1f10c12}
+on July 17, 2023.
 
@@
 
+To our best knowledge, no fully automated method for non-destructive otolith extraction from high-resolution tomographic data has been published up to now.
+Vasconcelos-Filho et al.~{[}doi:10.3389/fmars.2019.00728{]} show a potentially objective method to count growth rings in otoliths of six fish species, but performed their study on extracted otoliths ``embedded in a styrofoam cube'', while our method non-destructively extracts the otoliths from the tomographic data.
+Gu et al.
+{[}\protect\hyperlink{ref-HYXdLQTV}{36}{]} also provide detailed insight into otolith and combine microtomographic imaging (with unknown voxel size) with scanning electron microscopy, but also mention that the ``otoliths were removed {[}from \emph{Bahaba taipingensis}{]}, cleaned and kept dry for morphologic observation''.
+
 \hypertarget{outlook}{%
@@
 We are grateful to the \href{https//www.mic.unibe.ch/}{Microscopy Imaging Center} of the University of Bern for the infrastructural support.
-We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{36}{]} for helping us write this manuscript collaboratively.
+We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{37}{]} for helping us write this manuscript collaboratively.
 
@@
 \CSLLeftMargin{15. }
-\CSLRightInline{OpenSCAD. {[}cited 14 Jul 2023{]}. Available: \url{https://openscad.org}}
+\CSLRightInline{OpenSCAD. {[}cited 17 Jul 2023{]}. Available: \url{https://openscad.org}}
 
@@
 \CSLLeftMargin{23. }
-\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.03.0+7.g44908b3.dirty documentation. {[}cited 14 Jul 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
+\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.03.0+7.g44908b3.dirty documentation. {[}cited 17 Jul 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
 
@@
 \CSLLeftMargin{26. }
-\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 14 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
+\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 17 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-HYXdLQTV}{}}%
+\CSLLeftMargin{36. }
+\CSLRightInline{Gu Y-G, Huang H-H, Liang Y, Fang Y, Dai M, Ou Y-J, et al.
+Micro-CT and SEM investigation of sound absorption structure and chambers in the otoliths of Giant Panda fish species - Chinese Bahaba (Bahaba taipingensis).
+Micron.
+2022;161: 103342.
+doi:\href{https://doi.org/10.1016/j.micron.2022.103342}{10.1016/j.micron.2022.103342}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Himmelstein DS, Rubinetti V, Slochower DR, Hu D, Malladi VS, Greene CS, et al.

### 2023-07-17 manuscript.tex
Directly link to changes files, not commits [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/c49d0b8ac8f078c226318972b06e8c4a39100bb2.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/c49d0b8ac8f078c226318972b06e8c4a39100bb2/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5577316309

@@
 \emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...1f10c12e87d556170c61c2bcd4900dcecb5035ed}{has been updated} since submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...c49d0b8ac8f078c226318972b06e8c4a39100bb2\#files_bucket}{has been updated} since submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/1f10c12e87d556170c61c2bcd4900dcecb5035ed/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/1f10c12e87d556170c61c2bcd4900dcecb5035ed}{habi/EAWAG-manuscript@1f10c12}
+from \href{https://github.com/habi/EAWAG-manuscript/tree/c49d0b8ac8f078c226318972b06e8c4a39100bb2}{habi/EAWAG-manuscript@c49d0b8}
 on July 17, 2023.

### 2023-07-21 content/submission/plos_revision1/answer_to_reviewers.md
Comment otolith extraction notebook
Spell check

@@
 We've deliberately kept the introduction rather terse.
-The justification of the work lies in the non-desctructive imaging of unstained samples.
+The justification of the work lies in the non-destructive imaging of unstained samples.
 We have expanded the introduction a bit and added references to manuscripts detailing microtomographic imaging in the life sciences.
-As this manuscript is not a review, we kindly refuse to add more information on the background of microtomogrpahic imaging.
+As this manuscript is not a review, we kindly refuse to add more information on the background of microtomographic imaging.
 
@@
 The notebooks are written in Python, and are presented as Jupyter notebooks.
-This makes them accessible 'piecewise', e.g. each part of the code is didactically separate and somehow compartmentalized.
+This makes them accessible 'piece wise', e.g. each part of the code is didactically separate and somehow compartmentalized.
 The code is written in Python, so some experience with it is beneficial to thoroughly understand it.
@@
 As mentioned above, the Jupyter notebook used to detect the otolith position and to extract the otoliths from the scans covering the whole skull are extensively commented.
-We have added more explanatory comments and text to the notebook on GitHub, increading their didactiveness.
+We have added more explanatory comments and text to the notebook on GitHub, increasing their 'didactiveness'.
 
@@
 
+As mentioned above, we have improved both the text and the Jupyter notebooks (linked in the text) with explanatory sentences and comments.
+
 > By addressing these suggestions, the manuscript will become more comprehensive, accessible, and representative of the valuable contribution made by the authors.

### 2023-07-21 content/submission/plos_revision1/AnswerLetter.tex
Add LaTeX source of 'answer to reviewers'

\documentclass[color,english,personal]{ubletter}
\usepackage{siunitx}

\begin{document}
\begin{letter}{}
\subject{Submission of revised manuscript PONE-D-23-10896}

\opening{Dear Michael Schubert, Jay Richard Stauffer, Jr.\ and anonymous reviewer \#2}

We thank you for the opportunity to resubmit a revised version of our manuscript on the \emph{Microtomographic investigation of a large corpus of cichlids}.
We have implemented your suggestions and comments and considerably improved the manuscript.

Below, you will find our point-by-point response to the raised issues.

\begin{quote}
Reviewer \#1: Excellent paper. It was not clear if you could discern
daily rings on the otoliths. You might want to discuss if you can use
rings on otoliths to age the fish without removing them. Also, do you
have to stain the fish to use these rings?
\end{quote}

The data shown in this manuscript is from unstained specimen. They have
been stored in ethanol and imaged in wet foam to avoid any drying during
imaging, but \emph{no} staining was applied. Since we here only focus on
the morphology of the skull and teeth such a staining was not necessary
to extract the needed data from the tomographic images. Growth rings
would most probably be visible in the analyzed specimens, but only if
some staining is applied, e.g.~by storing the fish in Lugol solution.
Since this was \emph{not} the focus of the present study we did not do
this here.

To use the data on both growth rings and volume of the otoliths one
would have to calibrate this first to be able to extract age estimates.
I.e.\ one would have to make a simple growth experiment where a number of
fish with known age are euthanized, tomographically imaged and then the
volume of their extracted otoliths is correlated with their age. Such a
calibration would match size and volume of both the (lab-raised) fish
and the otoliths with the age of the fish. This data could then be used
to estimate the age of fishes collected in the wild.

\begin{quote}
Reviewer \#2: I have carefully evaluated the manuscript titled
``Microtomographic investigation of a large corpus of cichlids''. The
authors present a substantial collection of tomographic images from
cichlids collected in Lake Victoria, Africa. They showcase significant
cranial, maxillary, and otolith images from 362 specimens and provide
open-source Python notebooks to facilitate the manipulation and
extraction of specific parts. I believe that this work represents a
significant contribution to the understanding of cichlids and the
application of Micro-CT imaging in fish studies. However, I have some
suggestions to improve the manuscript:
\end{quote}

Thank you very much for the kind words. As we (now) state in the
\href{https://habi.github.io/EAWAG-manuscript/\#micro-computed-tomographic-imaging}{imaging
section} we acquired 372 single tomographic scans of 133 different
specimen (updated since submission of the manuscript, as a rest of fish
relevant for the study was added). This means that each specimen was
scanned several times, usually one lower-resolution scan of the full
head and two single higher-resolution scans for the oral and pharyngeal
jaws.

\begin{quote}
The introduction section needs improvement. It is too simplistic and
lacks informative details about the state of the art and the
justification for the work.
\end{quote}

We've deliberately kept the introduction rather terse. The justification
of the work lies in the non-destructive imaging of unstained samples. We
have expanded the introduction a bit and added references to manuscripts
detailing microtomographic imaging in the life sciences. As this
manuscript is not a review, we kindly refuse to add more information on
the background of microtomographic imaging.

\begin{quote}
Merging the Materials and Methods section with the Results is not a
reasonable way to present the work. It would be better to separate them
for clarity.
\end{quote}

The manuscript is focused on the method on how to acquire and assess
tomographic datasets of a large corpus of cichlids. Especially for the
image processing part, the method and results are highly intertwined as
the Python code directly delivers the results. We believe that the
approach we chose here here is the most appropriate way to present the
whole data data acquisition and analysis pipeline and kindly ask the
reviewer to accept our choice.

\begin{quote}
The section on Micro-computed tomographic imaging should be the core of
the paper and explained in more detail. The authors have extensive
experience scanning 362 fish specimens of different species and sizes.
Therefore, a detailed imaging protocol that can assist readers in
obtaining new images should be provided. For example, what criteria did
the authors use to select the best set of parameters? It is clear and
expected that larger fish would have lower resolution (larger voxel
size), but how does the relationship between size and parameters work?
How was the filter thickness chosen?
\end{quote}

As stated above and in the text, we acquired 372 single tomographic
scans of 133 different specimen.

\begin{quote}
The first sentence of the last paragraph of the subsection
Micro-computed tomographic imaging is unclear: ``While performing the
work, a subset of the data was always present on the production system,
for working with it (see Preparation for analysis below)''. Please
provide more precise information.
\end{quote}

We are sorry for the imprecise description of the data archival and
copying process. The last paragraph of
\href{https://habi.github.io/EAWAG-manuscript/\#micro-computed-tomographic-imaging}{this
section} was expanded and improved.

\begin{quote}
The authors should revise the entire ``Data analysis'' subsection to
present a more didactic version that helps any reader use the notebooks.
Currently, it seems that only Python users with some expertise can
understand what needs to be done. Perhaps the authors could provide a
guide or tutorial in the GitHub repository.
\end{quote}

The notebooks are written in Python, and are presented as Jupyter
notebooks. This makes them accessible `piece wise', e.g.~each part of
the code is didactically separate and somehow compartmentalized. The
code is written in Python, so some experience with it is beneficial to
thoroughly understand it. The code and notebooks are also prepared in a
way that \emph{no} installation of \emph{any} software except an up-to
date web browser is necessary to test it. This testing can be done by
clicking one button in the code repository (linking to
https://mybinder.org/v2/gh/habi/eawag/HEAD) to launch a Jupyter
environment in the cloud, which is also already explained in the last
paragraph before the
\href{https://habi.github.io/EAWAG-manuscript/\#discussion}{Discussion
section}. We understand the concerns of the reviewer though, and added
explanation text and comments to the notebooks guiding (first time)
users of the notebooks. All these updates happen in
\href{https://github.com/habi/EAWAG}{the code repository} and have
\emph{not} been specifically mentioned in the manuscript text. Two of
the notebooks
(\href{https://nbviewer.org/github/habi/EAWAG/blob/main/DataWrangling.ipynb}{DataWrangling}
and
\href{https://nbviewer.org/github/habi/EAWAG/blob/main/DataSize.ipynb}{DataSize})
were used to help us generate `checking' and `collaboration' files
(DataWrangling) or used to help us generate text for the manuscript,
i.e.~to extract exact details on sample numbers, total amount of
projections and reconstructions and their exact size on disk (DataSize).
As these notebooks are not explicitly mentioned in the manuscript they
are not extensively commented (only commented). The two notebooks
mentioned in the text
(\href{https://nbviewer.org/github/habi/EAWAG/blob/main/DisplayFishes.ipynb}{DisplayFishes})
and
(\href{https://nbviewer.org/github/habi/EAWAG/blob/main/ExtractOtoliths.ipynb}{ExtractOtoliths})
have been updated with more comments and explanatory text between the
logical steps. These additions are
\href{https://github.com/habi/EAWAG/compare/v1.1...HEAD}{visualized in
the respective GitHub repository}, but not specifically mentioned in the
text. We slightly expanded the description of the notebooks at the start
of the
\href{https://habi.github.io/EAWAG-manuscript/\#data-analysis}{Data
analysis section} though.

\begin{quote}
How was the sanity check performed (as mentioned in the second paragraph
of the subsection ``Preparation for Analysis'')?
\end{quote}

The mentioned `sanity check' was performed manually, e.g.~by looking at
all the values (mostly the reconstruction parameters), to exclude any
operator error. If errors were spotted at this stage, the
reconstructions were deleted and re-done with the correct parameters.
Sometimes errors or problems were only spotted at a later stage, when
either the pharyngeal or oral jaws were extracted, or when we noticed
that some part of the the whole skull were out of the field of view of
the tomographic scan prior to performing the PCA analysis mentioned
later in the manuscript. This means that specifying this as `sanity
check' is more of a glorified wording of telling the readers that we
manually looked at the values of each performed tomographic scan to
exclude and catch operator errors. We reworded the sentence to hopefully
make this more clear.

\begin{quote}
In the same paragraph, the authors mentioned that each tomographic
dataset contains around 2700 slices, exceeding the available RAM size on
an average high-end workstation. Could you clarify if this limitation
affected the analysis and its implications?
\end{quote}

We wrote that \emph{the total size of the acquired data exceeds the RAM}
of any workstation (e.g.~around 1.5 TB). \emph{One} or more single
datasets would fit into RAM very well, It is not possible to load
\emph{all} data concurrently for analysis. The use of \emph{Dask} and
more specifically \href{@https://image.dask.org/}{\emph{dask-image}} for
loading only the currently used data for each specimen from the HD (or
remote storage) into RAM on demand made working with the \emph{all} the
data feasible. We have updated the sentence to explain this.

\begin{quote}
The Wikipedia citation in the second paragraph of the subsection
``Extraction of oral and pharyngeal jaws\ldots{}'' is not clear. Please
provide more specific information or replace the citation with a more
appropriate reference.
\end{quote}

The Wikipedia citation to a \href{https://w.wiki/5mBK}{date-specific
version of the \texttt{Nrrd} article on Wikipedia} was not correctly
expanded by our manuscript preparation system. We replaced the Wikipedia
link with a more appropriate link to
\href{https://teem.sourceforge.net/nrrd/format.html}{the \texttt{Nrrd}
format definition} and thank the reviewer for noticing this issue.

\begin{quote}
Regarding the sentence ``In total, we compiled an overview of 125
specimens with full head morphology, oral jaw, and lower pharyngeal jaw
profiles,'' why was this done only for a subset of the sample? Please
explain the rationale.
\end{quote}

As stated above and in the text, we actually acquired 372 single
tomographic scans of 133 different specimen. It is correct though that
``125'' here is wrong, since we've acquired more scans after submission
of the manuscript. This has been corrected, and we thank the reviewer
for noticing this.

\begin{quote}
The results of the subsection ``Principal components analysis of skull
landmarks'' should be presented in a more accessible manner. Consider
providing a tutorial or guide for readers to better understand and apply
the analysis. As it currently stands, this subsection may be considered
irrelevant for the paper.
\end{quote}

This subsection is currently being `expanded' into a self-contained
publication. We deliberately only very briefly mentioned the method
here, as the upcoming publication is to be submitted soon.

\begin{quote}
The procedure for detecting and extracting otoliths in the subsection
``Automatic extraction of otoliths'' is not clear. Please provide
clearer instructions or guidelines for readers using the notebook.
\end{quote}

As mentioned above, the Jupyter notebook used to detect the otolith
position and to extract the otoliths from the scans covering the whole
skull are extensively commented. We have added more explanatory comments
and text to the notebook on GitHub, increasing their `didactiveness'.

\begin{quote}
Use the full words, rather than abbreviations, in figure legends for
clarity.
\end{quote}

Abbreviations in the legends have been written-out (except SI units).
Additionally we added a bit of background information on the specimen to
the legend of Fig. 1.

\begin{quote}
In the discussion section, the authors mentioned acquiring
high-resolution tomographic datasets of a large collection of cichlids.
However, the statement that ``the acquired datasets were imaged over a
wide-spanning range of voxel size (3.5--\SI{50}{\micro\meter})'' is incorrect. The voxel
size is specimen-specific, depending on the size of the fish and the
chosen parameters. Please clarify this point to accurately represent the
imaging process. The finest resolution was obtained only for small
fishes, so specific structures of a fish will have the same image
resolution throughout the entire specimen.
\end{quote}

The statement over the `wide-spanning range of voxel sizes' is
\emph{not} incorrect, at most---if applied to \emph{one}
specimen---imprecise. The range of voxel sizes is true for the whole
study, while---as also correctly noted by the reviewer---the voxel size
is specimen- or scan-specific. We have added a bit of explanatory text
to both the materials and discussion section.

\begin{quote}
It would be beneficial to include references in the discussion section
to support the arguments and provide a broader context for the findings.
\end{quote}

The main scientific `use case' of the method focuses on the automated,
non-destructive extraction of the otolith volume from the tomographic
data. To the best of our knowledge, our manuscript is the first to
describe such a method. We have found two references describing otoliths
or otolith structure, both on explanted otoliths. We have added those to
the discussion section.

\begin{quote}
Overall, the study seems to have spanned a considerable time frame.
However, the manuscript's content and structure need improvement to
reach a wider audience and effectively communicate the significance of
the work. The authors have provided a valuable set of open-source Python
notebooks, which is commendable and will be highly useful for the
scientific community. However, the workflow needs to be better explained
to enable readers to follow the procedures accurately.
\end{quote}

As mentioned above, we have improved both the text and the Jupyter
notebooks (linked in the text) with explanatory sentences and comments.

\begin{quote}
By addressing these suggestions, the manuscript will become more
comprehensive, accessible, and representative of the valuable
contribution made by the authors.
\end{quote}

We thank the reviewer for the kind words and the time spent on improving
our work with relevant questions and comments. The manuscript has
considerably improved by the updates we have performed.

We are looking forward to all your feedback if there is any remaining.

\addtolength{\medskipamount}{-\medskipamount} % skip some space with imported image
\closing{Yours sincerely\\\includegraphics[scale=0.618]{_Signature}}
\end{letter}
\end{document}

### 2023-07-21 manuscript.tex
Merge pull request #15 from habi/rootstock-2023-07-21 [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/3abb043a6e2aed52fd6af13c2ff321e9a640c139.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/3abb043a6e2aed52fd6af13c2ff321e9a640c139/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5623370536

--- 2023-07-14 manuscript.tex
@@
 \emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
-\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...a690fe23582f53c283f038e12d0f163b7ffa128a}{has been updated} since submission.}
+\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
+\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.1...3abb043a6e2aed52fd6af13c2ff321e9a640c139\#files_bucket}{is further updated} since re-submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/a690fe23582f53c283f038e12d0f163b7ffa128a/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/3abb043a6e2aed52fd6af13c2ff321e9a640c139/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/a690fe23582f53c283f038e12d0f163b7ffa128a}{habi/EAWAG-manuscript@a690fe2}
-on July 14, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/3abb043a6e2aed52fd6af13c2ff321e9a640c139}{habi/EAWAG-manuscript@3abb043}
+on July 21, 2023.
 
@@
   \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187} ·
-  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/habi}{habi}
   · \includegraphics[width=0.16667in,height=0.16667in]{images/mastodon.svg}
-  \href{https://mastodon.social/@habi}{habi}
+  \href{https://mastodon.social/@habi}{@habi@mastodon.social}
   Institute of Anatomy, University of Bern, Baltzerstrasse 2, CH-3012 Bern, Switzerland
@@
   \textbf{Mikki Law}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/mlaw-migalig}{mlaw-migalig}
@@
   \href{https://orcid.org/0000-0002-4413-2633}{0000-0002-4413-2633} ·
-  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/kassthefish}{kassthefish}
@@
   \textbf{Marcel Häsler}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/mphaesler}{mphaesler}
@@
   \href{https://orcid.org/0000-0001-6598-1434}{0000-0001-6598-1434} ·
-  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/OleSeehausen}{OleSeehausen}
@@
   \href{https://orcid.org/0000-0002-6722-8996}{0000-0002-6722-8996} ·
-  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/RuslanHlushchuk}{RuslanHlushchuk}
@@
 \end{itemize}
+
+\leavevmode\vadjust pre{\hypertarget{correspondence}{}}%
+✉ --- Correspondence possible via \href{https://github.com/habi/EAWAG-manuscript/issues}{GitHub Issues}
 
@@
 
-Depending on the structures of interest, biomedical samples are often only tomographically scanned after being stained with a contrast agent {[}\protect\hyperlink{ref-pN1S9E5p}{11}{]}, most often employing contrast agents containing heavy metals {[}\protect\hyperlink{ref-kkBa4qNV}{12}{]}.
+Depending on the structures of interest to be assessed, biomedical samples are often only tomographically scanned after them being stained with a contrast agent {[}\protect\hyperlink{ref-pN1S9E5p}{11}{]}, most often employing contrast agents containing heavy metals {[}\protect\hyperlink{ref-kkBa4qNV}{12}{]}.
+This is done to increase the contrast difference between different structures in the sample.
 Due to their inherent contrast difference to the surrounding tissue, the structures of interest we touch upon in this manuscript (teeth and bones, i.e.~jaws and skull) are well visualized in native samples.
@@
 Due to the geometric magnification employed by the Bruker SkyScan microCT machines, the voxel size of the resulting dataset is depending on the position of the specimen in the machine.
-Natually, the field of view of the resulting dataset also depends on the chosen voxel size.
+Naturally, the field of view of the resulting dataset also depends on the chosen voxel size.
 The chosen voxel size is thus scan-specific.
@@
 
+To our best knowledge, no fully automated method for non-destructive otolith extraction from high-resolution tomographic data has been published up to now.
+Vasconcelos-Filho et al.
+{[}\protect\hyperlink{ref-PgMc4mCy}{36}{]} show a potentially objective method to count growth rings in otoliths of six fish species, but performed their study on extracted otoliths ``embedded in a Styrofoam cube'', while our method non-destructively extracts the otoliths from the tomographic data.
+Gu et al.
+{[}\protect\hyperlink{ref-HYXdLQTV}{37}{]} also provide detailed insight into otolith and combine microtomographic imaging (with unknown voxel size) with scanning electron microscopy, but also mention that the ``otoliths were removed {[}from \emph{Bahaba taipingensis}{]}, cleaned and kept dry for morphologic observation''.
+
 \hypertarget{outlook}{%
@@
   >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
-\toprule
+\toprule()
 \begin{minipage}[b]{\linewidth}\raggedright
@@
 \end{minipage} \\
-\midrule
+\midrule()
 \endhead
@@
 Ruslan Hlushchuk & Conceptualization, Resources, Supervision, Writing -- review \& editing \\
-\bottomrule
+\bottomrule()
 \end{longtable}
@@
 We are grateful to the \href{https//www.mic.unibe.ch/}{Microscopy Imaging Center} of the University of Bern for the infrastructural support.
-We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{36}{]} for helping us write this manuscript collaboratively.
+We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{38}{]} for helping us write this manuscript collaboratively.
 
@@
 The three-dimensional view of sample 104016 was generated in \href{https://github.com/habi/EAWAG/blob/master/ExtractOtoliths.ipynb}{the otolith extraction notebook} and saved as a \href{https://github.com/habi/EAWAG-manuscript/blob/main/content/data/104016.head.rec.otolith.region.3D.html}{self-contained \texttt{HTML} file} with \href{https://github.com/K3D-tools/K3D-jupyter}{\emph{K3D-jupyter}}.
-A copy of this \texttt{HTML} file can be viewed and interacted with through the \href{https://htmlpreview.github.io/?https://github.com/habi/EAWAG-manuscript/blob/main/content/data/104016.head.rec.otolith.region.3D.html}{GitHub HTML preview}.
+A copy of this \texttt{HTML} file can be viewed and interacted with through the \href{https://htmlpreview.github.io/?https://github.com/habi/EAWAG-manuscript/blob/main/content/data/104016_Enterochromis_I_cinctus_St_E.head.rec.Otolith.Region.3D.html}{GitHub HTML preview}.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-TUQFenhc}{}}%
-\CSLLeftMargin{1. }
+\CSLLeftMargin{1. }%
 \CSLRightInline{Kocher TD. Adaptive evolution and explosive speciation: the cichlid fish model. Nat Rev Genet. 2004;5: 288--298. doi:\href{https://doi.org/10.1038/nrg1316}{10.1038/nrg1316}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-W2f2SDjn}{}}%
-\CSLLeftMargin{2. }
+\CSLLeftMargin{2. }%
 \CSLRightInline{Seehausen O.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-WVIa4CH0}{}}%
-\CSLLeftMargin{3. }
+\CSLLeftMargin{3. }%
 \CSLRightInline{Konings AF, Wisor JM, Stauffer JR Jr.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1GEljkDsf}{}}%
-\CSLLeftMargin{4. }
+\CSLLeftMargin{4. }%
 \CSLRightInline{Liem KF. Evolutionary Strategies and Morphological Innovations: Cichlid Pharyngeal Jaws. Systematic Zoology. 1973;22: 425. doi:\href{https://doi.org/10.2307/2412950}{10.2307/2412950}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-c3poTogo}{}}%
-\CSLLeftMargin{5. }
+\CSLLeftMargin{5. }%
 \CSLRightInline{Seehausen O.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-19h9vxsYG}{}}%
-\CSLLeftMargin{6. }
+\CSLLeftMargin{6. }%
 \CSLRightInline{Ford KL, Albert JS, Summers AP, Hedrick BP, Schachner ER, Jones AS, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-IKVBgaCE}{}}%
-\CSLLeftMargin{7. }
+\CSLLeftMargin{7. }%
 \CSLRightInline{Rawson SD, Maksimcuka J, Withers PJ, Cartmell SH.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-8Pmc2mI8}{}}%
-\CSLLeftMargin{8. }
+\CSLLeftMargin{8. }%
 \CSLRightInline{Messerli M, Aaldijk D, Haberthür D, Röss H, García-Poyatos C, Sande-Melón M, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-BDrCSu8p}{}}%
-\CSLLeftMargin{9. }
+\CSLLeftMargin{9. }%
 \CSLRightInline{Ford KL, Peterson R, Bernt M, Albert JS.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3rxGCEvJ}{}}%
-\CSLLeftMargin{10. }
+\CSLLeftMargin{10. }%
 \CSLRightInline{Available: \url{https://osf.io/ecmz4}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pN1S9E5p}{}}%
-\CSLLeftMargin{11. }
+\CSLLeftMargin{11. }%
 \CSLRightInline{Descamps E, Sochacka A, De Kegel B, Van Loo D, Van Hoorebeke L, Adriaens D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kkBa4qNV}{}}%
-\CSLLeftMargin{12. }
+\CSLLeftMargin{12. }%
 \CSLRightInline{Babaei F, Hong TLC, Yeung K, Cheng SH, Lam YW.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-VCZPOv2f}{}}%
-\CSLLeftMargin{13. }
+\CSLLeftMargin{13. }%
 \CSLRightInline{Available: \url{https://github.com/TomoGraphics/Hol3Drs/blob/master/STL/EAWAG.Fish.stl}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-115PPSuQp}{}}%
-\CSLLeftMargin{14. }
+\CSLLeftMargin{14. }%
 \CSLRightInline{Haberthür D. TomoGraphics/Hol3Drs: A release. Zenodo; 2019. doi:\href{https://doi.org/10.5281/zenodo.2587555}{10.5281/zenodo.2587555}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{OpenSCAD. {[}cited 14 Jul 2023{]}. Available: \url{https://openscad.org}}
+\CSLLeftMargin{15. }%
+\CSLRightInline{OpenSCAD. {[}cited 21 Jul 2023{]}. Available: \url{https://openscad.org}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-f7OzrzUv}{}}%
-\CSLLeftMargin{16. }
+\CSLLeftMargin{16. }%
 \CSLRightInline{Available: \url{https://github.com/TomoGraphics/Hol3Drs/blob/master/EAWAG.Fish.scad}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZjgrPHTa}{}}%
-\CSLLeftMargin{17. }
+\CSLLeftMargin{17. }%
 \CSLRightInline{Available: \url{https://github.com/habi/EAWAG/blob/master/rsync-fishes.sh}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pQ6Wbz73}{}}%
-\CSLLeftMargin{18. }
+\CSLLeftMargin{18. }%
 \CSLRightInline{Kluyver T, Ragan-Kelley B, Pérez F, Granger B, Bussonnier M, Frederic J, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1HteOscVd}{}}%
-\CSLLeftMargin{19. }
+\CSLLeftMargin{19. }%
 \CSLRightInline{Haberthür D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-19qQOHlFN}{}}%
-\CSLLeftMargin{20. }
+\CSLLeftMargin{20. }%
 \CSLRightInline{Team TPD. pandas-dev/pandas: Pandas. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.7093122}{10.5281/zenodo.7093122}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-U5AcoDOX}{}}%
-\CSLLeftMargin{21. }
+\CSLLeftMargin{21. }%
 \CSLRightInline{McKinney W.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hj1CnyWB}{}}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{22. }%
 \CSLRightInline{Dask Development Team. Dask: Library for dynamic task scheduling. 2016. Available: \url{https://dask.org}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.03.0+7.g44908b3.dirty documentation. {[}cited 14 Jul 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
+\CSLLeftMargin{23. }%
+\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.03.0+8.g88d81c6.dirty documentation. {[}cited 21 Jul 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-OsCpHsJH}{}}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{24. }%
 \CSLRightInline{Fedorov A, Beichel R, Kalpathy-Cramer J, Finet J, Fillion-Robin J-C, Pujol S, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MwdN6kPV}{}}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{25. }%
 \CSLRightInline{Rolfe S, Pieper S, Porto A, Diamond K, Winchester J, Shan S, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 14 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
+\CSLLeftMargin{26. }%
+\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 21 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-JtHcU2O2}{}}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{27. }%
 \CSLRightInline{Kishe-Machumu MA, van Rijssel JC, Poste A, Hecky RE, Witte F.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-15FafMZm5}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{28. }%
 \CSLRightInline{Ford KL, Bernt MJ, Summers AP, Albert JS.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-VPUOQA2P}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{29. }%
 \CSLRightInline{Collyer ML, Adams DC. RRPP: An
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Ziptbtib}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{30. }%
 \CSLRightInline{Adams DC, Collyer ML, Kaliontzopoulou A, Baken EK.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-EwNL0C0Y}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{31. }%
 \CSLRightInline{Collyer ML, Adams DC.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-whEyWyQh}{}}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{32. }%
 \CSLRightInline{R Core Team. R: A language and environment for statistical computing. Vienna, Austria: R Foundation for Statistical Computing; 2018. Available: \url{https://www.R-project.org/}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-QfVloFVu}{}}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{33. }%
 \CSLRightInline{RStudio Team. RStudio: Integrated development environment for r. Boston, MA: RStudio, PBC.; 2022. Available: \url{https://www.rstudio.com/}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-a9ZL41Of}{}}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{34. }%
 \CSLRightInline{K3D Jupyter. K3D-tools; 2023. Available: \url{https://github.com/K3D-tools/K3D-jupyter}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Q20Bxdsr}{}}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{35. }%
 \CSLRightInline{Jupyter P, Bussonnier M, Forde J, Freeman J, Granger B, Head T, et al.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-PgMc4mCy}{}}%
+\CSLLeftMargin{36. }%
+\CSLRightInline{Vasconcelos-Filho JE, Thomsen FSL, Stosic B, Antonino ACD, Duarte DA, Heck RJ, et al.
+Peeling the Otolith of Fish: Optimal Parameterization for Micro-CT Scanning.
+Front Mar Sci.
+2019;6.
+doi:\href{https://doi.org/10.3389/fmars.2019.00728}{10.3389/fmars.2019.00728}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-HYXdLQTV}{}}%
+\CSLLeftMargin{37. }%
+\CSLRightInline{Gu Y-G, Huang H-H, Liang Y, Fang Y, Dai M, Ou Y-J, et al.
+Micro-CT and SEM investigation of sound absorption structure and chambers in the otoliths of Giant Panda fish species - Chinese Bahaba (Bahaba taipingensis).
+Micron.
+2022;161: 103342.
+doi:\href{https://doi.org/10.1016/j.micron.2022.103342}{10.1016/j.micron.2022.103342}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{38. }%
 \CSLRightInline{Himmelstein DS, Rubinetti V, Slochower DR, Hu D, Malladi VS, Greene CS, et al.

### 2023-08-15 manuscript.tex
Merge pull request #16 from habi/rootstock-2023-07-21 [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/5b917ff57ead69077c03df93cc1bc121f2152c06.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/5b917ff57ead69077c03df93cc1bc121f2152c06/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5866657691

@@
 \emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.1...3abb043a6e2aed52fd6af13c2ff321e9a640c139\#files_bucket}{is further updated} since re-submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.1...5b917ff57ead69077c03df93cc1bc121f2152c06\#files_bucket}{is further updated} since re-submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/3abb043a6e2aed52fd6af13c2ff321e9a640c139/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/5b917ff57ead69077c03df93cc1bc121f2152c06/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/3abb043a6e2aed52fd6af13c2ff321e9a640c139}{habi/EAWAG-manuscript@3abb043}
-on July 21, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/5b917ff57ead69077c03df93cc1bc121f2152c06}{habi/EAWAG-manuscript@5b917ff}
+on August 15, 2023.
 
@@
   \href{https://github.com/kassthefish}{kassthefish}
-  Department of Biological Sciences, George Washington University, USA; Department of Fish Ecology and Evolution, Eawag, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland; Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland
+  Department of Biological Sciences, George Washington University, USA; Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, Eawag, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
 \item
@@
 \CSLLeftMargin{15. }%
-\CSLRightInline{OpenSCAD. {[}cited 21 Jul 2023{]}. Available: \url{https://openscad.org}}
+\CSLRightInline{OpenSCAD. {[}cited 15 Aug 2023{]}. Available: \url{https://openscad.org}}
 
@@
 \CSLLeftMargin{23. }%
-\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.03.0+8.g88d81c6.dirty documentation. {[}cited 21 Jul 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
+\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+1.g86b56a7.dirty documentation. {[}cited 15 Aug 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
 
@@
 \CSLLeftMargin{26. }%
-\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 21 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
+\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 15 Aug 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
 

### 2023-08-15 manuscript.tex
Merge branch 'main' of github.com:habi/EAWAG-manuscript into main [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/cf71b71e6291167fe12fef6359937f11e6552b5b.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/cf71b71e6291167fe12fef6359937f11e6552b5b/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5866679512

@@
 \emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.1...5b917ff57ead69077c03df93cc1bc121f2152c06\#files_bucket}{is further updated} since re-submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.1...cf71b71e6291167fe12fef6359937f11e6552b5b\#files_bucket}{is further updated} since re-submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/5b917ff57ead69077c03df93cc1bc121f2152c06/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/cf71b71e6291167fe12fef6359937f11e6552b5b/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/5b917ff57ead69077c03df93cc1bc121f2152c06}{habi/EAWAG-manuscript@5b917ff}
+from \href{https://github.com/habi/EAWAG-manuscript/tree/cf71b71e6291167fe12fef6359937f11e6552b5b}{habi/EAWAG-manuscript@cf71b71}
 on August 15, 2023.
@@
 
-A large collection of cichlids (N=133) from Lake Victoria in Africa spanning a length range of 6 to 18 cm was nondestructively imaged using micro-computed tomography.
-We describe our method to efficiently obtain three-dimensional tomographic datasets of the oral and pharyngeal jaws and the whole skull of these fishes for accurately describing their morphology.
+A large collection of cichlids (N=133) from Lake Victoria in Africa, with total lengths ranging from 6 to 18 cm, was nondestructively imaged using micro-computed tomography.
+We present a method to efficiently obtain three-dimensional tomographic datasets of the oral and pharyngeal jaws and the whole skull of these fishes to accurately describe their morphology.
 The tomographic data we acquired (9.8 TB of projection images) yielded 1.5 TB of three-dimensional image stacks used for extracting the relevant features of interest.
-Herein we present our method and an outlook on analyzing the acquired data; a morphological description of the oral and pharyngeal jaws of the fishes, a three-dimensional geometric morphometrics analysis of landmark features on the fish skulls, and a robust method to automatically extract the otoliths of the fishes from the tomographic data.
+Herein we present our method and outlooks on analyzing the acquired data; a morphological description of the oral and pharyngeal jaws, a three-dimensional geometric morphometrics analysis of landmarked skull features, and a robust method to automatically extract otoliths from the tomographic data.
 
@@
 
-Cichlid fish in African lakes are powerful model systems in speciation and adaptive evolutionary radiation research {[}\protect\hyperlink{ref-TUQFenhc}{1}--\protect\hyperlink{ref-WVIa4CH0}{3}{]}.
-The functional decoupling of their oral and pharyngeal jaws is hypothesized to be a factor in making cichlids unusually versatile in their feeding and allowing them the ability to adapt to a wide range of environmental factors {[}\protect\hyperlink{ref-1GEljkDsf}{4}{]}.
-The hypothesis is that the fusion of the lower pharyngeal jaws makes that jaw system a powerful food processing tool, in turn releasing the oral jaws from functional constraint.
+Cichlid fish in African lakes are powerful model systems for evolutionary biology in speciation and adaptive radiation research {[}\protect\hyperlink{ref-TUQFenhc}{1}--\protect\hyperlink{ref-WVIa4CH0}{3}{]}.
+The functional decoupling of their oral and pharyngeal jaws is hypothesized to be a factor in making cichlids unusually versatile in their feeding strategies, allowing them the ability to adapt to a wide range of environmental factors {[}\protect\hyperlink{ref-1GEljkDsf}{4}{]}.
+The hypothesis is that the fusion of the lower pharyngeal jaws enables it to become an adaptable tool for processing food, in turn releasing the oral jaws from functional constraint.
 The oral jaws no longer need to process prey and can therefore specialize on prey capture.
 
-Even though the evolutionary diversification of cichlid fish radiations in Lake Victoria in Africa is a well researched issue it remains a complex system in need of further study {[}\protect\hyperlink{ref-W2f2SDjn}{2},\protect\hyperlink{ref-c3poTogo}{5}{]}.
+Even though the evolutionary diversification of cichlid fish radiations in Lake Victoria, East Africa is a well researched topic, it remains a complex system in need of further study {[}\protect\hyperlink{ref-W2f2SDjn}{2},\protect\hyperlink{ref-c3poTogo}{5}{]}.
 We aim to better understand the functional anatomy of the skulls and jaws in these fish in order to test the functional decoupling and other hypotheses about what may facilitate exceptionally high rates of morphological evolution.
@@
 The collection of cichlid fish available is extremely valuable, hence a nondestructive imaging method is paramount for studying these samples.
-Since micro--computed tomography can be regarded as nondestructive method for biological samples, it is the ideal imaging method for investigating the oral and pharyngeal jaws as well as the skull features of the fish presented in this study {[}\protect\hyperlink{ref-19h9vxsYG}{6}{]} (N=133).
+Since micro--computed tomography can be regarded as a nondestructive investigation method for biological samples, it is the ideal imaging method for investigating the oral and pharyngeal jaws as well as the skull features of the fish presented in this study {[}\protect\hyperlink{ref-19h9vxsYG}{6}{]} (N=133).
 
@@
 
-Depending on the structures of interest to be assessed, biomedical samples are often only tomographically scanned after them being stained with a contrast agent {[}\protect\hyperlink{ref-pN1S9E5p}{11}{]}, most often employing contrast agents containing heavy metals {[}\protect\hyperlink{ref-kkBa4qNV}{12}{]}.
+Depending on the structures of interest to be assessed, biomedical samples are often only tomographically scanned after them being stained with a contrast agent {[}\protect\hyperlink{ref-pN1S9E5p}{11}{]}, most often applying contrast agents that contain heavy metals {[}\protect\hyperlink{ref-kkBa4qNV}{12}{]}.
 This is done to increase the contrast difference between different structures in the sample.
-Due to their inherent contrast difference to the surrounding tissue, the structures of interest we touch upon in this manuscript (teeth and bones, i.e.~jaws and skull) are well visualized in native samples.
-Enhancing contrast differences by staining prior to tomographic imaging was thus not necessary to for the samples presented herein.
+Due to their inherent contrast difference to the surrounding tissue, the structures of interest we touch upon in this manuscript (teeth and bones, i.e.~jaws and skull) are well visualized in the unstained samples.
+Thus, staining the samples presented in this manuscript prior to imaging was not necessary.
 
@@
 
-The study used specimens from an already existing fish collection, built over decades of research led by Ole Seehausen and continuing until today.
-All relevant permits for research, the permits for export from the respective country and import to Switzerland were given and the research has followed modern ethical guidelines for scientific research.
+The study used specimens from an already existing fish collection built over decades of research led by Ole Seehausen that continues to this day.
+All relevant permits for research, exportsfrom the respective country and import to Switzerland were given and the research has followed modern ethical guidelines for scientific research.
 
@@
 
-Since the fish greatly varied in their length (specimen length varied between 6 cm and 18 cm), the voxel sizes of each of the acquired datasets also varies greatly.
+Since the fish varied greatly in their length (total length varied between 6 cm and 18 cm), the voxel size of each dataset also varied greatly.
 We acquired datasets with (isometric) voxel sizes ranging from 3.5 to 50 μm.
-Due to the geometric magnification employed by the Bruker SkyScan microCT machines, the voxel size of the resulting dataset is depending on the position of the specimen in the machine.
-Naturally, the field of view of the resulting dataset also depends on the chosen voxel size.
+Due to the geometric magnification employed by the Bruker SkyScan microCT machines, the voxel size of the resulting dataset is dependent on the position of the specimen in the machine.
+Naturally, the field of view of the resulting dataset is also dependent on the chosen voxel size.
 The chosen voxel size is thus scan-specific.
-It was always chosen in a way that the region of interest to be images fit into the available lateral field of view of the microCT machine at the smallest necessary voxel size to resolve the structures of interest.
-Since the region of interest (either oral or pharyngeal jaws or the complete skulls of the fish) often did not fit into a single field of view \emph{along} the anteroposterior axis of the fish, we often performed several tomographic scans along the rotation axis of the specimen in the machine (since the specimen were all scanned rotating around the anteroposterior axis).
-The projection images from those so-called stacked scans are subsequently automatically merged to one stack of reconstructions images by the reconstruction software.
+The voxel size was chosen in a way that the region of interest would fit into the available lateral field of view of the microCT machine, as well as having the smallest required voxel size that could resolve the structures of interest.
+Since the region of interest (either oral or pharyngeal jaws or the complete skulls) often did not fit into a single field of view \emph{along} the anteroposterior axis of the fish, we often performed several tomographic scans along the rotation axis of the specimen in the machine (since the specimen were all scanned rotating around the anteroposterior axis).
+The projection images from those so-called stacked scans are then automatically merged to one stack of reconstruction images by the reconstruction software.
 
@@
 All the specimens were scanned with their mouths facing downward in the sample holder and rotating along their long axis.
-We thus manually aligned each of the reconstructed datasets so that the lateral axis of the fish was horizontal in relation to the x and y direction of the reconstructed slices.
+We manually aligned each of the reconstructed datasets so that the lateral axis of the fish was horizontal in relation to the x and y direction of the reconstructed slices.
 We reconstructed the projection images with NRecon (Version 1.7.4.6, Bruker microCT, Kontich, Belgium) with varying ring artifact and beam hardening correction values, depending on each fish (again, all relevant values are listed in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}).
@@
 This automated archival and copying process made it possible to delete the raw projection images on the production system shortly after acquisition, freeing resources and easing data handling.
-A subset of the data, namely the log files and reconstructed image stacks were kept on the production system for working with it (as described in \protect\hyperlink{preparation-for-analysis}{Preparation for analysis} below).
+A subset of the data, namely the log files and reconstructed image stacks were always kept on the production system for image processing (as described in \protect\hyperlink{preparation-for-analysis}{Preparation for analysis} below).
 
@@
 The first author of this study is happy to help other scientists to adapt the notebooks to their use-case.
-They notebooks are split into different task performed for this study and are specifically mentioned in the respective sections below.
+The notebooks are split into different tasks performed for this study and are specifically mentioned in the respective sections below.
 
@@
 
-At first, \emph{all} log files of \emph{all} the scan present in the processed folder were read into a \emph{pandas} {[}\protect\hyperlink{ref-19qQOHlFN}{20},\protect\hyperlink{ref-U5AcoDOX}{21}{]} dataframe.
+At first, \emph{all} log files of \emph{all} the scans present in the processed folder were read into a \emph{pandas} {[}\protect\hyperlink{ref-19qQOHlFN}{20},\protect\hyperlink{ref-U5AcoDOX}{21}{]} dataframe.
 This already enabled us to extract the specimen name and scan.
-Since we performed multiple scans for each specimen, i.e.~a low resolution scan with large field of view for the whole head and one or two scans in high resolution focusing on the region of the oral and pharyngeal jaws it was necessary to be able to efficiently find the scan to be looked at in detail.
-From the log files we extracted the scanning and reconstruction parameters of each performed scan for double-checking them and excluding (or necessarily correcting) any operator-error.
-All relevant values for each scan were also saved into the aforementioned ataframe.
+Since we performed multiple scans for each specimen, i.e.~a low resolution scan with large field of view for the whole head and one or two scans in high resolution focusing on the region of the oral and pharyngeal jaws, it was necessary to be able to efficiently find the scan to be looked at in detail.
+From the log files we extracted the scanning and reconstruction parameters of each performed scan to double-check them.
+This allowed us to exclude scans with unexpected values or errors and correct for those prior to a next run of the notebook.
+All relevant values for each scan were also saved into the aforementioned dataframe.
 This allows for an easy collation of all the relevant values into a table (as shown in the \protect\hyperlink{supplementary-materials}{Supplementary Materials}) at the end of each run of the notebook.
 
-After displaying several parameters of both data acquisition and reconstruction for ruling out any operator error we used \emph{Dask} {[}\protect\hyperlink{ref-hj1CnyWB}{22}{]} to efficiently access the tomographic data on disk (in the end amounting to a total of nearly a million single images).
-On average, each of the tomographic datasets contains around 2700 slices, so the total size of the acquired data (1.5 TB) exceeds the RAM size available on an average high-end workstation.
+After displaying several parameters of both data acquisition and reconstruction, for ruling out any operator error, we used \emph{Dask} {[}\protect\hyperlink{ref-hj1CnyWB}{22}{]} to efficiently access the tomographic data on disk (in the end amounting to a total of nearly a million single images).
+On average, each of the tomographic datasets contain around 2700 slices, so the total size of the acquired data (1.5 TB) exceeds the RAM size available on an average high-end workstation.
 The use of \emph{Dask} (and more specifically \emph{dask-image} {[}\protect\hyperlink{ref-wIfTDBqd}{23}/{]}) facilitated on-demand loading of the needed data directly from disk for each of the specimen to be analyzed in each step of the notebooks.
@@
 In this check we examined the mapping of the gray values of the raw projection images to gray values in the reconstructions, i.e.~checked that no overexposed pixels were present.
-This is an efficient way for double-checking the gray value mapping, since the MIP images have already been generated in prior steps of the notebook and contain the highest gray values present in all the reconstructed images for each scan.
+This is an efficient way to double-check the gray value mapping, since the MIP images have already been generated in prior steps of the notebook and contain the highest gray values present in all the reconstructed images for each scan.
 
@@
 
-Processed regions of interest were exported as \texttt{Nrrd} {[}\protect\hyperlink{ref-rn6XbmFW}{26}{]} files.
-The three-dimensional visualizations of all regions of interest for each specimen were compiled into overview images (see Figure \ref{fig:104016} for an example from the compilation document).
+Processed regions of interest were then exported as \texttt{Nrrd} {[}\protect\hyperlink{ref-rn6XbmFW}{26}{]} files.
+The three-dimensional visualizations of all regions of interest were compiled into overview images (see Figure \ref{fig:104016} for an example from the compilation document).
 In total, we compiled such overview images for 133 specimens with full head morphology, oral jaw and lower pharyngeal jaw profiles.
@@
 
-Since we took great care to scan the fish parallel to their anteroposterior direction and reconstructed the tomographic datasets parallel to the lateral and dorsoventral direction of the fish we could use this `preparation' for automatically extracting the otoliths the tomographic datasets of the whole fish heads.
-By extracting both the peaks and the peak widths of the gray values along both the horizontal and vertical direction of the MIP (generated above) we robustly detected the position of the otoliths in the datasets.
+Since we took great care to scan the fish parallel to their anteroposterior direction and reconstructed the tomographic datasets parallel to the lateral and dorsoventral direction of the fish, we could use this `preparation' for automatically extracting the otoliths.
+By extracting both the peaks and the peak widths of the gray values along both the horizontal and vertical direction of the MIP (generated above) we robustly detect the position of the otoliths in the datasets.
 The robust detection is supported by suppressing a small, configurable part of each region, i.e.~the front and back, top and bottom or the flanks.
@@
 Figure \ref{fig:otolithextraction} shows the visualization of the process.
-The colored horizontal and vertical bars in each of the directional MIPs denote the found peak location of the two appropriate values.
-The white bars show the mean of the to detected positions, which was used for extracting the otoliths from the original datasets.
+The colored horizontal and vertical bars in each of the directional MIPs denote the found peak location of the two values found in the two other directional views.
+The white bars show the mean of these two detected positions, which were used for extracting the otoliths from the original datasets.
 Making use of the \emph{Dask} library facilitated efficient access to all the data on disk and writing out small, cropped copies of the datasets around the otolith positions.
@@
 We acquired high resolution tomographic datasets of a large collection of cichlids (N=133), several tomographic scans were performed for each specimen.
-The 372 acquired datasets were imaged over a wide-spanning range of voxel size (3.5--50 μm) permitting both the analysis of finest details we wanted to resolve (i.e.~containing only the oral and pharyngeal jaws) and having datasets (N=104) containing the whole head for principle components analysis and extraction of the otoliths.
+The 372 acquired datasets were imaged over a wide-spanning range of voxel sizes (3.5--50 μm), permitting both the analysis of fine details we wanted to resolve (i.e.~containing only the oral and pharyngeal jaws) and having datasets (N=104) containing the whole head for principle components analysis and extraction of the otoliths.
 In our microCT imaging setup the resulting voxel size is directly correlated with the sample diameter, i.e.~smaller specimen were scanned with the smallest voxel size, in the range of several μm.
 The skulls of larger specimen were scanned with the largest voxel sizes, in the range of several tens of μm.
-The chosen voxel size is thus specimen- or scan-specific and was always selected such that the desired region of interest fits into the available lateral field of view of the microCT machine at the minimally necessary voxel size to resolve the structures of interest.
+The chosen voxel size is thus specimen- and scan-specific, and was always selected such that the desired region of interest fits into the available lateral field of view of the microCT machine at the smallest necessary voxel size to resolve the structures of interest.
 
@@
 The extraction is robust because it is based on a combination of distinct details of the gray value curve over the different anatomical directions.
-The details of the otolith extraction method have been extensively tuned and run in a fully automatic way.
+The details of the otolith extraction method have been extensively tuned and run in a fully automated way.
 This allows a highly reproducible and unbiased extraction of the otoliths from the tomographic datasets.
-This is even the case for one fish which was scanned with still a hook in his mouth, where the otoliths were nonetheless extracted automatically.
+This is even the case for one fish which was scanned with a hook still in it's mouth, where the otoliths were nonetheless automatically extracted without any issue.
 
@@
 One could help estimate the age of wild fishes using a calibration based on the otolith measurements of a fish of known age.
-It is worth nothing that estimation of age of tropical fishes is not as simple as for fishes from temperate regions where one can distinguish summer and winter layers within the otolith.
+It is worth noting that the estimation of age in tropical fishes are not as simple as for fishes from temperate regions, where one can distinguish summer and winter layers within the otolith {[}\protect\hyperlink{ref-doi:10.1126ux2fscience.173.4002.112}{\textbf{doi:10.1126/science.173.4002.112?}}{]}.
 
-To our best knowledge, no fully automated method for non-destructive otolith extraction from high-resolution tomographic data has been published up to now.
+To the best of our knowledge, no fully automated method for non-destructive otolith extraction from high-resolution tomographic data has been published up to now.
 Vasconcelos-Filho et al.
 {[}\protect\hyperlink{ref-PgMc4mCy}{36}{]} show a potentially objective method to count growth rings in otoliths of six fish species, but performed their study on extracted otoliths ``embedded in a Styrofoam cube'', while our method non-destructively extracts the otoliths from the tomographic data.
-Gu et al.
-{[}\protect\hyperlink{ref-HYXdLQTV}{37}{]} also provide detailed insight into otolith and combine microtomographic imaging (with unknown voxel size) with scanning electron microscopy, but also mention that the ``otoliths were removed {[}from \emph{Bahaba taipingensis}{]}, cleaned and kept dry for morphologic observation''.
+Gu et al. {[}\protect\hyperlink{ref-HYXdLQTV}{37}{]} also provide detailed insight into otoliths and combine microtomographic imaging (with unknown voxel size) with scanning electron microscopy.
+However, they also mention that the ``otoliths were removed {[}from \emph{Bahaba taipingensis}{]}, cleaned and kept dry for morphologic observation''.
 

### 2023-08-15 manuscript.tex
Instead of writing of 'haplochromine' cichlids [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/37cc38a386f502ad80dd15509062ce55dc9330d8.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/37cc38a386f502ad80dd15509062ce55dc9330d8/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5869141381

@@
 \emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.1...cf71b71e6291167fe12fef6359937f11e6552b5b\#files_bucket}{is further updated} since re-submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.1...37cc38a386f502ad80dd15509062ce55dc9330d8\#files_bucket}{is further updated} since re-submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/cf71b71e6291167fe12fef6359937f11e6552b5b/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/37cc38a386f502ad80dd15509062ce55dc9330d8/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/cf71b71e6291167fe12fef6359937f11e6552b5b}{habi/EAWAG-manuscript@cf71b71}
+from \href{https://github.com/habi/EAWAG-manuscript/tree/37cc38a386f502ad80dd15509062ce55dc9330d8}{habi/EAWAG-manuscript@37cc38a}
 on August 15, 2023.
@@
 
-The collection of cichlid fish available is extremely valuable, hence a nondestructive imaging method is paramount for studying these samples.
+The collection of Lake Victoria cichlids investigated here is extremely valuable, hence a nondestructive imaging method for studying these samples is paramount.
 Since micro--computed tomography can be regarded as a nondestructive investigation method for biological samples, it is the ideal imaging method for investigating the oral and pharyngeal jaws as well as the skull features of the fish presented in this study {[}\protect\hyperlink{ref-19h9vxsYG}{6}{]} (N=133).

### 2023-08-17 manuscript.tex
Skip `manubot` update in "further updated" link [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/3bd352c60eea4ece353bd537273c44174cfb1d78.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/3bd352c60eea4ece353bd537273c44174cfb1d78/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5891020105

@@
 \emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.1...37cc38a386f502ad80dd15509062ce55dc9330d8\#files_bucket}{is further updated} since re-submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...3bd352c60eea4ece353bd537273c44174cfb1d78\#files_bucket}{is further updated} since re-submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/37cc38a386f502ad80dd15509062ce55dc9330d8/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/3bd352c60eea4ece353bd537273c44174cfb1d78/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/37cc38a386f502ad80dd15509062ce55dc9330d8}{habi/EAWAG-manuscript@37cc38a}
-on August 15, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/3bd352c60eea4ece353bd537273c44174cfb1d78}{habi/EAWAG-manuscript@3bd352c}
+on August 17, 2023.
 
@@
 \CSLLeftMargin{15. }%
-\CSLRightInline{OpenSCAD. {[}cited 15 Aug 2023{]}. Available: \url{https://openscad.org}}
+\CSLRightInline{OpenSCAD. {[}cited 17 Aug 2023{]}. Available: \url{https://openscad.org}}
 
@@
 \CSLLeftMargin{23. }%
-\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+1.g86b56a7.dirty documentation. {[}cited 15 Aug 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
+\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+1.g86b56a7.dirty documentation. {[}cited 17 Aug 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
 
@@
 \CSLLeftMargin{26. }%
-\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 15 Aug 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
+\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 17 Aug 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
 

### 2023-08-21 manuscript.tex
Merge pull request #17 from habi/rootstock-2023-08-21 [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/28f3d2d2eba7b007cc01d09b5cd6d4e926848aa5.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/28f3d2d2eba7b007cc01d09b5cd6d4e926848aa5/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5926946849

--- 2023-08-15 manuscript.tex
@@
 \emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.1...37cc38a386f502ad80dd15509062ce55dc9330d8\#files_bucket}{is further updated} since re-submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...28f3d2d2eba7b007cc01d09b5cd6d4e926848aa5\#files_bucket}{is further updated} since re-submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/37cc38a386f502ad80dd15509062ce55dc9330d8/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/28f3d2d2eba7b007cc01d09b5cd6d4e926848aa5/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/37cc38a386f502ad80dd15509062ce55dc9330d8}{habi/EAWAG-manuscript@37cc38a}
-on August 15, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/28f3d2d2eba7b007cc01d09b5cd6d4e926848aa5}{habi/EAWAG-manuscript@28f3d2d}
+on August 21, 2023.
 
@@
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187} ·
+  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
   · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
@@
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0002-4413-2633}{0000-0002-4413-2633} ·
+  \href{https://orcid.org/0000-0002-4413-2633}{0000-0002-4413-2633}
   · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
@@
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0001-6598-1434}{0000-0001-6598-1434} ·
+  \href{https://orcid.org/0000-0001-6598-1434}{0000-0001-6598-1434}
   · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
@@
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0002-6722-8996}{0000-0002-6722-8996} ·
+  \href{https://orcid.org/0000-0002-6722-8996}{0000-0002-6722-8996}
   · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
@@
 \CSLLeftMargin{15. }%
-\CSLRightInline{OpenSCAD. {[}cited 15 Aug 2023{]}. Available: \url{https://openscad.org}}
+\CSLRightInline{OpenSCAD. {[}cited 21 Aug 2023{]}. Available: \url{https://openscad.org}}
 
@@
 \CSLLeftMargin{23. }%
-\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+1.g86b56a7.dirty documentation. {[}cited 15 Aug 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
+\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+1.g86b56a7.dirty documentation. {[}cited 21 Aug 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
 
@@
 \CSLLeftMargin{26. }%
-\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 15 Aug 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
+\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 21 Aug 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
 

### 2023-08-21 manuscript.tex
Merge branch 'main' of github.com:habi/EAWAG-manuscript into main [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/d49ab3e8164a4169e27e9555874ff7f107c09650.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/d49ab3e8164a4169e27e9555874ff7f107c09650/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5927766734

@@
 \emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...28f3d2d2eba7b007cc01d09b5cd6d4e926848aa5\#files_bucket}{is further updated} since re-submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...d49ab3e8164a4169e27e9555874ff7f107c09650\#files_bucket}{is further updated} since re-submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/28f3d2d2eba7b007cc01d09b5cd6d4e926848aa5/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/d49ab3e8164a4169e27e9555874ff7f107c09650/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/28f3d2d2eba7b007cc01d09b5cd6d4e926848aa5}{habi/EAWAG-manuscript@28f3d2d}
+from \href{https://github.com/habi/EAWAG-manuscript/tree/d49ab3e8164a4169e27e9555874ff7f107c09650}{habi/EAWAG-manuscript@d49ab3e}
 on August 21, 2023.
@@
   \textbf{David Haberthür}
+  \textsuperscript{\protect\hyperlink{correspondence}{✉}}
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187} ·
+  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/habi}{habi}
@@
   \textbf{Mikki Law}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/mlaw-migalig}{mlaw-migalig}
@@
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0002-4413-2633}{0000-0002-4413-2633}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://orcid.org/0000-0002-4413-2633}{0000-0002-4413-2633} ·
+  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/kassthefish}{kassthefish}
@@
   \textbf{Marcel Häsler}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/mphaesler}{mphaesler}
@@
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0001-6598-1434}{0000-0001-6598-1434}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://orcid.org/0000-0001-6598-1434}{0000-0001-6598-1434} ·
+  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/OleSeehausen}{OleSeehausen}
@@
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0002-6722-8996}{0000-0002-6722-8996}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://orcid.org/0000-0002-6722-8996}{0000-0002-6722-8996} ·
+  \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
   \href{https://github.com/RuslanHlushchuk}{RuslanHlushchuk}
@@
 \leavevmode\vadjust pre{\hypertarget{correspondence}{}}%
-✉ --- Correspondence possible via \href{https://github.com/habi/EAWAG-manuscript/issues}{GitHub Issues}
+✉ --- Correspondence possible via email or \href{https://github.com/habi/EAWAG-manuscript/issues}{GitHub Issues} (preferrably).
+or email to
+David Haberthür \textless david.haberthuer@unibe.ch\textgreater.
 
@@
 The study used specimens from an already existing fish collection built over decades of research led by Ole Seehausen that continues to this day.
-All relevant permits for research, exportsfrom the respective country and import to Switzerland were given and the research has followed modern ethical guidelines for scientific research.
+All relevant permits for research, exports from the respective country and import to Switzerland were given and the research has followed modern ethical guidelines for scientific research.
 

### 2023-08-22 manuscript.tex
Pretty `mailto` link [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/c050bb80f13115ddab1a67428d31c5177ce08ee7.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/c050bb80f13115ddab1a67428d31c5177ce08ee7/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5937561720

@@
 \emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...d49ab3e8164a4169e27e9555874ff7f107c09650\#files_bucket}{is further updated} since re-submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...c050bb80f13115ddab1a67428d31c5177ce08ee7\#files_bucket}{is further updated} since re-submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/d49ab3e8164a4169e27e9555874ff7f107c09650/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/c050bb80f13115ddab1a67428d31c5177ce08ee7/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/d49ab3e8164a4169e27e9555874ff7f107c09650}{habi/EAWAG-manuscript@d49ab3e}
-on August 21, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/c050bb80f13115ddab1a67428d31c5177ce08ee7}{habi/EAWAG-manuscript@c050bb8}
+on August 22, 2023.
 
@@
 \leavevmode\vadjust pre{\hypertarget{correspondence}{}}%
-✉ --- Correspondence possible via email or \href{https://github.com/habi/EAWAG-manuscript/issues}{GitHub Issues} (preferrably).
+✉ --- Correspondence via \href{https://github.com/habi/EAWAG-manuscript/issues}{GitHub Issues}
 or email to
-David Haberthür \textless david.haberthuer@unibe.ch\textgreater.
+\href{mailto:david.haberthuer@unibe.ch?subject=Feedback\%20for\%20\%22Microtomographic\%20investigation\%20of\%20a\%20large\%20corpus\%20of\%20cichlids\%22\&body=Write\%20your\%20feedback\%20here.}{David Haberthür}.
 
@@
 \CSLLeftMargin{10. }%
-\CSLRightInline{Available: \url{https://osf.io/ecmz4}}
+\CSLRightInline{Summers AP. CT Scans - \#ScanAllFish. 2015 {[}cited 22 Aug 2023{]}. Available: \url{https://osf.io/ecmz4/}}
 
@@
 \CSLLeftMargin{15. }%
-\CSLRightInline{OpenSCAD. {[}cited 21 Aug 2023{]}. Available: \url{https://openscad.org}}
+\CSLRightInline{OpenSCAD. {[}cited 22 Aug 2023{]}. Available: \url{https://openscad.org}}
 
@@
 \CSLLeftMargin{23. }%
-\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+1.g86b56a7.dirty documentation. {[}cited 21 Aug 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
+\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+1.g86b56a7.dirty documentation. {[}cited 22 Aug 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
 
@@
 \CSLLeftMargin{26. }%
-\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 21 Aug 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
+\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 22 Aug 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
 

### 2023-09-14 manuscript.tex
Correct citation [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/1dcd4ef07da5b54f4e19c12f8df6e68aaf709e51.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/1dcd4ef07da5b54f4e19c12f8df6e68aaf709e51/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/6187112824

@@
 \emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...c050bb80f13115ddab1a67428d31c5177ce08ee7\#files_bucket}{is further updated} since re-submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...1dcd4ef07da5b54f4e19c12f8df6e68aaf709e51\#files_bucket}{is further updated} since re-submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/c050bb80f13115ddab1a67428d31c5177ce08ee7/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/1dcd4ef07da5b54f4e19c12f8df6e68aaf709e51/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/c050bb80f13115ddab1a67428d31c5177ce08ee7}{habi/EAWAG-manuscript@c050bb8}
-on August 22, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/1dcd4ef07da5b54f4e19c12f8df6e68aaf709e51}{habi/EAWAG-manuscript@1dcd4ef}
+on September 14, 2023.
 
@@
 One could help estimate the age of wild fishes using a calibration based on the otolith measurements of a fish of known age.
-It is worth noting that the estimation of age in tropical fishes are not as simple as for fishes from temperate regions, where one can distinguish summer and winter layers within the otolith {[}\protect\hyperlink{ref-doi:10.1126ux2fscience.173.4002.112}{\textbf{doi:10.1126/science.173.4002.112?}}{]}.
+It is worth noting that the estimation of age in tropical fishes are not as simple as for fishes from temperate regions, where one can distinguish summer and winter layers within the otolith {[}\protect\hyperlink{ref-Iy1X7kEU}{36}{]}.
 
@@
 Vasconcelos-Filho et al.
-{[}\protect\hyperlink{ref-PgMc4mCy}{36}{]} show a potentially objective method to count growth rings in otoliths of six fish species, but performed their study on extracted otoliths ``embedded in a Styrofoam cube'', while our method non-destructively extracts the otoliths from the tomographic data.
-Gu et al. {[}\protect\hyperlink{ref-HYXdLQTV}{37}{]} also provide detailed insight into otoliths and combine microtomographic imaging (with unknown voxel size) with scanning electron microscopy.
+{[}\protect\hyperlink{ref-PgMc4mCy}{37}{]} show a potentially objective method to count growth rings in otoliths of six fish species, but performed their study on extracted otoliths ``embedded in a Styrofoam cube'', while our method non-destructively extracts the otoliths from the tomographic data.
+Gu et al. {[}\protect\hyperlink{ref-HYXdLQTV}{38}{]} also provide detailed insight into otoliths and combine microtomographic imaging (with unknown voxel size) with scanning electron microscopy.
 However, they also mention that the ``otoliths were removed {[}from \emph{Bahaba taipingensis}{]}, cleaned and kept dry for morphologic observation''.
@@
 We are grateful to the \href{https//www.mic.unibe.ch/}{Microscopy Imaging Center} of the University of Bern for the infrastructural support.
-We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{38}{]} for helping us write this manuscript collaboratively.
+We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{39}{]} for helping us write this manuscript collaboratively.
 
@@
 Microcomputed tomography used to link head morphology and observed feeding behavior in cichlids of Lake Malaŵi.
-Ecol Evol.
+Ecology and Evolution.
 2021;11: 4605--4615.
@@
 \CSLLeftMargin{10. }%
-\CSLRightInline{Summers AP. CT Scans - \#ScanAllFish. 2015 {[}cited 22 Aug 2023{]}. Available: \url{https://osf.io/ecmz4/}}
+\CSLRightInline{Available: \url{https://osf.io/ecmz4}}
 
@@
 \CSLLeftMargin{15. }%
-\CSLRightInline{OpenSCAD. {[}cited 22 Aug 2023{]}. Available: \url{https://openscad.org}}
+\CSLRightInline{OpenSCAD. {[}cited 14 Sep 2023{]}. Available: \url{https://openscad.org}}
 
@@
 \CSLLeftMargin{23. }%
-\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+1.g86b56a7.dirty documentation. {[}cited 22 Aug 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
+\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+3.gc52eec3.dirty documentation. {[}cited 14 Sep 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
 
@@
 \CSLLeftMargin{26. }%
-\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 22 Aug 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
+\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 14 Sep 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
 
@@
 \CSLLeftMargin{29. }%
-\CSLRightInline{Collyer ML, Adams DC. RRPP: An
-\textless scp\textgreater r\textless/scp\textgreater{}
-package for fitting linear models to high‐dimensional data using residual randomization.
+\CSLRightInline{Collyer ML, Adams DC.
+RRPP: An \textless scp\textgreater r\textless/scp\textgreater{} package for fitting linear models to high‐dimensional data using residual randomization.
 Freckleton R, editor.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Iy1X7kEU}{}}%
+\CSLLeftMargin{36. }%
+\CSLRightInline{Pannella G.
+Fish Otoliths: Daily Growth Layers and Periodical Patterns.
+Science.
+1971;173: 1124--1127.
+doi:\href{https://doi.org/10.1126/science.173.4002.1124}{10.1126/science.173.4002.1124}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-PgMc4mCy}{}}%
-\CSLLeftMargin{36. }%
+\CSLLeftMargin{37. }%
 \CSLRightInline{Vasconcelos-Filho JE, Thomsen FSL, Stosic B, Antonino ACD, Duarte DA, Heck RJ, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-HYXdLQTV}{}}%
-\CSLLeftMargin{37. }%
+\CSLLeftMargin{38. }%
 \CSLRightInline{Gu Y-G, Huang H-H, Liang Y, Fang Y, Dai M, Ou Y-J, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{38. }%
+\CSLLeftMargin{39. }%
 \CSLRightInline{Himmelstein DS, Rubinetti V, Slochower DR, Hu D, Malladi VS, Greene CS, et al.

### 2023-09-14 manuscript.tex
We provide multiple notebooks [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/c89de3aab786e55c724102ed14dbb33fb23561e5.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/c89de3aab786e55c724102ed14dbb33fb23561e5/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/6187161665

@@
 \emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...1dcd4ef07da5b54f4e19c12f8df6e68aaf709e51\#files_bucket}{is further updated} since re-submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...c89de3aab786e55c724102ed14dbb33fb23561e5\#files_bucket}{is further updated} since re-submission.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/1dcd4ef07da5b54f4e19c12f8df6e68aaf709e51/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/c89de3aab786e55c724102ed14dbb33fb23561e5/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/1dcd4ef07da5b54f4e19c12f8df6e68aaf709e51}{habi/EAWAG-manuscript@1dcd4ef}
+from \href{https://github.com/habi/EAWAG-manuscript/tree/c89de3aab786e55c724102ed14dbb33fb23561e5}{habi/EAWAG-manuscript@c89de3a}
 on September 14, 2023.
@@
 The workflow is relying only on free and open-source software and can thus be used and verified independently by any interested reader.
-All the \emph{Jupyter} notebook described herein is also freely available online {[}\protect\hyperlink{ref-1HteOscVd}{19}{]}.
+All the \emph{Jupyter} notebooks described herein are also freely available online {[}\protect\hyperlink{ref-1HteOscVd}{19}{]}.
 

### 2023-09-18 manuscript.tex
Accepted! [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/4b17b5aadc8f896a77b0e0ad3ef169ff6e149830.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/4b17b5aadc8f896a77b0e0ad3ef169ff6e149830/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/6219737950

@@
 \emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...c89de3aab786e55c724102ed14dbb33fb23561e5\#files_bucket}{is further updated} since re-submission.}
+\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...4b17b5aadc8f896a77b0e0ad3ef169ff6e149830\#files_bucket}{is further updated} since re-submission.}
+\emph{The manuscript ``has been judged scientifically suitable for publication and will be formally accepted for publication once it meets all outstanding technical requirements'' by PLOS ONE.}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/c89de3aab786e55c724102ed14dbb33fb23561e5/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/4b17b5aadc8f896a77b0e0ad3ef169ff6e149830/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/c89de3aab786e55c724102ed14dbb33fb23561e5}{habi/EAWAG-manuscript@c89de3a}
-on September 14, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/4b17b5aadc8f896a77b0e0ad3ef169ff6e149830}{habi/EAWAG-manuscript@4b17b5a}
+on September 18, 2023.
 
@@
 \CSLLeftMargin{10. }%
-\CSLRightInline{Available: \url{https://osf.io/ecmz4}}
+\CSLRightInline{Summers AP. CT Scans - \#ScanAllFish. 2015 {[}cited 18 Sep 2023{]}. Available: \url{https://osf.io/ecmz4/}}
 
@@
 \CSLLeftMargin{15. }%
-\CSLRightInline{OpenSCAD. {[}cited 14 Sep 2023{]}. Available: \url{https://openscad.org}}
+\CSLRightInline{OpenSCAD. {[}cited 18 Sep 2023{]}. Available: \url{https://openscad.org}}
 
@@
 \CSLLeftMargin{23. }%
-\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+3.gc52eec3.dirty documentation. {[}cited 14 Sep 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
+\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+3.gc52eec3.dirty documentation. {[}cited 18 Sep 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
 
@@
 \CSLLeftMargin{26. }%
-\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 14 Sep 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
+\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 18 Sep 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
 

### 2023-10-17 manuscript.tex
Add DOI from PLOS ONE [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/348c49975dcc5d8f29a226f04aaca4c476c8c667.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/348c49975dcc5d8f29a226f04aaca4c476c8c667/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/6547562661

--- 2023-09-14 manuscript.tex
@@
-\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
-\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
-\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
-\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...c89de3aab786e55c724102ed14dbb33fb23561e5\#files_bucket}{is further updated} since re-submission.}
+\emph{A DOI-citable version of this manuscript is available at \url{https://doi.org/10.1371/journal.pone.0291003}}
 
 This manuscript
-(\href{https://habi.github.io/EAWAG-manuscript/v/c89de3aab786e55c724102ed14dbb33fb23561e5/}{permalink})
+(\href{https://habi.github.io/EAWAG-manuscript/v/348c49975dcc5d8f29a226f04aaca4c476c8c667/}{permalink})
 was automatically generated
-from \href{https://github.com/habi/EAWAG-manuscript/tree/c89de3aab786e55c724102ed14dbb33fb23561e5}{habi/EAWAG-manuscript@c89de3a}
-on September 14, 2023.
+from \href{https://github.com/habi/EAWAG-manuscript/tree/348c49975dcc5d8f29a226f04aaca4c476c8c667}{habi/EAWAG-manuscript@348c499}
+on October 17, 2023.
 
@@
 \CSLLeftMargin{15. }%
-\CSLRightInline{OpenSCAD. {[}cited 14 Sep 2023{]}. Available: \url{https://openscad.org}}
+\CSLRightInline{OpenSCAD. {[}cited 17 Oct 2023{]}. Available: \url{https://openscad.org}}
 
@@
 \CSLLeftMargin{23. }%
-\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+3.gc52eec3.dirty documentation. {[}cited 14 Sep 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
+\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+3.gc52eec3.dirty documentation. {[}cited 17 Oct 2023{]}. Available: \url{https://image.dask.org/en/latest/}}
 
@@
 \CSLLeftMargin{26. }%
-\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 14 Sep 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
+\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 17 Oct 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
 
